---
title: "IGNYTE: RP1 + Nivolumab in PD-1–Failed Melanoma"
pagetitle: "IGNYTE | SoCO Journal Club"
description: "Meeting recap from the April 6, 2026 Society of Cutaneous Oncology Journal Club discussing IGNYTE, RP1 combined with nivolumab in anti–PD-1–failed melanoma."
date: 2026-04-06
author: "Society of Cutaneous Oncology"
categories:
  - 2026
  - Journal Club
  - Melanoma
  - Intratumoral Therapy
  - Oncolytic Immunotherapy
tags:
  - IGNYTE
  - RP1
  - Nivolumab
  - Melanoma
  - Regulatory Science
  - Estimands
image: card.svg
page-layout: full
title-block-style: none
toc: false
execute:
  echo: false
  warning: false
  message: false
---

<style>
  :root {
    --navy: #082D4D;
    --teal: #28A9A2;
    --coral: #E25A4E;
    --ink: #31424E;
    --muted: #6B747B;
    --pale: #F3F8F8;
    --line: #D9E8E8;
  }

  #title-block-header,
  .quarto-title-block,
  .quarto-title,
  .quarto-title-meta {
    display: none !important;
  }

  body {
    color: var(--ink);
    background: #fff;
  }

  main.content {
    width: 100%;
    max-width: 1120px;
    min-width: 0;
    margin: auto;
    padding-top: 0 !important;
  }

  main.content,
  main.content * {
    box-sizing: border-box;
  }

  h1,h2,h3 {
    color: var(--navy);
    font-weight: 800;
  }

  .hero {
    margin: 2rem 0 2.4rem;
    padding: 2.8rem 3rem;
    border-radius: 24px;
    background:
      radial-gradient(circle at 88% 12%, rgba(40,169,162,.11), transparent 31%),
      linear-gradient(135deg,#F3F8F8 0%,#FFFFFF 72%);
    border: 1px solid var(--line);
    box-shadow: 0 10px 30px rgba(8,45,77,.07);
  }

  .kicker,
  .section-kicker {
    color: var(--teal);
    font-weight: 800;
    letter-spacing: .15em;
    text-transform: uppercase;
    font-size: .8rem;
  }

  .hero h1 {
    max-width: 900px;
    font-size: clamp(2.7rem,5vw,4.1rem);
    line-height: 1.02;
    margin: .55rem 0 .8rem;
    letter-spacing: -.04em;
  }

  .hero-copy {
    font-size: 1.2rem;
    max-width: 860px;
    color: #56636D;
    line-height: 1.65;
  }

  .accent {
    width: 94px;
    height: 5px;
    border-radius: 4px;
    background:
      linear-gradient(
        90deg,
        var(--teal) 0 68%,
        var(--coral) 68%
      );
    margin-top: 1.4rem;
  }

  .metric-grid {
    display: grid;
    grid-template-columns: repeat(3,1fr);
    gap: 1rem;
    margin: 1.4rem 0 2rem;
  }

  .metric-card,
  .survey-card,
  .highlight-card {
    border: 1px solid var(--line);
    border-radius: 18px;
    padding: 1.3rem 1.4rem;
    background: #fff;
    box-shadow: 0 6px 18px rgba(8,45,77,.05);
  }

  .metric-label,
  .survey-label {
    display: block;
    color: var(--muted);
    font-size: .78rem;
    font-weight: 800;
    text-transform: uppercase;
    letter-spacing: .09em;
  }

  .metric-value,
  .survey-value {
    display: block;
    color: var(--navy);
    font-size: 2.25rem;
    font-weight: 850;
    line-height: 1.05;
    margin: .35rem 0;
  }

  .metric-note,
  .survey-copy {
    color: var(--muted);
    font-size: .92rem;
    line-height: 1.5;
  }

  .section-kicker {
    margin-top: 2.8rem;
  }

  .section-intro {
    font-size: 1.05rem;
    color: #56636D;
    max-width: 880px;
    margin-bottom: 1.2rem;
    line-height: 1.7;
  }

  .paper-card {
    max-width: 980px;
    margin: 1.2rem auto 2rem;
    padding: 1.75rem 2rem 1.7rem;
    border-left: 7px solid var(--teal);
    border-radius: 0 20px 20px 0;
    background:
      linear-gradient(
        135deg,
        rgba(40,169,162,.085),
        rgba(8,45,77,.035)
      );
    box-shadow: 0 12px 30px rgba(8,45,77,.08);
  }

  .paper-eyebrow {
    color: var(--teal);
    font-size: .78rem;
    font-weight: 850;
    letter-spacing: .14em;
    text-transform: uppercase;
    margin-bottom: .65rem;
  }

  .paper-title {
    color: var(--navy);
    font-size: 1.62rem;
    line-height: 1.22;
    font-weight: 850;
    letter-spacing: -.015em;
    margin: 0 0 .85rem;
  }

  .paper-citation {
    color: #52616D;
    font-size: .98rem;
    line-height: 1.45;
  }

  .link-row {
    display: flex;
    flex-wrap: wrap;
    gap: .7rem;
    margin-top: 1.2rem;
  }

  .soco-link {
    display: inline-flex;
    padding: .58rem .9rem;
    border-radius: 999px;
    background: var(--navy);
    color: #fff !important;
    text-decoration: none;
    font-size: .88rem;
    font-weight: 750;
  }

  .soco-link.secondary {
    background: #fff;
    border: 1px solid rgba(40,169,162,.42);
    color: var(--navy) !important;
  }

  .question-card {
    margin: 1.6rem 0 2rem;
    padding: 1.55rem 1.7rem;
    border-left: 5px solid var(--coral);
    border-radius: 0 14px 14px 0;
    background:
      linear-gradient(
        135deg,
        rgba(226,90,78,.055),
        rgba(40,169,162,.045)
      );
  }

  .question-card strong {
    display: block;
    color: var(--navy);
    font-size: 1.2rem;
    line-height: 1.55;
  }

  .survey-grid,
  .highlight-grid {
    display: grid;
    grid-template-columns:
      repeat(2,minmax(0,1fr));
    gap: 1rem;
    margin: 1.2rem 0 1.5rem;
  }

  .survey-value {
    color: var(--teal);
  }

  .survey-label {
    color: var(--navy);
    margin-bottom: .45rem;
  }

  .highlight-num {
    color: var(--coral);
    font-weight: 900;
    font-size: .8rem;
    letter-spacing: .06em;
    text-transform: uppercase;
  }

  .highlight-card h3 {
    color: var(--navy);
    font-size: 1.08rem;
    margin: .25rem 0 .55rem;
  }

  .highlight-card p {
    color: #405463;
    font-size: .94rem;
    line-height: 1.5;
    margin: 0;
  }

  .discussion-quote {
    margin: 1.4rem 0;
    padding: 1.1rem 1.25rem;
    border-left: 5px solid var(--teal);
    background: #EFF8F7;
    border-radius: 0 12px 12px 0;
    color: var(--navy);
    font-size: 1.05rem;
    font-weight: 700;
    line-height: 1.5;
  }

  .context-note {
    margin: 1.1rem 0 1.6rem;
    padding: 1.05rem 1.2rem;
    border-left: 5px solid #E6A34A;
    border-radius: 0 12px 12px 0;
    background: #FFF8F0;
    color: #59462E;
    line-height: 1.55;
  }

  .source-note {
    margin: 2rem 0;
    padding: 1.1rem 1.25rem;
    border: 1px solid var(--line);
    border-radius: 14px;
    background: #F9FBFB;
    color: #5C6871;
    font-size: .9rem;
    line-height: 1.6;
  }

  .footer-card {
    margin: 3rem 0 1rem;
    padding: 1.8rem 2rem;
    background: var(--navy);
    color: #fff;
    border-radius: 20px;
  }

  .footer-card h2 {
    color: #fff;
    margin-top: 0;
  }

  .footer-card p {
    margin-bottom: 0;
    color: #EAF2F5;
  }

  /* =========================================================
     COMMUNITY / ATTENDANCE
     ========================================================= */

  .community-banner {
    position: relative;
    overflow: hidden;
    margin: 1.2rem 0 1.3rem;
    padding: 1.45rem 1.6rem;
    border: 1px solid var(--line);
    border-radius: 18px;
    background:
      radial-gradient(circle at 90% 15%, rgba(40,169,162,.12), transparent 30%),
      linear-gradient(135deg, #F7FBFB 0%, #FFFFFF 78%);
    box-shadow: 0 8px 24px rgba(8,45,77,.05);
  }

  .community-banner::after {
    content: "";
    position: absolute;
    width: 170px;
    height: 170px;
    top: -70px;
    right: -25px;
    opacity: .18;
    background-image:
      radial-gradient(circle, rgba(40,169,162,.72) 0 1.2px, transparent 1.8px);
    background-size: 20px 20px;
    mask-image: radial-gradient(circle, #000 0%, transparent 72%);
    -webkit-mask-image: radial-gradient(circle, #000 0%, transparent 72%);
    pointer-events: none;
  }

  .community-banner-kicker {
    position: relative;
    z-index: 1;
    color: var(--teal);
    font-size: .76rem;
    font-weight: 850;
    letter-spacing: .14em;
    text-transform: uppercase;
  }

  .community-banner-title {
    position: relative;
    z-index: 1;
    margin: .28rem 0 .35rem;
    color: var(--navy);
    font-size: clamp(1.7rem, 3vw, 2.35rem);
    font-weight: 850;
    letter-spacing: -.035em;
    line-height: 1.05;
  }

  .community-banner-copy {
    position: relative;
    z-index: 1;
    max-width: 820px;
    margin: 0;
    color: var(--muted);
    font-size: .97rem;
    line-height: 1.6;
  }


  .engagement-spotlight {
    position: relative;
    overflow: hidden;
    margin: 1rem 0 1.4rem;
    padding: 1.35rem 1.45rem 1.25rem;
    border: 1px solid #E9C85F;
    border-left: 7px solid #D7A400;
    border-radius: 18px;
    background:
      radial-gradient(circle at 92% 18%, rgba(255,255,255,.58), transparent 28%),
      linear-gradient(135deg, #FFF8D8 0%, #FDE9A9 100%);
    box-shadow: 0 10px 28px rgba(116,83,0,.10);
  }

  .engagement-spotlight-title {
    display: flex;
    align-items: center;
    gap: .6rem;
    margin: 0 0 .35rem;
    color: #765308;
    font-size: 1.1rem;
    font-weight: 850;
    letter-spacing: -.01em;
  }

  .engagement-spotlight-copy {
    max-width: 860px;
    margin: 0;
    color: #735F2C;
    font-size: .94rem;
    line-height: 1.55;
  }

  .engagement-pill-row {
    display: flex;
    flex-wrap: wrap;
    gap: .55rem;
    margin-top: .95rem;
  }

  .engagement-pill {
    display: inline-flex;
    align-items: center;
    gap: .42rem;
    padding: .5rem .72rem;
    border: 1px solid rgba(118,83,8,.18);
    border-radius: 999px;
    background: rgba(255,255,255,.82);
    color: #57420D;
    font-size: .86rem;
    font-weight: 780;
    box-shadow: 0 2px 7px rgba(116,83,0,.08);
  }

  .engagement-score {
    color: #9A6A00;
    font-size: .76rem;
    font-weight: 850;
  }

  .engagement-method {
    margin: .75rem 0 0;
    color: #7C6B42;
    font-size: .78rem;
    line-height: 1.5;
  }


  .roster-summary {
    display: flex;
    align-items: baseline;
    justify-content: space-between;
    gap: 1rem;
    margin: 0 0 .8rem;
    padding: .95rem 1.05rem;
    border: 1px solid var(--line);
    border-radius: 14px;
    background: #F9FBFB;
  }

  .roster-summary strong {
    color: var(--navy);
    font-size: 1rem;
  }

  .roster-summary span {
    color: var(--muted);
    font-size: .84rem;
  }

  .gt_table {
    border: 1px solid var(--line) !important;
    border-radius: 16px !important;
    overflow: hidden !important;
    box-shadow: 0 8px 24px rgba(8,45,77,.045);
  }

  .gt_table tbody tr:nth-child(even) td {
    background: #FBFDFD;
  }

  .gt_table tbody tr:hover td {
    background: #F3F9F9;
  }

  .attendance-note {
    margin-top: .8rem;
    color: var(--muted);
    font-size: .82rem;
    line-height: 1.55;
  }

  .attendance-scroll {
    width: 100%;
    overflow-x: auto;
    -webkit-overflow-scrolling: touch;
    border-radius: 16px;
  }

  .attendance-table {
    width: 100%;
    min-width: 690px;
    border-collapse: separate;
    border-spacing: 0;
    overflow: hidden;
    border: 1px solid var(--line);
    border-radius: 16px;
    background: #fff;
    box-shadow: 0 8px 24px rgba(8,45,77,.045);
  }

  .attendance-table thead th {
    padding: .72rem .75rem;
    background: var(--navy);
    color: #fff;
    border: 0;
    font-size: .78rem;
    font-weight: 800;
    text-align: center;
  }

  .attendance-table thead th:first-child {
    text-align: left;
  }

  .attendance-table tbody td {
    padding: .66rem .75rem;
    border-top: 1px solid #E9EFF1;
    color: #334857;
    font-size: .88rem;
    text-align: center;
  }

  .attendance-table tbody tr:nth-child(even) td:not(.minutes-cell) {
    background: #FBFDFD;
  }

  .attendance-table tbody tr:hover td:not(.minutes-cell) {
    background: #F3F9F9;
  }

  .attendance-table .name-cell {
    color: var(--navy);
    font-weight: 750;
    text-align: left;
  }

  .attendance-table .minutes-cell {
    color: #17384C;
    font-variant-numeric: tabular-nums;
  }

  .attendance-table .signal-cell {
    color: #7A868E;
  }

  .attendance-table .signal-on {
    color: var(--teal);
    font-weight: 900;
  }

  /* =========================================================
     ESTIMAND PRIMER
     ========================================================= */

  .estimand-primer {
    margin: 1.3rem 0 2rem;
    padding: 1.5rem;
    border: 1px solid var(--line);
    border-radius: 20px;
    background:
      radial-gradient(circle at 92% 12%, rgba(40,169,162,.10), transparent 28%),
      linear-gradient(135deg, #F7FBFB 0%, #FFFFFF 72%);
    box-shadow: 0 8px 24px rgba(8,45,77,.05);
  }

  .estimand-primer-title {
    color: var(--navy);
    font-size: 1.35rem;
    font-weight: 850;
    letter-spacing: -.025em;
    margin-bottom: .35rem;
  }

  .estimand-primer-copy {
    max-width: 880px;
    color: var(--muted);
    line-height: 1.6;
    margin-bottom: 1.25rem;
  }

  .estimand-flow {
    display: grid;
    grid-template-columns: 1fr auto 1fr auto 1fr;
    gap: .6rem;
    align-items: stretch;
    margin: 1.1rem 0 1.4rem;
  }

  .estimand-step {
    padding: 1rem 1.05rem;
    border: 1px solid var(--line);
    border-radius: 15px;
    background: #fff;
  }

  .estimand-step strong {
    display: block;
    color: var(--teal);
    font-size: .77rem;
    font-weight: 900;
    letter-spacing: .10em;
    text-transform: uppercase;
    margin-bottom: .35rem;
  }

  .estimand-step span {
    color: var(--navy);
    font-size: .96rem;
    font-weight: 750;
    line-height: 1.4;
  }

  .estimand-arrow {
    display: flex;
    align-items: center;
    justify-content: center;
    color: var(--coral);
    font-size: 1.35rem;
    font-weight: 900;
  }

  .estimand-components {
    display: grid;
    grid-template-columns: repeat(4, minmax(0,1fr));
    gap: .7rem;
    margin: 1rem 0 1.4rem;
  }

  .estimand-component {
    padding: .85rem .9rem;
    border-top: 4px solid var(--teal);
    border-radius: 12px;
    background: #F4FAF9;
    color: var(--navy);
    font-size: .86rem;
    font-weight: 780;
    text-align: center;
  }

  .estimand-contrast {
    display: grid;
    grid-template-columns: repeat(2, minmax(0,1fr));
    gap: .8rem;
    margin-top: 1rem;
  }

  .estimand-box {
    padding: 1.1rem 1.15rem;
    border: 1px solid var(--line);
    border-radius: 15px;
    background: #fff;
  }

  .estimand-box.local {
    border-top: 4px solid #6B8DA7;
  }

  .estimand-box.systemic {
    border-top: 4px solid var(--teal);
  }

  .estimand-box h3 {
    margin: 0 0 .45rem;
    font-size: 1rem;
  }

  .estimand-box p {
    margin: 0;
    color: #526574;
    font-size: .9rem;
    line-height: 1.5;
  }

  .component-estimand {
    margin-top: .9rem;
    padding: 1rem 1.1rem;
    border-left: 5px solid var(--coral);
    border-radius: 0 13px 13px 0;
    background: #FFF8F6;
    color: #5C4742;
    font-size: .92rem;
    line-height: 1.55;
  }

  /* =========================================================
     CUSTOM SURVEY DISCLOSURE
     ========================================================= */

  .survey-disclosure {
    margin: 1.35rem 0 2rem;
  }

  .survey-toggle {
    width: 100%;
    display: grid;
    grid-template-columns: auto 1fr auto;
    gap: .9rem;
    align-items: center;
    padding: 1rem 1.15rem;
    border: 1px solid var(--line);
    border-radius: 16px;
    background:
      linear-gradient(135deg, #F3F8F8 0%, #FFFFFF 100%);
    color: var(--navy);
    text-align: left;
    cursor: pointer;
    box-shadow: 0 6px 18px rgba(8,45,77,.04);
  }

  .survey-toggle:hover {
    border-color: rgba(40,169,162,.48);
    box-shadow: 0 8px 24px rgba(8,45,77,.07);
  }

  .survey-toggle-badge {
    display: inline-flex;
    width: 38px;
    height: 38px;
    align-items: center;
    justify-content: center;
    border-radius: 50%;
    background: rgba(40,169,162,.12);
    font-size: 1.05rem;
  }

  .survey-toggle-copy strong {
    display: block;
    color: var(--navy);
    font-size: 1rem;
    font-weight: 850;
  }

  .survey-toggle-copy span {
    display: block;
    margin-top: .15rem;
    color: var(--muted);
    font-size: .84rem;
    line-height: 1.4;
  }

  .survey-toggle-icon {
    color: var(--teal);
    font-size: 1.3rem;
    font-weight: 900;
    transition: transform .2s ease;
  }

  .survey-toggle[aria-expanded="true"] .survey-toggle-icon {
    transform: rotate(45deg);
  }

  .survey-panel {
    display: none;
    margin-top: .8rem;
    padding: 1.2rem;
    border: 1px solid var(--line);
    border-radius: 16px;
    background: #fff;
  }

  .survey-panel.is-open {
    display: block;
  }

  .survey-panel-intro {
    margin: 0 0 1.2rem;
    padding: .85rem 1rem;
    border-left: 4px solid var(--teal);
    background: #F5FAFA;
    color: var(--muted);
    font-size: .9rem;
    line-height: 1.55;
  }

  .survey-figure-separator {
    margin: 1.6rem 0;
    border: 0;
    border-top: 1px solid #EDF2F4;
  }

  .survey-question-label {
    color: var(--teal);
    font-size: .76rem;
    font-weight: 850;
    letter-spacing: .10em;
    text-transform: uppercase;
    margin: 1rem 0 .4rem;
  }

  .survey-text-list {
    display: grid;
    gap: .55rem;
    margin-top: .5rem;
  }

  .survey-text-item {
    padding: .78rem .9rem;
    border: 1px solid var(--line);
    border-radius: 11px;
    background: #FAFCFC;
    color: #4B5E6C;
    font-size: .88rem;
    line-height: 1.5;
  }

  /* =========================================================
     RELEVANT UPDATES
     ========================================================= */

  .updates-wrap {
    margin: 3rem 0 2rem;
  }

  .updates-intro {
    max-width: 900px;
    margin-bottom: 1.2rem;
    color: var(--muted);
    font-size: 1rem;
    line-height: 1.65;
  }

  .updates-timeline {
    position: relative;
    display: grid;
    gap: .85rem;
    margin-top: 1rem;
  }

  .updates-item {
    display: grid;
    grid-template-columns: 118px minmax(0, 1fr);
    gap: 1rem;
    align-items: stretch;
  }

  .updates-date {
    display: flex;
    align-items: flex-start;
    justify-content: flex-end;
    padding-top: 1rem;
    color: var(--teal);
    font-size: .78rem;
    font-weight: 850;
    letter-spacing: .08em;
    text-transform: uppercase;
  }

  .updates-card {
    position: relative;
    padding: 1rem 1.15rem 1.05rem;
    border: 1px solid var(--line);
    border-radius: 15px;
    background: #fff;
    box-shadow: 0 6px 18px rgba(8,45,77,.045);
  }

  .updates-card::before {
    content: "";
    position: absolute;
    left: -1.45rem;
    top: 1.2rem;
    width: .72rem;
    height: .72rem;
    border-radius: 50%;
    background: var(--teal);
    box-shadow: 0 0 0 4px #E8F5F3;
  }

  .updates-item.approval .updates-card {
    border-color: #B9DED9;
    background:
      linear-gradient(135deg, #F3FAF9 0%, #FFFFFF 100%);
  }

  .updates-item.approval .updates-card::before {
    background: #0F8D78;
    box-shadow: 0 0 0 4px #DDF3EE;
  }

  .updates-card h3 {
    margin: 0 0 .35rem;
    color: var(--navy);
    font-size: 1.02rem;
  }

  .updates-card p {
    margin: 0;
    color: #516472;
    font-size: .91rem;
    line-height: 1.55;
  }

  .updates-links {
    display: flex;
    flex-wrap: wrap;
    gap: .55rem;
    margin-top: .75rem;
  }

  .updates-link {
    display: inline-flex;
    align-items: center;
    padding: .42rem .7rem;
    border: 1px solid #BED7DF;
    border-radius: 999px;
    background: #fff;
    color: var(--navy) !important;
    font-size: .78rem;
    font-weight: 750;
    text-decoration: none;
  }

  .updates-link:hover {
    border-color: var(--teal);
    background: #F2FAF9;
  }

  .updates-reflection {
    margin-top: 1.2rem;
    padding: 1.05rem 1.15rem;
    border-left: 5px solid var(--coral);
    border-radius: 0 13px 13px 0;
    background: #FFF8F6;
    color: #5B4945;
    font-size: .92rem;
    line-height: 1.6;
  }

  /* =========================================================
     MOBILE
     ========================================================= */

  @media (max-width:760px) {
    /*
      Quarto uses a page-level CSS grid. The important mobile fixes are:
      - allow the content grid item and every custom child to shrink;
      - use minmax(0,1fr) for one-column layouts;
      - keep intentionally wide attendance tables inside their own scroller.
    */

    html,
    body {
      max-width: 100%;
      overflow-x: hidden;
    }

    #quarto-content,
    #quarto-content.page-columns,
    main.content,
    .page-columns .content {
      min-width: 0 !important;
      max-width: 100% !important;
    }

    main.content {
      width: 100% !important;
      margin: 0 !important;
      padding: 0 1rem !important;
    }

    main.content > *,
    .hero,
    .metric-grid,
    .metric-card,
    .survey-grid,
    .survey-card,
    .highlight-grid,
    .highlight-card,
    .paper-card,
    .question-card,
    .context-note,
    .discussion-quote,
    .source-note,
    .community-banner,
    .engagement-spotlight,
    .engagement-pill-row,
    .engagement-pill,
    .roster-summary,
    .attendance-scroll,
    .estimand-primer,
    .estimand-flow,
    .estimand-step,
    .estimand-components,
    .estimand-component,
    .estimand-contrast,
    .estimand-box,
    .component-estimand,
    .survey-disclosure,
    .survey-toggle,
    .survey-toggle-copy,
    .survey-panel,
    .survey-text-list,
    .survey-text-item,
    .updates-wrap,
    .updates-timeline,
    .updates-item,
    .updates-card,
    .updates-links,
    .updates-link,
    .updates-reflection,
    .footer-card,
    .link-row {
      min-width: 0;
      max-width: 100%;
    }

    .hero {
      margin: 1rem 0 1.8rem;
      padding: 1.55rem 1.1rem 1.45rem;
      border-radius: 18px;
    }

    .hero h1 {
      max-width: 100%;
      font-size: clamp(2rem, 9.5vw, 2.55rem);
      line-height: 1.04;
      letter-spacing: -.035em;
      overflow-wrap: anywhere;
    }

    .hero-copy {
      max-width: 100%;
      font-size: 1rem;
      line-height: 1.52;
    }

    .kicker,
    .section-kicker,
    .community-banner-kicker {
      font-size: .72rem;
      line-height: 1.45;
      letter-spacing: .11em;
      overflow-wrap: anywhere;
    }

    main.content h2 {
      max-width: 100%;
      font-size: clamp(1.55rem, 7vw, 2rem);
      line-height: 1.12;
      overflow-wrap: anywhere;
    }

    main.content h3,
    .paper-title,
    .community-banner-title,
    .estimand-primer-title {
      max-width: 100%;
      overflow-wrap: anywhere;
    }

    .metric-grid,
    .survey-grid,
    .highlight-grid,
    .estimand-components,
    .estimand-contrast {
      grid-template-columns: minmax(0,1fr);
      gap: .8rem;
    }

    .metric-card,
    .survey-card,
    .highlight-card {
      padding: 1.05rem 1.1rem;
      border-radius: 14px;
    }

    .metric-value,
    .survey-value {
      font-size: 2rem;
    }

    .paper-card {
      width: 100%;
      margin: 1rem 0 1.8rem;
      padding: 1.2rem 1rem;
      border-left-width: 5px;
      border-radius: 0 15px 15px 0;
    }

    .paper-title {
      font-size: 1.28rem;
    }

    .paper-citation {
      overflow-wrap: anywhere;
    }

    .link-row {
      display: grid;
      grid-template-columns: minmax(0,1fr);
      width: 100%;
      gap: .6rem;
    }

    .soco-link {
      width: 100%;
      max-width: 100%;
      justify-content: center;
      text-align: center;
      white-space: normal;
    }

    .question-card,
    .context-note,
    .discussion-quote,
    .source-note,
    .component-estimand,
    .updates-reflection {
      padding: 1rem;
    }

    .community-banner {
      padding: 1.15rem 1rem;
      border-radius: 16px;
    }

    .community-banner-title {
      font-size: clamp(1.55rem, 7.5vw, 2rem);
    }

    .engagement-spotlight {
      padding: 1.1rem 1rem;
    }

    .engagement-pill-row {
      display: grid;
      grid-template-columns: minmax(0,1fr);
    }

    .engagement-pill {
      width: 100%;
      min-width: 0;
      justify-content: space-between;
      white-space: normal;
    }

    .roster-summary {
      display: block;
      padding: .85rem .9rem;
    }

    .roster-summary span {
      display: block;
      margin-top: .3rem;
    }

    .attendance-scroll {
      width: 100%;
      max-width: 100%;
      margin-left: 0;
      margin-right: 0;
      padding-bottom: .3rem;
      overflow-x: auto;
      -webkit-overflow-scrolling: touch;
    }

    .attendance-table {
      width: 690px;
      min-width: 690px;
      max-width: none;
    }

    .estimand-primer {
      padding: 1rem;
      border-radius: 16px;
    }

    .estimand-flow {
      display: grid;
      grid-template-columns: minmax(0,1fr);
      gap: .6rem;
    }

    .estimand-arrow {
      transform: rotate(90deg);
      min-height: 18px;
      line-height: 1;
    }

    .estimand-step,
    .estimand-component,
    .estimand-box {
      width: 100%;
    }

    .survey-toggle {
      grid-template-columns: auto minmax(0,1fr) auto;
      gap: .65rem;
      padding: .9rem;
    }

    .survey-toggle-copy strong,
    .survey-toggle-copy span {
      overflow-wrap: anywhere;
    }

    .survey-panel {
      width: 100%;
      padding: .85rem;
    }

    .survey-panel .cell,
    .survey-panel .cell-output,
    .survey-panel .cell-output-display,
    .survey-panel figure,
    .survey-panel .quarto-figure {
      min-width: 0;
      max-width: 100%;
    }

    .updates-item {
      grid-template-columns: minmax(0,1fr);
      gap: .35rem;
    }

    .updates-date {
      justify-content: flex-start;
      padding-top: .35rem;
    }

    .updates-card::before {
      display: none;
    }

    .updates-links {
      display: grid;
      grid-template-columns: minmax(0,1fr);
    }

    .updates-link {
      width: 100%;
      max-width: 100%;
      justify-content: center;
      text-align: center;
      white-space: normal;
    }

    .footer-card {
      margin-top: 2.4rem;
      padding: 1.3rem 1.15rem;
      border-radius: 16px;
    }

    img,
    svg,
    video,
    iframe,
    canvas {
      max-width: 100%;
      height: auto;
    }
  }

  @media (max-width:420px) {
    main.content {
      padding-left: .85rem !important;
      padding-right: .85rem !important;
    }

    .hero {
      padding-left: 1rem;
      padding-right: 1rem;
    }

    .hero h1 {
      font-size: clamp(1.9rem, 9vw, 2.25rem);
    }

    .metric-value,
    .survey-value {
      font-size: 1.9rem;
    }

    .section-kicker {
      margin-top: 2.1rem;
    }

    .community-banner,
    .estimand-primer {
      padding-left: .9rem;
      padding-right: .9rem;
    }

    .survey-toggle-badge {
      width: 34px;
      height: 34px;
    }

    .attendance-table {
      width: 620px;
      min-width: 620px;
    }
  }


</style>

```{r}
#| label: setup-attendance

resolve_meeting_dir <- function() {

  if (
    exists("meeting_dir", inherits = TRUE) &&
    is.character(meeting_dir) &&
    length(meeting_dir) == 1 &&
    nzchar(meeting_dir) &&
    dir.exists(meeting_dir)
  ) {
    return(
      normalizePath(
        meeting_dir,
        winslash = "/",
        mustWork = TRUE
      )
    )
  }

  current_input <- tryCatch(
    knitr::current_input(dir = TRUE),
    error = function(e) NULL
  )

  if (
    !is.null(current_input) &&
    length(current_input) == 1 &&
    !is.na(current_input) &&
    nzchar(current_input) &&
    file.exists(current_input)
  ) {
    return(
      dirname(
        normalizePath(
          current_input,
          winslash = "/",
          mustWork = TRUE
        )
      )
    )
  }

  if (
    interactive() &&
    requireNamespace("rstudioapi", quietly = TRUE)
  ) {

    ctx <- tryCatch(
      rstudioapi::getSourceEditorContext(),
      error = function(e) NULL
    )

    if (
      !is.null(ctx) &&
      !is.null(ctx$path) &&
      nzchar(ctx$path) &&
      file.exists(ctx$path)
    ) {

      active_path <- normalizePath(
        ctx$path,
        winslash = "/",
        mustWork = TRUE
      )

      active_dir <- dirname(active_path)

      if (basename(active_path) == "index.qmd") {
        return(active_dir)
      }

      if (basename(active_dir) == "scripts") {
        return(dirname(active_dir))
      }
    }
  }

  stop(
    paste0(
      "Could not determine the Journal Club meeting directory.\n",
      "Render index.qmd with Quarto, or open index.qmd / process_attendance.R ",
      "in RStudio before running this chunk interactively."
    )
  )
}

meeting_dir <- resolve_meeting_dir()

source(
  file.path(
    meeting_dir,
    "scripts",
    "process_attendance.R"
  ),
  local = TRUE
)

attendance_dir <- file.path(
  meeting_dir,
  "files",
  "meeting recap-attendance"
)

people <- readr::read_csv(
  file.path(
    attendance_dir,
    "attendance_clean.csv"
  ),
  show_col_types = FALSE
)

headline <- readr::read_csv(
  file.path(
    attendance_dir,
    "attendance_summary.csv"
  ),
  show_col_types = FALSE
)

# -------------------------------------------------------------------------
# Archived pre-meeting survey
#
# Important: this uses the SAVED RDS and data dictionary. It does not make
# a live REDCap call, so the public website build is reproducible.
# -------------------------------------------------------------------------

survey_rds_path <- file.path(
  meeting_dir,
  "files",
  "Pre_JC_survey_unprocessed",
  "survey_results.rds"
)

survey_dict_candidates <- list.files(
  file.path(meeting_dir, "files", "data dictionary"),
  pattern = "_DataDictionary_.*\\.csv$",
  full.names = TRUE
)

survey_available <-
  file.exists(survey_rds_path) &&
  length(survey_dict_candidates) > 0 &&
  file.exists(file.path(meeting_dir, "scripts", "REDCap Helpers.R"))

if (survey_available) {

  survey_dict_path <- survey_dict_candidates[
    which.max(file.info(survey_dict_candidates)$mtime)
  ]

  source(
    file.path(meeting_dir, "scripts", "REDCap Helpers.R"),
    local = TRUE
  )

  survey_raw <- readRDS(survey_rds_path)

  survey_choice_map <- get_dictionary_choices(
    dict_path = survey_dict_path
  )

  survey_clean <- clean_all_survey_data(
    survey_raw,
    choice_map = survey_choice_map,
    dict_path = survey_dict_path
  )

  survey_checkbox_data <- prepare_all_checkboxes(
    survey_clean,
    choice_map = survey_choice_map,
    dict_path = survey_dict_path
  )

  survey_question_map <- create_question_map(
    dict_path = survey_dict_path
  )
}
```

:::: {.hero}

::: {.kicker}
SoCO Journal Club · April 6, 2026
:::

# IGNYTE: when a compelling signal meets an inference problem

::: {.hero-copy}
RP1 plus nivolumab produced durable responses in anti–PD-1–failed melanoma. The harder question was not whether the signal was interesting. It was **what treatment effect the study had actually established — and whether that evidence was sufficient for regulatory or clinical adoption.**
:::

::: {.accent}
:::

::::


::: {.section-kicker}
Meeting pulse
:::

## A heavily engaged melanoma group

::: {.metric-grid}

::: {.metric-card}
[Unique Teams connections]{.metric-label}

[`r headline$connections`]{.metric-value}

[`r ifelse(headline$room_connections > 0, paste0("Reconnects reconciled; includes ", headline$room_connections, " conference-room connection"), "Reconnects reconciled")`]{.metric-note}
:::

::: {.metric-card}
[Median time together]{.metric-label}

[`r round(headline$median_minutes)` min]{.metric-value}

[Median attendance after reconnects were combined]{.metric-note}
:::

::: {.metric-card}
[Stayed at least an hour]{.metric-label}

[`r scales::percent(headline$pct_60min_plus, accuracy = 1)`]{.metric-value}

[Present for at least 60 minutes]{.metric-note}
:::

:::


::: {.section-kicker}
Participation
:::

## A few ways people participated

::: {.metric-grid}

::: {.metric-card}
[Camera on]{.metric-label}

[`r scales::percent(headline$pct_camera, accuracy = 1)`]{.metric-value}

[Had the camera on at least once]{.metric-note}
:::

::: {.metric-card}
[Unmuted]{.metric-label}

[`r scales::percent(headline$pct_unmute, accuracy = 1)`]{.metric-value}

[Unmuted at least once during the meeting]{.metric-note}
:::

::: {.metric-card}
[Raised a hand]{.metric-label}

[`r scales::percent(headline$pct_hand_raise, accuracy = 1)`]{.metric-value}

[Used the Teams hand-raise signal]{.metric-note}
:::

:::


::: {.section-kicker}
The paper we discussed
:::

## Wong et al. — RP1 + nivolumab after anti–PD-1 failure

:::: {.paper-card}

::: {.paper-eyebrow}
Primary article · Journal of Clinical Oncology
:::

::: {.paper-title}
RP1 Combined With Nivolumab in Advanced Anti–PD-1–Failed Melanoma (IGNYTE)
:::

::: {.paper-citation}
**Wong MK, et al.** *J Clin Oncol.* 2025;43:3589–3599.  
doi: 10.1200/JCO-25-01346
:::

::: {.link-row}
[DOI](https://doi.org/10.1200/JCO-25-01346){.soco-link}
:::

::::

IGNYTE enrolled 140 patients with advanced melanoma and confirmed progression on prior anti–PD-1 therapy. RP1 was administered intratumorally with nivolumab. By RECIST 1.1 independent central review, the confirmed objective response rate was **32.9%**, including **15.0% complete responses**. Median duration of response was **33.7 months**; 1- and 2-year overall survival were **75.3%** and **63.3%**, respectively. Responses were observed in both injected and noninjected lesions, including visceral sites.

::: {.question-card}
**The question beneath the paper:** When an intratumoral agent is combined with continued PD-1 blockade in a single-arm trial, what exactly has been demonstrated — local activity, systemic activity, contribution of RP1, activity of the combination, or some mixture of all four?
:::


::: {.context-note}
**Regulatory context mattered.** The meeting took place during active uncertainty around RP1's regulatory path. The preserved Journal Club presentation reviewed the July 22, 2025 FDA complete response letter, including concerns about whether IGNYTE constituted an adequate and well-controlled investigation, heterogeneity of the study population, and contribution of components. No safety concern was identified in the sponsor's description of that letter.
:::


::: {.section-kicker}
Before the discussion
:::

## The survey revealed a group that liked the signal — but not the certainty

::: {.section-intro}
There is no preserved transcript from this session, so the most durable record of the group's starting position is the pre-Journal Club survey. The responses were unusually useful because they separated biological plausibility from inferential and regulatory sufficiency.
:::

::: {.survey-grid}

::: {.survey-card}
[75%]{.survey-value}
[Familiar with IGNYTE]{.survey-label}

::: {.survey-copy}
Three quarters of respondents were already moderately or very familiar with the IGNYTE study before the session, and 94% reported prior clinical use of an intratumoral melanoma therapy.
:::
:::

::: {.survey-card}
[56%]{.survey-value}
[Single-arm evidence can persuade]{.survey-label}

::: {.survey-copy}
The most common view was that single-arm studies can be persuasive when results substantially exceed historical expectations. Only 12% said such evidence is often sufficient on its own for clinical decision-making.
:::
:::

::: {.survey-card}
[56%]{.survey-value}
[ORR meaningful — but insufficient alone]{.survey-label}

::: {.survey-copy}
Most respondents considered objective response rate moderately clinically meaningful in PD-1–refractory melanoma but not sufficient by itself. Another 25% considered it highly meaningful when responses are durable.
:::
:::

::: {.survey-card}
[69%]{.survey-value}
[Biology looked plausible]{.survey-label}

::: {.survey-copy}
Sixty-nine percent rated the proposed systemic immune mechanism as either highly plausible or plausible but still somewhat uncertain. The remaining 31% called it possible but not strongly supported.
:::
:::

::: {.survey-card}
[65%]{.survey-value}
[Single-arm design was the leading limitation]{.survey-label}

::: {.survey-copy}
The single-arm design was the most commonly selected limitation, followed by uncertainty about the contribution of RP1 versus nivolumab (41%) and interpretation of injected versus noninjected lesions (29%).
:::
:::

::: {.survey-card}
[53%]{.survey-value}
[Preferred randomized add-on design]{.survey-label}

::: {.survey-copy}
A majority selected randomization of RP1 plus nivolumab versus nivolumab alone as the most convincing confirmatory design. Another 27% preferred randomization against physician's choice.
:::
:::

:::



<div class="survey-disclosure">

<button
  type="button"
  class="survey-toggle"
  id="survey-toggle"
  aria-expanded="false"
  aria-controls="full-survey-panel">

  <span class="survey-toggle-badge">▤</span>

  <span class="survey-toggle-copy">
    <strong>Explore the full pre-meeting survey</strong>
    <span>Open all survey figures and the final open-text uncertainty responses.</span>
  </span>

  <span class="survey-toggle-icon">+</span>

</button>

</div>

<div id="full-survey-panel" class="survey-panel">

<p class="survey-panel-intro">
These are the archived <strong>pre-discussion</strong> responses. They are intentionally tucked away so the recap can stay readable while preserving the full survey record for anyone who wants to inspect it.
</p>

```{r}
#| label: full-survey-results
#| echo: false
#| message: false
#| warning: false
#| results: asis
#| fig-width: 10
#| fig-height: 5.6
#| dpi: 120

if (!survey_available) {

  cat(
    '<p style="color:#6B747B;">',
    'Archived survey files were not found in the expected meeting folder.',
    '</p>'
  )

} else {

  survey_ids <- paste0(
    "q",
    seq_len(min(19, length(survey_question_map)))
  )

  for (i in seq_along(survey_ids)) {

    qid <- survey_ids[i]
    qinfo <- survey_question_map[[qid]]

    p <- tryCatch(
      plot_question(
        qinfo,
        survey_clean,
        survey_checkbox_data,
        dict_path = survey_dict_path,
        title_width = 72,
        x_label_width = 48,
        y_breaks = 1,
        title_size = 14,
        title_margin = ggplot2::margin(0, 0, 10, 0)
      ),
      error = function(e) NULL
    )

    if (!is.null(p)) {

      if (length(p$layers) >= 1) {
        p$layers[[1]]$aes_params$fill <- "#168A8F"
      }

      p <- p +
        ggplot2::theme_minimal(base_size = 11) +
        ggplot2::theme(
          plot.title = ggplot2::element_text(
            color = "#082D4D",
            face = "bold",
            size = 14,
            hjust = 0,
            margin = ggplot2::margin(0,0,8,0)
          ),
          plot.subtitle = ggplot2::element_text(
            color = "#6B747B",
            size = 10,
            hjust = 0
          ),
          axis.title.x = ggplot2::element_blank(),
          axis.title.y = ggplot2::element_text(
            color = "#6B747B",
            size = 9
          ),
          axis.text = ggplot2::element_text(
            color = "#405463",
            size = 9
          ),
          panel.grid.major.y = ggplot2::element_blank(),
          panel.grid.minor = ggplot2::element_blank(),
          plot.margin = ggplot2::margin(8, 18, 8, 8)
        )

      cat(
        paste0(
          '<div class="survey-question-label">',
          'Question ', i,
          '</div>'
        )
      )

      print(p)

      cat('<hr class="survey-figure-separator">')
    }
  }

  if ("key_uncertainty" %in% names(survey_clean)) {

    open_text <- survey_clean |>
      dplyr::filter(
        !is.na(key_uncertainty),
        stringr::str_squish(key_uncertainty) != ""
      ) |>
      dplyr::transmute(
        uncertainty = stringr::str_squish(key_uncertainty)
      )

    if (nrow(open_text) > 0) {

      cat(
        '<div class="survey-question-label">',
        'Open-text responses',
        '</div>',
        '<div class="survey-text-list">'
      )

      for (response in open_text$uncertainty) {
        cat(
          '<div class="survey-text-item">',
          htmltools::htmlEscape(response),
          '</div>'
        )
      }

      cat('</div>')
    }
  }
}
```

</div>

<script>
document.addEventListener("DOMContentLoaded", function () {
  const button = document.getElementById("survey-toggle");
  const panel = document.getElementById("full-survey-panel");

  if (!button || !panel) return;

  button.addEventListener("click", function () {
    const isOpen = button.getAttribute("aria-expanded") === "true";

    button.setAttribute(
      "aria-expanded",
      isOpen ? "false" : "true"
    );

    panel.classList.toggle(
      "is-open",
      !isOpen
    );
  });
});
</script>


::: {.section-kicker}
The inferential problem
:::

## The meeting became a primer on estimands

::: {.section-intro}
A substantial part of the session focused on a concept that was unfamiliar to much of the room: the **ICH E9(R1) estimand framework**. The point was not statistical terminology for its own sake. It was to force the clinical question to become explicit **before** choosing the analysis.
:::

:::: {.estimand-primer}

::: {.estimand-primer-title}
Estimand → estimator → estimate
:::

::: {.estimand-primer-copy}
The presentation separated three ideas that are easy to blur together: first define the treatment effect we want to learn, then choose the statistical method that can estimate it, and only then interpret the numerical result.
:::

::: {.estimand-flow}

::: {.estimand-step}
**Estimand**
[What treatment effect are we trying to learn?]{}
:::

::: {.estimand-arrow}
→
:::

::: {.estimand-step}
**Estimator**
[What statistical method will estimate that effect?]{}
:::

::: {.estimand-arrow}
→
:::

::: {.estimand-step}
**Estimate**
[What numerical result do we obtain?]{}
:::

:::

::: {.estimand-components}

::: {.estimand-component}
1 · Population
:::

::: {.estimand-component}
2 · Endpoint
:::

::: {.estimand-component}
3 · Intercurrent events
:::

::: {.estimand-component}
4 · Summary measure
:::

:::

::: {.estimand-contrast}

::: {.estimand-box .local}
### Local estimand
**Question:** what is the effect on lesions that are directly injected?

The endpoint can reflect the combined procedural and biologic effect of the intratumoral intervention.
:::

::: {.estimand-box .systemic}
### Systemic estimand
**Question:** what is the effect on lesions that remain uninjected?

Response in uninjected — particularly visceral — lesions provides a different kind of evidence about systemic antitumor activity.
:::

:::

::: {.component-estimand}
**And IGNYTE had a second estimand problem:** RP1 was given with nivolumab. Even if the combination is active, the observed response does not by itself answer how much activity is attributable to RP1, nivolumab, or their interaction. A randomized add-on contrast — **nivolumab versus nivolumab + RP1** — asks that component question much more directly.
:::

::::


## The inferential questions we kept returning to

::: {.highlight-grid}

::: {.highlight-card}
[01 · Where?]{.highlight-num}

### Local effect or systemic effect?

Injected lesions are directly exposed to the intervention. Their shrinkage can demonstrate local antitumor activity, but it does not by itself establish a systemic treatment effect. Noninjected lesions therefore carry special interpretive weight when the intended claim is systemic benefit.
:::

::: {.highlight-card}
[02 · What caused it?]{.highlight-num}

### RP1, nivolumab, or the combination?

Because RP1 was administered with nivolumab and there was no randomized component comparison, the observed response cannot cleanly identify the contribution of RP1. The survey recognized this: 41% selected unclear contribution of components as a primary limitation.
:::

::: {.highlight-card}
[03 · Compared with what?]{.highlight-num}

### Historical expectations are useful — and fragile

The paper contextualized the observed ORR against low expected activity from continued anti–PD-1 therapy. The survey showed clinicians are open to that logic when the observed result substantially exceeds historical expectations, while also worrying about population heterogeneity and external validity.
:::

::: {.highlight-card}
[04 · What endpoint?]{.highlight-num}

### ORR is informative, but its meaning depends on the question

The study's 32.9% RECIST response rate was clinically interesting, particularly with a median DOR of 33.7 months. But the group entered the discussion largely unwilling to treat ORR alone as the whole evidentiary story.
:::

::: {.highlight-card}
[05 · What estimand?]{.highlight-num}

### The clinical question should precede the estimator

The ICH E9(R1) framework became an organizing language for the discussion. Most respondents entered the session with little or no familiarity with estimands, so the meeting became both a critique of IGNYTE and a practical lesson in defining the treatment effect before debating the estimator or the numerical result.
:::

::: {.highlight-card}
[06 · What would settle it?]{.highlight-num}

### Randomization was the clearest path forward

When asked what confirmatory design would be most convincing, the strongest preference was an add-on comparison of nivolumab versus nivolumab + RP1. That design directly targets the contribution-of-components question that the single-arm study cannot resolve.
:::

:::


::: {.discussion-quote}
A response rate can be impressive and still leave the central causal question unresolved. For intratumoral combination therapy, **where the response occurs and what comparison generated it are part of the treatment effect — not merely details of the analysis.**
:::


### Where the discussion appears to have landed

Without a transcript, we should be careful not to recreate individual comments that were not preserved. But the survey and presentation materials point to a clear intellectual center of gravity.

The **clinical signal was taken seriously**. A 32.9% response rate, 15% complete-response rate, long duration of response, activity in noninjected and visceral lesions, and a comparatively favorable safety profile made RP1 + nivolumab difficult to dismiss as biologically uninteresting.

At the same time, **interest in the therapy did not equal certainty about the inference**. The single-arm design, patient heterogeneity, lesion-level interpretation, and inability to isolate the contribution of RP1 remained central problems. The estimand framework gave the group a useful way to separate those concerns: *Where is the treatment effect being claimed? What outcome defines it? What happens when lesion roles change? And what causal contrast would actually isolate RP1's contribution?* The survey's open-text responses repeatedly returned to the same themes: attribution of systemic benefit, contribution of components, comparability with historical controls, and the limitations of the single-arm design.

The most defensible landing point was therefore not “the study worked” or “the study failed.” It was that **IGNYTE generated a compelling therapeutic signal whose regulatory and causal interpretation depended on questions the study design could not fully answer.**


::: {.section-kicker}
Practice threshold
:::

## Regulatory sufficiency and clinical adoption were not the same question

::: {.survey-grid}

::: {.survey-card}
[38%]{.survey-value}
[Possibly approval-ready with postmarketing evidence]{.survey-label}

::: {.survey-copy}
The largest group thought IGNYTE could possibly support FDA approval if accompanied by postmarketing requirements. Another 25% were uncertain, 19% viewed the evidence as sufficient for accelerated approval, and 12% thought randomized data were probably still needed.
:::
:::

::: {.survey-card}
[40%]{.survey-value}
[FDA approval would be enough for routine use]{.survey-label}

::: {.survey-copy}
When the question shifted from regulatory approval to personal practice, 40% said FDA approval would be sufficient, while only 13% said the current evidence was already enough for routine use.
:::
:::

:::

::: {.source-note}
**About this recap:** no meeting transcript was available for the April 6 session. This page therefore summarizes the published IGNYTE paper, the preserved SoCO presentation, the pre-meeting survey, and the Teams attendance record. It intentionally avoids attributing discussion positions to individual attendees unless they are preserved in those materials.
:::


::: {.section-kicker}
Our community
:::

## Who joined us?

:::: {.community-banner}

::: {.community-banner-kicker}
Our community
:::

::: {.community-banner-title}
Who’s in the room today?
:::

::: {.community-banner-copy}
The Teams record gives us a useful snapshot of participation: how long people stayed, whether they appeared on camera, whether they unmuted, and whether they raised a hand. None of those signals measures the quality of a contribution—but together they can give us a light-touch view of recorded engagement.
:::

::::

```{r}
#| label: engagement-standouts
#| results: asis

meeting_max <- max(people$duration_min, na.rm = TRUE)

# -------------------------------------------------------------------------
# Moderator discussion bonus
#
# This is intentionally easy to edit after the meeting.
# "pattern" is matched against the cleaned Teams display name.
#
# A 25-point bonus is intentionally meaningful without overwhelming the
# objective Teams-derived component. Teams can tell us who was present and who
# triggered certain interface signals, but it cannot tell us who materially
# advanced the live scientific discussion.
# -------------------------------------------------------------------------

discussion_bonus_rules <- tibble::tribble(
  ~pattern,                 ~discussion_bonus,
  "^Don Lawrence$",         25,
  "^Vern Sondak$",          25,
  "^David M\\. Miller$",    25
)

get_discussion_bonus <- function(person_name) {

  matched <- discussion_bonus_rules |>
    dplyr::filter(
      stringr::str_detect(
        person_name,
        stringr::regex(
          pattern,
          ignore_case = TRUE
        )
      )
    )

  if (nrow(matched) == 0) {
    return(0)
  }

  max(matched$discussion_bonus)
}

engagement <- people |>
  mutate(
    attendance_fraction = pmin(duration_min / meeting_max, 1),

    # Objective Teams-derived component: maximum 100 points.
    recorded_engagement =
      55 * attendance_fraction +
      15 * as.numeric(any_camera) +
      20 * as.numeric(any_unmute) +
      10 * as.numeric(any_hand_raise),

    # Moderator-entered component: captures substantive live discussion that
    # Teams telemetry does not measure.
    discussion_bonus = purrr::map_dbl(
      Name,
      get_discussion_bonus
    ),

    engagement_score =
      recorded_engagement +
      discussion_bonus
  ) |>
  arrange(
    desc(engagement_score),
    desc(discussion_bonus),
    desc(duration_min),
    Name
  )

top_engagement <- engagement |>
  slice_head(n = 5)

pill_html <- paste0(
  '<div class="engagement-pill">',
  top_engagement$Name,
  '</div>',
  collapse = ""
)

cat(
  paste0(
    '<div class="engagement-spotlight">',
      '<div class="engagement-spotlight-title">🏅 Engagement standouts</div>',
      '<p class="engagement-spotlight-copy">',
        'A small thank-you to five colleagues who stood out in the April discussion.',
      '</p>',
      '<div class="engagement-pill-row">',
        pill_html,
      '</div>',
      '<p class="engagement-method">',
        'The ranking combines time present and recorded Teams signals with a moderator-entered discussion bonus for substantive participation that Teams cannot capture. ',
        'It is meant as recognition, not as a formal measure of contribution quality.',
      '</p>',
    '</div>'
  )
)
```

::: {.section-intro}
Teams reconnects are reconciled before display. The shared conference-room connection is shown as **Replimune team**, and abbreviated attendee names are normalized in the attendance-processing script. The full table remains below so the underlying signals are transparent.
:::

```{r}
#| label: attendance-table
#| results: asis

library(dplyr)

roster <- people |>
  transmute(
    Name,
    Minutes = round(duration_min),
    Camera = if_else(any_camera, "●", "—"),
    Unmuted = if_else(any_unmute, "●", "—"),
    `Raised hand` = if_else(any_hand_raise, "●", "—")
  ) |>
  arrange(desc(Minutes), Name)

cat(
  paste0(
    '<div class="roster-summary">',
      '<strong>', nrow(roster), ' attendee/team connections represented</strong>',
      '<span>Sorted by time in meeting · ● indicates the Teams signal was recorded at least once</span>',
    '</div>'
  )
)

min_minutes <- min(roster$Minutes, na.rm = TRUE)
max_minutes <- max(roster$Minutes, na.rm = TRUE)

minute_fill <- function(x) {
  if (max_minutes == min_minutes) return("rgba(40,169,162,.18)")
  alpha <- 0.06 + 0.28 * ((x - min_minutes) / (max_minutes - min_minutes))
  sprintf("rgba(40,169,162,%.3f)", alpha)
}

cat('<div class="attendance-scroll">')
cat('<table class="attendance-table">')
cat(
  '<thead><tr>',
  '<th>Name</th>',
  '<th>Minutes</th>',
  '<th>Camera</th>',
  '<th>Unmuted</th>',
  '<th>Raised hand</th>',
  '</tr></thead><tbody>'
)

for (i in seq_len(nrow(roster))) {

  row <- roster[i, ]

  signal_cell <- function(value) {
    cls <- if (identical(value, "●")) " signal-on" else ""
    paste0('<td class="signal-cell', cls, '">', value, '</td>')
  }

  cat(
    '<tr>',
      '<td class="name-cell">', htmltools::htmlEscape(row$Name), '</td>',
      '<td class="minutes-cell" style="background:', minute_fill(row$Minutes), ';">',
        row$Minutes,
      '</td>',
      signal_cell(row$Camera),
      signal_cell(row$Unmuted),
      signal_cell(row$`Raised hand`),
    '</tr>'
  )
}

cat('</tbody></table></div>')
```


::: {.attendance-note}
Participation signals are descriptive only. Camera use, unmuting, and hand raises do not measure the quality or depth of participation.
:::


:::: {.updates-wrap}

::: {.section-kicker}
Relevant updates
:::

## What happened after the April discussion

::: {.updates-intro}
This recap preserves the questions the group was asking on April 6. The regulatory story continued to evolve rapidly afterward—and several of the issues debated in Journal Club became central to the subsequent FDA review.
:::

::: {.updates-timeline}

:::: {.updates-item}

::: {.updates-date}
April 10, 2026
:::

::: {.updates-card}
### FDA issued a second Complete Response Letter

Four days after this Journal Club, FDA again declined to approve the RP1 biologics license application. The regulatory questions around the interpretability of the single-arm IGNYTE data remained unresolved.

::: {.updates-links}
[FDA / regulatory history](https://ir.replimune.com/press-releases){.updates-link}
:::

:::

::::


:::: {.updates-item}

::: {.updates-date}
July 30, 2026
:::

::: {.updates-card}
### FDA advisory committee voted 10–3 in favor

The Cellular, Tissue, and Gene Therapies Advisory Committee voted **10 to 3** that the efficacy results from IGNYTE were evaluable and clinically meaningful. The discussion centered on many of the same questions raised here: reliability of the single-arm evidence, durability, systemic activity, and attribution of benefit to RP1.

::: {.updates-links}
[Advisory committee outcome](https://ir.replimune.com/news-releases/news-release-details/replimune-announces-favorable-outcome-fdas-cellular-tissue-and){.updates-link}
:::

:::

::::


:::: {.updates-item .approval}

::: {.updates-date}
August 6, 2026
:::

::: {.updates-card}
### FDA granted accelerated approval

FDA granted accelerated approval to **vusolimogene oderparepvec-wtpg (Tudriqev; formerly RP1) plus nivolumab** for adults with unresectable advanced cutaneous melanoma whose disease progressed on a PD-1–blocking antibody-based regimen. The approval was based on objective response rate and duration of response and remains subject to confirmatory evidence requirements.

::: {.updates-links}
[FDA approval announcement](https://www.fda.gov/drugs/resources-information-approved-drugs/fda-grants-accelerated-approval-vusolimogene-oderparepvec-wtpg-combination-nivolumab-melanoma){.updates-link}
:::

:::

::::


:::: {.updates-item}

::: {.updates-date}
August 7, 2026
:::

::: {.updates-card}
### “Persuaded, Not Certain”

The subsequent *Journal of Cutaneous Oncology* editorial reflects on the advisory committee review and the tension that defined this Journal Club as well: a clinically persuasive signal can justify action while important inferential uncertainty remains.

::: {.updates-links}
[Read the editorial](https://doi.org/10.59449/joco.2026.08.07){.updates-link}
:::

:::

::::

:::

::: {.updates-reflection}
**In retrospect:** the April discussion was unusually prescient. The distinction between *persuasion* and *certainty*—and the need to specify exactly what treatment effect IGNYTE established—became the central regulatory question over the months that followed.
:::

::::


::: {.footer-card}

## A useful disagreement about evidence

This Journal Club was less about deciding whether RP1 was interesting than about deciding **what evidence is necessary to know why a treatment appears to work, how broadly the result applies, and when a promising signal becomes an actionable treatment effect.**

:::

::: {.link-row}
[Back to Journal Club](../../jc.qmd){.soco-link}
[Read the article](https://doi.org/10.1200/JCO-25-01346){.soco-link .secondary}
:::
