---
title: "Community Highlights"
pagetitle: "Community Highlights | Society of Cutaneous Oncology"
description: "Recognition of the clinicians, researchers, trainees, and industry collaborators who have participated in tracked Society of Cutaneous Oncology Journal Clubs and Research Forums."
page-layout: full
title-block-style: none
toc: false
---

<style>
:root {
  --soco-navy:#041b33;
  --soco-blue:#06436e;
  --soco-teal:#0f7f86;
  --soco-coral:#ff3b3f;
  --soco-ink:#18293d;
  --soco-muted:#5c6f82;
  --soco-surface:#f6fafb;
  --soco-line:#dbe8ee;
  --soco-pale:#eef8f7;
}

#title-block-header,
.quarto-title-block,
.quarto-title,
.quarto-title-meta {
  display:none !important;
}

html, body {
  max-width:100%;
  overflow-x:hidden;
}

body {
  background:#fff;
}

main.content {
  max-width:100%;
  padding-top:0 !important;
}

.ch-wrap {
  max-width:1160px;
  margin:0 auto;
  padding:0 1.5rem;
}

.ch-hero {
  max-width:1320px;
  margin:3rem auto 0;
  padding:0 1.5rem;
}

.ch-hero-inner {
  position:relative;
  overflow:hidden;
  padding:clamp(2.8rem,5vw,4.7rem);
  border:1px solid var(--soco-line);
  border-radius:1.2rem;
  background:
    radial-gradient(circle at 88% 15%,rgba(15,127,134,.14),transparent 29%),
    radial-gradient(circle at 12% 88%,rgba(255,59,63,.05),transparent 30%),
    linear-gradient(135deg,#fff 0%,#f5faf9 100%);
  box-shadow:0 22px 60px rgba(4,27,51,.07);
}

.ch-hero-inner::after {
  content:"";
  position:absolute;
  width:380px;
  height:380px;
  top:-100px;
  right:-75px;
  opacity:.22;
  background-image:radial-gradient(circle,rgba(15,127,134,.75) 0 1.3px,transparent 2px);
  background-size:30px 30px;
  mask-image:radial-gradient(circle,#000 0%,transparent 72%);
  -webkit-mask-image:radial-gradient(circle,#000 0%,transparent 72%);
  pointer-events:none;
}

.ch-eyebrow {
  position:relative;
  z-index:1;
  color:var(--soco-teal);
  font-size:.78rem;
  font-weight:850;
  letter-spacing:.13em;
  text-transform:uppercase;
}

.ch-hero h1 {
  position:relative;
  z-index:1;
  max-width:900px;
  margin:.55rem 0 .9rem;
  color:var(--soco-navy);
  font-size:clamp(3rem,5vw,4.8rem);
  line-height:.98;
  letter-spacing:-.055em;
}

.ch-hero p {
  position:relative;
  z-index:1;
  max-width:860px;
  margin:0;
  color:#4d6170;
  font-size:1.12rem;
  line-height:1.72;
}

.ch-accent {
  position:relative;
  z-index:1;
  width:94px;
  height:5px;
  margin-top:1.5rem;
  border-radius:99px;
  background:linear-gradient(90deg,var(--soco-teal) 0 68%,var(--soco-coral) 68%);
}

.ch-note {
  margin:2rem 0 0;
  padding:1rem 1.15rem;
  border-left:4px solid var(--soco-teal);
  border-radius:.8rem;
  background:var(--soco-pale);
  color:#40586a;
  line-height:1.62;
}

.ch-section {
  margin-top:5rem;
}

.ch-section-head {
  max-width:850px;
  margin-bottom:1.7rem;
}

.ch-section h2 {
  margin:.25rem 0 .75rem;
  color:var(--soco-navy);
  font-size:clamp(2rem,3.4vw,3rem);
  letter-spacing:-.04em;
}

.ch-section-head p {
  margin:0;
  color:var(--soco-muted);
  font-size:1.04rem;
  line-height:1.72;
}

.ch-convener-note {
  margin-top:1rem;
  padding:.82rem 1rem;
  border-left:3px solid var(--soco-teal);
  border-radius:.6rem;
  background:#f7fbfb;
  color:#536979;
  font-size:.9rem;
  line-height:1.55;
}

.ch-convener-line {
  display:flex;
  flex-wrap:wrap;
  align-items:baseline;
  gap:.3rem .55rem;
  margin-bottom:.16rem;
}

.ch-convener-label {
  color:var(--soco-teal-dark);
  font-size:.72rem;
  font-weight:800;
  letter-spacing:.07em;
  text-transform:uppercase;
}

.ch-convener-name {
  color:var(--soco-navy);
  font-weight:800;
}

.ch-convener-copy {
  color:#617584;
}

@media (max-width: 640px) {
  .ch-convener-line {
    display:block;
  }

  .ch-convener-label {
    display:block;
    margin-bottom:.12rem;
  }
}

.ch-metrics {
  display:grid;
  grid-template-columns:repeat(4,minmax(0,1fr));
  gap:1rem;
  margin-top:1.5rem;
}

.ch-metric {
  padding:1.35rem 1.35rem;
  border:1px solid var(--soco-line);
  border-radius:1rem;
  background:#fff;
  box-shadow:0 8px 22px rgba(4,27,51,.05);
}

.ch-metric-label {
  color:var(--soco-muted);
  font-size:.72rem;
  font-weight:800;
  letter-spacing:.09em;
  text-transform:uppercase;
}

.ch-metric-value {
  margin:.25rem 0;
  color:var(--soco-navy);
  font-size:2.2rem;
  font-weight:850;
  line-height:1;
}

.ch-metric-note {
  color:#6a7985;
  font-size:.83rem;
  line-height:1.45;
}

.ch-rollcall {
  display:flex;
  flex-wrap:wrap;
  gap:.55rem;
  margin-top:1.25rem;
}

.ch-name-chip {
  padding:.52rem .72rem;
  border:1px solid var(--soco-line);
  border-radius:999px;
  background:#fff;
  color:#3f5566;
  font-size:.83rem;
  font-weight:650;
}

.ch-leaderboard {
  display:grid;
  gap:.8rem;
  margin-top:1.4rem;
}

.ch-person {
  display:grid;
  grid-template-columns:minmax(0,1fr) auto;
  gap:1rem;
  align-items:center;
  padding:1rem 1.1rem;
  border:1px solid var(--soco-line);
  border-radius:.95rem;
  background:#fff;
}

.ch-person-name {
  min-width:0;
  color:var(--soco-navy);
  font-weight:800;
}

.ch-meeting-count {
  display:flex;
  align-items:baseline;
  gap:.35rem;
  white-space:nowrap;
  color:var(--soco-muted);
}

.ch-meeting-count-value {
  color:var(--soco-navy);
  font-size:1.35rem;
  font-weight:850;
  line-height:1;
}

.ch-meeting-count-label {
  font-size:.78rem;
  font-weight:700;
}

.ch-industry-grid {
  display:grid;
  grid-template-columns:repeat(2,minmax(0,1fr));
  gap:1rem;
  margin-top:1.4rem;
}

.ch-industry-card {
  padding:1.35rem 1.4rem;
  border:1px solid rgba(15,127,134,.26);
  border-radius:1rem;
  background:linear-gradient(135deg,#eef8f7,#fff);
}

.ch-industry-card h3 {
  margin:0 0 .45rem;
  color:var(--soco-navy);
}

.ch-industry-meta {
  margin-bottom:.9rem;
  color:var(--soco-muted);
  font-size:.84rem;
}

.ch-industry-names {
  display:flex;
  flex-wrap:wrap;
  gap:.45rem;
}

.ch-industry-name {
  padding:.45rem .62rem;
  border:1px solid rgba(15,127,134,.22);
  border-radius:999px;
  background:rgba(255,255,255,.88);
  color:#415b6a;
  font-size:.79rem;
  font-weight:650;
}

.ch-meeting-grid {
  display:grid;
  grid-template-columns:repeat(2,minmax(0,1fr));
  gap:1rem;
  margin-top:1.35rem;
}

.ch-meeting {
  display:block;
  position:relative;
  padding:1rem 3rem 1rem 1.1rem;
  border:1px solid var(--soco-line);
  border-radius:.9rem;
  background:var(--soco-surface);
  color:inherit !important;
  text-decoration:none !important;
  transition:
    transform .15s ease,
    border-color .15s ease,
    box-shadow .15s ease,
    background .15s ease;
}

.ch-meeting::after {
  content:"→";
  position:absolute;
  right:1.05rem;
  top:50%;
  transform:translateY(-50%);
  color:var(--soco-teal-dark);
  font-size:1.05rem;
  font-weight:800;
}

.ch-meeting:hover,
.ch-meeting:focus-visible {
  transform:translateY(-2px);
  border-color:rgba(22,138,143,.42);
  background:#eef8f7;
  box-shadow:0 10px 24px rgba(4,27,51,.06);
  text-decoration:none !important;
}

.ch-meeting:focus-visible {
  outline:3px solid rgba(40,169,162,.24);
  outline-offset:2px;
}

.ch-meeting-type {
  color:var(--soco-teal);
  font-size:.7rem;
  font-weight:850;
  letter-spacing:.08em;
  text-transform:uppercase;
}

.ch-meeting-title {
  margin:.22rem 0 .45rem;
  color:var(--soco-navy);
  font-weight:780;
}

.ch-meeting-meta {
  color:var(--soco-muted);
  font-size:.82rem;
}



/* ============================================================
   COMMUNITY ROSTER
   ============================================================ */

.ch-roster-details {
  margin-top:1.3rem;
  overflow:hidden;
  border:1px solid var(--soco-line);
  border-radius:1rem;
  background:#fff;
  box-shadow:0 8px 22px rgba(4,27,51,.04);
}

.ch-roster-details > summary {
  position:relative;
  min-height:64px;
  padding:1rem 3.4rem 1rem 1.15rem;
  cursor:pointer;
  list-style:none;
  background:linear-gradient(135deg,#f3f8f8 0%,#fff 100%);
  color:var(--soco-navy);
}

.ch-roster-details > summary::-webkit-details-marker {
  display:none;
}

.ch-roster-details > summary::after {
  content:"+";
  position:absolute;
  right:1.15rem;
  top:50%;
  transform:translateY(-50%);
  color:var(--soco-teal-dark);
  font-size:1.65rem;
  font-weight:500;
  line-height:1;
}

.ch-roster-details[open] > summary::after {
  content:"−";
}

.ch-roster-summary-title {
  display:block;
  color:var(--soco-navy);
  font-size:1rem;
  font-weight:850;
}

.ch-roster-summary-subtitle {
  display:block;
  margin-top:.18rem;
  color:var(--soco-muted);
  font-size:.82rem;
  line-height:1.45;
}

.ch-roster-note {
  padding:.9rem 1.05rem;
  border-top:1px solid var(--soco-line);
  background:#fbfdfd;
  color:#607381;
  font-size:.82rem;
  line-height:1.55;
}

.ch-roster-group {
  padding:1.05rem;
  border-top:1px solid var(--soco-line);
}

.ch-roster-group:first-of-type {
  border-top:0;
}

.ch-roster-group h3 {
  margin:0 0 .8rem;
  color:var(--soco-navy);
  font-size:1rem;
  font-weight:850;
}

.ch-roster-columns {
  display:grid;
  grid-template-columns:repeat(2,minmax(0,1fr));
  gap:1rem;
  align-items:start;
}

.ch-roster-table-wrap {
  width:100%;
  min-width:0;
  overflow:hidden;
  border:1px solid #e2ecef;
  border-radius:.78rem;
  background:#fff;
}

.ch-roster-table {
  width:100%;
  margin:0;
  border-collapse:collapse;
  table-layout:fixed;
  font-size:.79rem;
}

.ch-roster-table th,
.ch-roster-table td {
  padding:.62rem .7rem;
  border-bottom:1px solid #e6eeee;
  vertical-align:top;
  text-align:left;
}

.ch-roster-table th {
  background:#eef8f7;
  color:var(--soco-navy);
  font-size:.7rem;
  font-weight:850;
  letter-spacing:.035em;
  text-transform:uppercase;
}

.ch-roster-table th:first-child,
.ch-roster-table td:first-child {
  width:42%;
}

.ch-roster-table td:first-child {
  color:var(--soco-navy);
  font-weight:780;
}

.ch-roster-table tbody tr:nth-child(even) {
  background:#fbfdfd;
}

.ch-roster-table tbody tr:last-child td {
  border-bottom:0;
}

.ch-roster-affiliation {
  color:#526a79;
  overflow-wrap:anywhere;
}

/* ============================================================
   COLLAPSIBLE ATTENDANCE QC MATRIX
   ============================================================ */

.ch-qc-details {
  margin-top:1.4rem;
  overflow:hidden;
  border:1px solid var(--soco-line);
  border-radius:1rem;
  background:#fff;
  box-shadow:0 8px 22px rgba(4,27,51,.04);
}

.ch-qc-details > summary {
  position:relative;
  display:flex;
  align-items:center;
  justify-content:space-between;
  gap:1rem;
  min-height:64px;
  padding:1rem 3.4rem 1rem 1.15rem;
  cursor:pointer;
  list-style:none;
  background:linear-gradient(135deg,#f3f8f8 0%,#fff 100%);
  color:var(--soco-navy);
}

.ch-qc-details > summary::-webkit-details-marker {
  display:none;
}

.ch-qc-details > summary::after {
  content:"+";
  position:absolute;
  right:1.15rem;
  top:50%;
  transform:translateY(-50%);
  color:var(--soco-teal-dark);
  font-size:1.65rem;
  font-weight:500;
  line-height:1;
}

.ch-qc-details[open] > summary::after {
  content:"−";
}

.ch-qc-summary-copy {
  min-width:0;
}

.ch-qc-summary-title {
  display:block;
  color:var(--soco-navy);
  font-size:1rem;
  font-weight:850;
}

.ch-qc-summary-subtitle {
  display:block;
  margin-top:.18rem;
  color:var(--soco-muted);
  font-size:.82rem;
  line-height:1.45;
}

.ch-qc-note {
  padding:.9rem 1.05rem;
  border-top:1px solid var(--soco-line);
  background:#fbfdfd;
  color:#607381;
  font-size:.82rem;
  line-height:1.55;
}

.ch-qc-table-wrap {
  width:100%;
  max-width:100%;
  overflow-x:auto;
  overflow-y:visible;
  -webkit-overflow-scrolling:touch;
  overscroll-behavior-x:contain;
  border-top:1px solid var(--soco-line);
}

.ch-qc-table {
  width:max-content;
  min-width:100%;
  margin:0;
  border-collapse:separate;
  border-spacing:0;
  font-size:.76rem;
}

.ch-qc-table th,
.ch-qc-table td {
  min-width:152px;
  padding:.68rem .72rem;
  border-right:1px solid #e6eeee;
  border-bottom:1px solid #e6eeee;
  vertical-align:middle;
  text-align:center;
}

.ch-qc-table thead th {
  position:sticky;
  top:0;
  z-index:3;
  background:#eef8f7;
  color:var(--soco-navy);
  font-weight:800;
}

.ch-qc-table th:first-child,
.ch-qc-table td:first-child {
  position:sticky;
  left:0;
  min-width:210px;
  max-width:210px;
  text-align:left;
}

.ch-qc-table thead th:first-child {
  z-index:5;
  background:#e7f5f4;
}

.ch-qc-table tbody td:first-child {
  z-index:2;
  background:#fff;
  box-shadow:7px 0 12px -12px rgba(4,27,51,.5);
}

.ch-qc-table tbody tr:nth-child(even) td:first-child {
  background:#fbfdfd;
}

.ch-qc-table tbody tr:nth-child(even) td:not(:first-child) {
  background-color:#fbfdfd;
}

.ch-qc-table tbody tr:hover td {
  background-color:#f5fbfa;
}

.ch-qc-table tbody tr:hover td:first-child {
  background:#eef8f7;
}

.ch-qc-person {
  display:block;
  color:var(--soco-navy);
  font-weight:780;
  line-height:1.3;
}

.ch-qc-audience {
  display:block;
  margin-top:.18rem;
  color:#7a8993;
  font-size:.66rem;
  font-weight:650;
  line-height:1.25;
}


.ch-qc-meeting-title {
  display:block;
  max-width:150px;
  margin:0 auto;
  line-height:1.28;
  overflow-wrap:anywhere;
}

.ch-qc-meeting-date {
  display:block;
  margin-top:.22rem;
  color:var(--soco-teal-dark);
  font-size:.68rem;
  font-weight:750;
}


.ch-qc-present {
  background:rgba(40,169,162,.045);
}

.ch-qc-present-label {
  display:inline-flex;
  align-items:center;
  justify-content:center;
  padding:.28rem .52rem;
  border:1px solid rgba(15,127,134,.18);
  border-radius:999px;
  background:#eef8f7;
  color:var(--soco-teal-dark);
  font-size:.69rem;
  font-weight:800;
  letter-spacing:.02em;
}

.ch-qc-absent {
  color:#a8b3ba;
  font-weight:650;
}


@media (max-width:900px) {
  .ch-metrics {
    grid-template-columns:repeat(2,minmax(0,1fr));
  }

  .ch-person {
    grid-template-columns:minmax(0,1fr) auto;
  }
}

@media (max-width:700px) {
  html,
  body,
  main.content {
    width:100%;
    max-width:100%;
    overflow-x:hidden;
  }

  .ch-hero {
    width:100%;
    margin-top:.75rem;
    padding:0 .7rem;
  }

  .ch-hero-inner {
    width:100%;
    min-width:0;
    padding:1.35rem 1rem;
    border-radius:1rem;
  }

  .ch-hero h1 {
    max-width:100%;
    font-size:clamp(2.15rem,10.5vw,3rem);
    line-height:1.01;
    overflow-wrap:anywhere;
  }

  .ch-hero p {
    font-size:1rem;
    line-height:1.58;
  }

  .ch-wrap {
    width:100%;
    max-width:100%;
    padding:0 .7rem;
  }

  .ch-metrics,
  .ch-industry-grid,
  .ch-meeting-grid {
    grid-template-columns:minmax(0,1fr);
  }

  .ch-metric,
  .ch-industry-card,
  .ch-meeting {
    min-width:0;
  }

  .ch-section {
    margin-top:3.25rem;
  }

  .ch-section h2 {
    font-size:clamp(1.8rem,8.3vw,2.35rem);
    line-height:1.05;
  }

  .ch-rollcall {
    gap:.42rem;
  }

  .ch-name-chip,
  .ch-industry-name {
    max-width:100%;
    padding:.46rem .62rem;
    font-size:.78rem;
    overflow-wrap:anywhere;
  }

  .ch-person {
    grid-template-columns:minmax(0,1fr) auto;
    gap:.65rem;
    min-width:0;
    padding:.82rem .75rem;
  }

  .ch-person-name {
    min-width:0;
    overflow-wrap:anywhere;
  }

  .ch-meeting-count {
    gap:.25rem;
  }

  .ch-meeting-count-value {
    font-size:1.15rem;
  }

  .ch-meeting-count-label {
    font-size:.7rem;
  }

  .ch-industry-card h3,
  .ch-meeting-title {
    overflow-wrap:anywhere;
  }

  .ch-qc-details > summary {
    min-height:60px;
    padding:.85rem 3rem .85rem .85rem;
  }

  .ch-qc-summary-title {
    font-size:.92rem;
  }

  .ch-qc-summary-subtitle {
    font-size:.74rem;
  }

  .ch-qc-details > summary::after {
    right:.9rem;
  }

  .ch-qc-note {
    padding:.78rem .85rem;
    font-size:.75rem;
  }

  .ch-qc-table {
    font-size:.69rem;
  }

  .ch-qc-table th,
  .ch-qc-table td {
    min-width:128px;
    padding:.58rem .55rem;
  }

  .ch-qc-table th:first-child,
  .ch-qc-table td:first-child {
    min-width:150px;
    max-width:150px;
  }

  .ch-qc-meeting-title {
    max-width:124px;
  }

  .ch-qc-person {
    font-size:.72rem;
  }

  .ch-qc-audience {
    font-size:.6rem;
  }

  .ch-qc-present-label {
    padding:.24rem .44rem;
    font-size:.64rem;
  }


  .ch-roster-details > summary {
    min-height:60px;
    padding:.85rem 3rem .85rem .85rem;
  }

  .ch-roster-summary-title {
    font-size:.92rem;
  }

  .ch-roster-summary-subtitle,
  .ch-roster-note {
    font-size:.74rem;
  }

  .ch-roster-group {
    padding:.8rem;
  }

  .ch-roster-columns {
    grid-template-columns:minmax(0,1fr);
    gap:.75rem;
  }

  .ch-roster-table {
    width:100%;
    min-width:0;
    font-size:.72rem;
  }

  .ch-roster-table th,
  .ch-roster-table td {
    padding:.55rem .55rem;
  }

  .ch-note {
    padding:.9rem 1rem;
    font-size:.9rem;
  }
}

@media (max-width:430px) {
  .ch-hero {
    padding:0 .5rem;
  }

  .ch-wrap {
    padding:0 .5rem;
  }

  .ch-hero-inner {
    padding:1.15rem .9rem;
  }

  .ch-hero h1 {
    font-size:2.05rem;
  }

  .ch-metric-value {
    font-size:1.9rem;
  }

  .ch-person {
    padding:.78rem .7rem;
  }

  .ch-meeting-count-label {
    font-size:.68rem;
  }
}
</style>

```{r setup}
#| include: false
#| warning: false
#| message: false

suppressPackageStartupMessages({
  library(tidyverse)
  library(htmltools)
})

# ============================================================
# PROJECT ROOT + REGISTRY VIEW
# ============================================================
#
# The persistent SoCO registry is the source of truth for:
#   - identity
#   - current affiliation
#   - event metadata
#   - tracked participation
#
# Community Highlights is now a downstream presentation layer. It no longer
# reparses Teams files or maintains a parallel alias / affiliation system.
# Any attendance or identity correction should be curated upstream in the
# registry and then inherited here on the next render.

find_soco_root <- function(start = getwd(), max_up = 10L) {
  here <- normalizePath(start, winslash = "/", mustWork = TRUE)

  for (i in 0:max_up) {
    if (
      dir.exists(file.path(here, "data", "registry")) &&
      dir.exists(file.path(here, "workflows", "registry"))
    ) {
      return(here)
    }

    parent <- dirname(here)
    if (identical(parent, here)) break
    here <- parent
  }

  stop(
    paste(
      "Could not locate the SoCO project root.",
      "Expected data/registry/ and workflows/registry/ under the same root."
    ),
    call. = FALSE
  )
}

project_root <- find_soco_root()
community_dir <- file.path(project_root, "community_highlights")
output_dir <- file.path(community_dir, "files")

dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)

registry_view_script <- file.path(
  project_root,
  "workflows",
  "registry",
  "R",
  "tools",
  "40_build_registry_views.R"
)

if (!file.exists(registry_view_script)) {
  stop(
    "Could not find registry view helper:\n",
    registry_view_script,
    call. = FALSE
  )
}

source(registry_view_script, local = TRUE)

# Full-program count is intentionally separate from the tracked registry subset.
# Update this single value when a new SoCO meeting occurs.
soco_total_meetings <- 79L


# ============================================================
# DISPLAY HELPERS
# ============================================================

clean_name_key <- function(x) {
  x |>
    as.character() |>
    replace_na("") |>
    str_squish() |>
    str_to_lower() |>
    str_replace_all("[^a-z0-9]", "")
}

format_meeting_date <- function(x) {
  if (length(x) != 1 || is.na(x)) return("")

  paste0(
    format(x, "%B"),
    " ",
    as.integer(format(x, "%d")),
    ", ",
    format(x, "%Y")
  )
}

display_affiliation <- function(x) {
  x <- str_squish(as.character(x))

  case_when(
    is.na(x) | x == "" ~ "—",

    x %in% c(
      "Massachusetts General Hospital",
      "Brigham and Women's Hospital",
      "Mass General Brigham"
    ) ~ "Mass General Brigham",

    x == "Washington University School of Medicine in St. Louis" ~
      "Washington University in St. Louis",

    TRUE ~ x
  )
}

esc <- function(x) htmltools::htmlEscape(as.character(x))


# ============================================================
# REGISTRY-DERIVED TRACKED ATTENDANCE
# ============================================================
#
# event_participation is built centrally by 40_build_registry_views.R.
# It combines canonical identity, event metadata, persistent participation,
# and organization-at-event context. This page therefore does not have to
# reconstruct event/person joins or infer historical employer context itself.

meeting_index <- event_participation |>
  distinct(
    event_id,
    meeting_folder = source_folder,
    meeting_date = event_date,
    meeting_type = event_type,
    meeting_title = event_title
  ) |>
  arrange(
    meeting_date,
    meeting_folder
  )

attendance_long <- event_participation |>
  transmute(
    event_id,
    person_id,
    meeting_folder = source_folder,
    meeting_date = event_date,
    meeting_type = event_type,
    meeting_title = event_title,

    name_key = clean_name_key(name),
    name,
    preferred_name,
    minutes = as.numeric(duration_min),

    audience = if_else(
      sector_at_event == "industry",
      "Industry",
      "Academic / clinical"
    ),

    company = if_else(
      sector_at_event == "industry",
      company_at_event,
      NA_character_
    ),

    # Directory/roster affiliation remains the CURRENT registry affiliation.
    # Historical organization-at-event is used separately for industry cards.
    affiliation_display = display_affiliation(current_affiliation),

    current_title,
    identity_match_method,
    attendance_names_observed,
    participation_source,
    organization_context_source
  )

if (!nrow(attendance_long)) {
  stop("The registry contains no tracked attendance rows.", call. = FALSE)
}

if (
  attendance_long |>
    count(event_id, person_id) |>
    filter(n > 1) |>
    nrow() > 0
) {
  stop(
    "Registry-derived Community Highlights attendance contains duplicate event/person rows.",
    call. = FALSE
  )
}


# ============================================================
# DENOMINATORS
# ============================================================

n_tracked_meetings <- nrow(meeting_index)

n_tracked_jc <- meeting_index |>
  filter(meeting_type == "Journal Club") |>
  nrow()

n_tracked_rf <- meeting_index |>
  filter(meeting_type == "Research Forum") |>
  nrow()


# ============================================================
# ACADEMIC / CLINICAL MEMBER SUMMARY
# ============================================================

academic <- attendance_long |>
  filter(audience == "Academic / clinical")

member_summary <- academic |>
  group_by(
    person_id,
    name_key
  ) |>
  summarise(
    name = first(name),
    meetings_attended = n_distinct(event_id),
    journal_clubs_attended = n_distinct(
      event_id[meeting_type == "Journal Club"]
    ),
    research_forums_attended = n_distinct(
      event_id[meeting_type == "Research Forum"]
    ),
    total_minutes = sum(minutes, na.rm = TRUE),
    affiliation_display = first(affiliation_display),
    .groups = "drop"
  ) |>
  mutate(
    tracked_meeting_attendance_pct =
      if (n_tracked_meetings > 0) {
        100 * meetings_attended / n_tracked_meetings
      } else {
        rep(NA_real_, n())
      },

    journal_club_attendance_pct =
      if (n_tracked_jc > 0) {
        100 * journal_clubs_attended / n_tracked_jc
      } else {
        rep(NA_real_, n())
      },

    research_forum_attendance_pct =
      if (n_tracked_rf > 0) {
        100 * research_forums_attended / n_tracked_rf
      } else {
        rep(NA_real_, n())
      }
  )

max_minutes <- if (nrow(member_summary)) {
  max(member_summary$total_minutes, na.rm = TRUE)
} else {
  0
}

member_summary <- member_summary |>
  mutate(
    normalized_minutes_pct =
      if (is.finite(max_minutes) && max_minutes > 0) {
        100 * total_minutes / max_minutes
      } else {
        rep(0, n())
      }
  ) |>
  arrange(
    desc(meetings_attended),
    desc(total_minutes),
    name
  ) |>
  mutate(
    rank = row_number()
  )


# ============================================================
# INDUSTRY RECOGNITION
# ============================================================

industry_summary <- attendance_long |>
  filter(audience == "Industry") |>
  group_by(
    person_id,
    name_key,
    company
  ) |>
  summarise(
    name = first(name),
    meetings_attended = n_distinct(event_id),
    total_minutes = sum(minutes, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(
    company,
    desc(meetings_attended),
    desc(total_minutes),
    name
  )

company_summary <- industry_summary |>
  group_by(company) |>
  summarise(
    unique_colleagues = n_distinct(person_id),
    total_person_minutes = sum(total_minutes, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(
    desc(unique_colleagues),
    company
  )


# ============================================================
# COMMUNITY ROSTER / AFFILIATION
# ============================================================

community_roster <- attendance_long |>
  group_by(
    person_id,
    name_key
  ) |>
  summarise(
    name = first(name),
    audience = if_else(
      any(audience == "Industry"),
      "Industry",
      "Academic / clinical"
    ),
    company = {
      z <- company[!is.na(company) & company != ""]
      if (length(z)) z[[1]] else NA_character_
    },
    affiliation_display = {
      z <- affiliation_display[
        !is.na(affiliation_display) &
          affiliation_display != ""
      ]
      if (length(z)) z[[1]] else "—"
    },
    meetings_attended = n_distinct(event_id),
    total_minutes = sum(minutes, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(
    audience,
    affiliation_display,
    name
  )

academic_roster_show <- community_roster |>
  filter(audience == "Academic / clinical") |>
  arrange(name)

industry_roster_show <- community_roster |>
  filter(audience == "Industry") |>
  arrange(
    company,
    name
  )

missing_affiliations <- community_roster |>
  filter(
    audience == "Academic / clinical",
    is.na(affiliation_display) |
      affiliation_display == "—"
  ) |>
  select(
    person_id,
    name,
    affiliation_display
  )


# ============================================================
# MEETING-LEVEL SUMMARY
# ============================================================

meeting_summary <- attendance_long |>
  group_by(
    event_id,
    meeting_folder,
    meeting_date,
    meeting_type,
    meeting_title
  ) |>
  summarise(
    unique_people = n_distinct(person_id),
    academic_people = n_distinct(
      person_id[audience == "Academic / clinical"]
    ),
    industry_people = n_distinct(
      person_id[audience == "Industry"]
    ),
    total_person_minutes = sum(minutes, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(
    meeting_date,
    meeting_folder
  )


# ============================================================
# ATTENDANCE MATRIX
# ============================================================
#
# Presence comes directly from persistent PARTICIPATION. Community Highlights
# does not apply page-level attendance overrides. Any confirmed participant
# missing from a tracked event should be curated upstream in the registry.

qc_attendance <- attendance_long |>
  transmute(
    event_id,
    person_id,
    name_key,
    name,
    audience,
    company,
    meeting_folder,
    meeting_date,
    meeting_type,
    minutes,
    attendance_status = if_else(
      is.na(minutes),
      "present_time_not_captured",
      "tracked"
    )
  )

qc_people <- qc_attendance |>
  group_by(
    person_id,
    name_key
  ) |>
  summarise(
    name = first(name),
    audience = if_else(
      any(audience == "Industry"),
      "Industry",
      "Academic / clinical"
    ),
    total_minutes = sum(minutes, na.rm = TRUE),
    meetings_attended = n_distinct(event_id),
    .groups = "drop"
  ) |>
  arrange(name)


# ============================================================
# OPTIONAL CSV OUTPUTS FOR AUDIT / REUSE
# ============================================================

readr::write_csv(
  attendance_long,
  file.path(output_dir, "community_attendance_long.csv")
)

readr::write_csv(
  member_summary,
  file.path(output_dir, "community_member_summary.csv")
)

readr::write_csv(
  industry_summary,
  file.path(output_dir, "community_industry_summary.csv")
)

readr::write_csv(
  company_summary,
  file.path(output_dir, "community_company_summary.csv")
)

readr::write_csv(
  meeting_summary,
  file.path(output_dir, "community_meeting_summary.csv")
)

readr::write_csv(
  qc_attendance,
  file.path(output_dir, "community_attendance_qc_long.csv")
)

readr::write_csv(
  community_roster,
  file.path(output_dir, "community_roster.csv")
)

readr::write_csv(
  missing_affiliations,
  file.path(output_dir, "community_missing_affiliations.csv")
)


# ============================================================
# PAGE OBJECTS
# ============================================================

meeting_archive_links <- tribble(
  ~meeting_folder,                                                     ~archive_href,

  "September 25 2026 - DAROMUN PIVOTAL",
  "/journal_club/September%2025%202026%20-%20DAROMUN%20PIVOTAL/",

  "August 14 2026 - FIRST in CSCC",
  "/journal_club/August%2014%202026%20-%20FIRST%20in%20CSCC/",

  "July 24 2026 - The Open Inference Project",
  "/research_forum/July%2024%202026%20-%20The%20Open%20Inference%20Project/",

  "June 12 2026 - Local Recurrence in MCC",
  "/journal_club/June%2012%202026%20-%20Local%20Recurrence%20in%20MCC/",

  # Attendance archive folder is dated April 12; the actual Journal Club
  # recap lives in the April 6 IGNYTE meeting folder.
  "April 12 2026 - IGNYTE",
  "/journal_club/April%206%202026%20-%20IGNYTE/",

  "March 9 2026 - Bayesian Causal Analysis of Dose Intensity in CSCC",
  "/research_forum/March%209%202026%20-%20Bayesian%20Causal%20Analysis%20of%20Dose%20Intensity%20in%20CSCC/",

  "February 13 2026 - Nivo-Rela vs BRAF-MEKi MAIC",
  "/journal_club/February%2013%202026%20-%20Nivo-Rela%20vs%20BRAF-MEKi%20MAIC/",

  "November 24 2025 - MATISSE",
  "/journal_club/November%2024%202025%20-%20MATISSE/",

  "July 11 2025 - c-Post",
  "/journal_club/July%2011%202025%20-%20c-Post/"
)

n_meetings <- nrow(meeting_summary)
n_jc <- sum(meeting_summary$meeting_type == "Journal Club")
n_rf <- sum(meeting_summary$meeting_type == "Research Forum")
n_academic <- nrow(member_summary)
n_industry <- nrow(industry_summary)

total_person_hours <- if (nrow(attendance_long)) {
  sum(attendance_long$minutes, na.rm = TRUE) / 60
} else {
  0
}

# Public recognition view:
# The scientific convener remains in the full attendance archive/matrix, but
# is omitted from the ranked participation view because attendance is expected
# as part of the role.
david_key <- clean_name_key("David M. Miller")

community_participation <- member_summary |>
  filter(name_key != david_key)

community_max_minutes <- if (nrow(community_participation)) {
  max(community_participation$total_minutes, na.rm = TRUE)
} else {
  0
}

community_participation <- community_participation |>
  mutate(
    normalized_minutes_pct =
      if (
        is.finite(community_max_minutes) &&
          community_max_minutes > 0
      ) {
        100 * total_minutes / community_max_minutes
      } else {
        rep(0, n())
      }
  ) |>
  arrange(
    desc(tracked_meeting_attendance_pct),
    desc(normalized_minutes_pct),
    name
  ) |>
  mutate(
    rank = row_number()
  )

top20 <- community_participation |>
  slice_head(n = 20)

```

<div class="ch-hero">
<div class="ch-hero-inner">
<div class="ch-eyebrow">Society of Cutaneous Oncology</div>

# Community Highlights

<p>
A record of the people who keep showing up: clinicians, researchers, trainees, and collaborators who have contributed their time to SoCO Journal Clubs and Research Forums.
</p>

<div class="ch-accent"></div>

<div class="ch-note">
<strong>A note on the archive.</strong> SoCO has held <strong>`r soco_total_meetings` meetings</strong> to date. Detailed person-level attendance is currently curated in the SoCO registry for <strong>`r n_meetings` meetings</strong>, so participation metrics on this page refer to that tracked subset rather than the full history of the community. <a href="jc.qmd">Explore the Journal Club archive</a> and <a href="research_forum.qmd">Research Forum archive</a>.
</div>
</div>
</div>

<div class="ch-wrap">

<section class="ch-section">
<div class="ch-section-head">
<div class="ch-eyebrow">The tracked community</div>

## Showing up matters.

<p>
The numbers below offer a simple way to recognize the people who have repeatedly made time for thoughtful, multidisciplinary discussion.
</p>
</div>

<div class="ch-metrics">
<div class="ch-metric">
<div class="ch-metric-label">Tracked meetings</div>
<div class="ch-metric-value">`r n_meetings`</div>
<div class="ch-metric-note">`r n_jc` Journal Clubs · `r n_rf` Research Forums</div>
</div>

<div class="ch-metric">
<div class="ch-metric-label">Academic / clinical participants</div>
<div class="ch-metric-value">`r n_academic`</div>
<div class="ch-metric-note">unique people represented in the registry-backed tracked archive</div>
</div>

<div class="ch-metric">
<div class="ch-metric-label">Industry collaborators</div>
<div class="ch-metric-value">`r n_industry`</div>
<div class="ch-metric-note">recognized separately from the academic / clinical participation view</div>
</div>

<div class="ch-metric">
<div class="ch-metric-label">Person-hours</div>
<div class="ch-metric-value">`r round(total_person_hours)`</div>
<div class="ch-metric-note">combined participation time across tracked meetings</div>
</div>
</div>
</section>

<section class="ch-section">
<div class="ch-section-head">
<div class="ch-eyebrow">Thank you</div>

## Everyone who has joined us

<p>
Every name below represents at least one appearance at a tracked SoCO Journal Club or Research Forum. No ranking here—just recognition.
</p>
</div>

```{r roll-call}
#| echo: false
#| results: asis

if (nrow(member_summary)) {
  cat('<div class="ch-rollcall">')

  for (nm in sort(member_summary$name)) {
    cat(
      '<span class="ch-name-chip">',
      esc(nm),
      '</span>'
    )
  }

  cat('</div>')
}
```
</section>

<section class="ch-section">
<div class="ch-section-head">
<div class="ch-eyebrow">Sustained participation</div>

## Community participation

<p>
A recognition of community members who have joined us most consistently across the registry-backed tracked archive. This group reflects frequency of participation across tracked meetings, with participation time used only to distinguish otherwise equal records.
</p>
</div>

```{r sustained-participation}
#| echo: false
#| results: asis

if (nrow(top20)) {

  cat('<div class="ch-leaderboard">')

  for (i in seq_len(nrow(top20))) {

    meeting_word <- if (top20$meetings_attended[i] == 1) {
      "meeting"
    } else {
      "meetings"
    }

    cat(
      '<div class="ch-person">',
        '<div class="ch-person-name">', esc(top20$name[i]), '</div>',
        '<div class="ch-meeting-count">',
          '<span class="ch-meeting-count-value">',
            top20$meetings_attended[i],
          '</span>',
          '<span class="ch-meeting-count-label">',
            meeting_word,
          '</span>',
        '</div>',
      '</div>'
    )
  }

  cat('</div>')
}
```
</section>

<section class="ch-section">
<div class="ch-section-head">
<div class="ch-eyebrow">Academic–industry participation</div>

## Industry collaborators

<p>
Industry colleagues are recognized separately from the academic and clinical community. Company grouping reflects the organization represented at the tracked meeting when that historical context is curated; the directory below continues to show the current registry affiliation.
</p>
</div>

```{r industry-recognition}
#| echo: false
#| results: asis

if (nrow(company_summary)) {

  cat('<div class="ch-industry-grid">')

  for (company_name in company_summary$company) {

    company_people <- industry_summary |>
      filter(company == company_name) |>
      arrange(desc(meetings_attended), desc(total_minutes), name)

    company_row <- company_summary |>
      filter(company == company_name) |>
      slice(1)

    cat(
      '<div class="ch-industry-card">',
        '<h3>', esc(company_name), '</h3>',
        '<div class="ch-industry-meta">',
          company_row$unique_colleagues,
          ' colleagues represented · ',
          round(company_row$total_person_minutes / 60),
          ' individually tracked person-hours',
        '</div>',
        '<div class="ch-industry-names">'
    )

    for (j in seq_len(nrow(company_people))) {
      cat(
        '<span class="ch-industry-name">',
        esc(company_people$name[j]),
        '</span>'
      )
    }

    cat(
        '</div>',
      '</div>'
    )
  }

  cat('</div>')
}
```
</section>

<section class="ch-section">
<div class="ch-section-head">
<div class="ch-eyebrow">Across institutions</div>

## Community roster

<p>
A directory-style view of the people, institutions, and organizations represented across the current tracked SoCO archive. Identity and current affiliation come from the persistent SoCO registry; related health-system names are consolidated for display.
</p>
</div>

<details class="ch-roster-details">
<summary>
<span class="ch-roster-summary-title">View community roster</span>
<span class="ch-roster-summary-subtitle">Registry-backed people and current affiliations represented across the tracked archive</span>
</summary>

```{r community-roster}
#| echo: false
#| results: asis

render_roster_half <- function(df, affiliation_label) {

  cat('<div class="ch-roster-table-wrap">')
  cat('<table class="ch-roster-table">')
  cat(
    '<thead><tr>',
      '<th>Name</th>',
      '<th>', esc(affiliation_label), '</th>',
    '</tr></thead><tbody>'
  )

  if (nrow(df)) {
    for (i in seq_len(nrow(df))) {
      cat(
        '<tr>',
          '<td>', esc(df$name[i]), '</td>',
          '<td class="ch-roster-affiliation">',
            esc(df$affiliation_display[i]),
          '</td>',
        '</tr>'
      )
    }
  }

  cat('</tbody></table>')
  cat('</div>')
}

render_roster_table <- function(df, heading, affiliation_label) {

  if (!nrow(df)) return(invisible(NULL))

  # Split the alphabetized directory into two balanced columns.
  # On small screens CSS stacks the two halves vertically.
  split_at <- ceiling(nrow(df) / 2)

  left_half <- df |>
    slice(seq_len(split_at))

  right_half <- if (split_at < nrow(df)) {
    df |>
      slice((split_at + 1):nrow(df))
  } else {
    df[0, , drop = FALSE]
  }

  cat('<div class="ch-roster-group">')
  cat('<h3>', esc(heading), '</h3>')
  cat('<div class="ch-roster-columns">')

  render_roster_half(
    left_half,
    affiliation_label
  )

  if (nrow(right_half)) {
    render_roster_half(
      right_half,
      affiliation_label
    )
  }

  cat('</div>')
  cat('</div>')
}

render_roster_table(
  academic_roster_show,
  "Academic / clinical community",
  "Institution / Organization"
)

render_roster_table(
  industry_roster_show,
  "Industry collaborators",
  "Organization"
)
```

</details>
</section>

<section class="ch-section">
<div class="ch-section-head">
<div class="ch-eyebrow">What is represented</div>

## Meetings in the current attendance archive

<p>
This page will continue to grow as additional SoCO meetings are added to the archive.
</p>
</div>

```{r meeting-archive}
#| echo: false
#| results: asis

if (nrow(meeting_summary)) {

  meeting_show <- meeting_summary |>
    left_join(
      meeting_archive_links,
      by = "meeting_folder"
    ) |>
    arrange(desc(meeting_date), meeting_folder)

  cat('<div class="ch-meeting-grid">')

  for (i in seq_len(nrow(meeting_show))) {

    title <- str_remove(
      meeting_show$meeting_folder[i],
      "^[A-Za-z]+\\s+\\d{1,2}\\s+\\d{4}\\s*-\\s*"
    )

    date_display <- format_meeting_date(
      as.Date(meeting_show$meeting_date[i])
    )

    href <- meeting_show$archive_href[i]

    if (is.na(href) || href == "") {

      cat(
        '<div class="ch-meeting">',
          '<div class="ch-meeting-type">',
            esc(meeting_show$meeting_type[i]),
          '</div>',
          '<div class="ch-meeting-title">',
            esc(title),
          '</div>',
          '<div class="ch-meeting-meta">',
            esc(date_display),
            ' · ',
            meeting_show$academic_people[i],
            ' academic / clinical',
            if (meeting_show$industry_people[i] > 0)
              paste0(
                ' · ',
                meeting_show$industry_people[i],
                ' industry'
              )
            else '',
          '</div>',
        '</div>'
      )

    } else {

      cat(
        '<a class="ch-meeting" href="',
          esc(href),
        '" aria-label="Open meeting archive: ',
          esc(title),
        '">',
          '<div class="ch-meeting-type">',
            esc(meeting_show$meeting_type[i]),
          '</div>',
          '<div class="ch-meeting-title">',
            esc(title),
          '</div>',
          '<div class="ch-meeting-meta">',
            esc(date_display),
            ' · ',
            meeting_show$academic_people[i],
            ' academic / clinical',
            if (meeting_show$industry_people[i] > 0)
              paste0(
                ' · ',
                meeting_show$industry_people[i],
                ' industry'
              )
            else '',
          '</div>',
        '</a>'
      )
    }
  }

  cat('</div>')
}
```

<details class="ch-qc-details">
<summary>
<span class="ch-qc-summary-copy">
<span class="ch-qc-summary-title">View full attendance matrix</span>
<span class="ch-qc-summary-subtitle">Meeting-by-meeting participation across the recent tracked archive</span>
</span>
</summary>

<div class="ch-qc-note">
The matrix provides a simple meeting-by-meeting record of who was present when attendance data are available. <strong>We recognize that clinical, research, and personal schedules vary, and joining for any portion of a meeting is appreciated.</strong> The matrix intentionally does not display how long someone participated; presence reflects participation for any portion of the meeting.
</div>

```{r attendance-qc-matrix}
#| echo: false
#| results: asis

qc_meetings <- meeting_index |>
  arrange(desc(meeting_date), meeting_folder)

if (nrow(qc_people) && nrow(qc_meetings)) {

  cat('<div class="ch-qc-table-wrap">')
  cat('<table class="ch-qc-table">')
  cat('<thead><tr>')
  cat('<th scope="col">Participant</th>')

  for (m in seq_len(nrow(qc_meetings))) {

    meeting_title <- str_remove(
      qc_meetings$meeting_folder[m],
      "^[A-Za-z]+\\s+\\d{1,2}\\s+\\d{4}\\s*-\\s*"
    )

    meeting_date_display <- format_meeting_date(
      as.Date(qc_meetings$meeting_date[m])
    )


    cat(
      '<th scope="col">',
        '<span class="ch-qc-meeting-title">',
          esc(meeting_title),
        '</span>',
        '<span class="ch-qc-meeting-date">',
          esc(meeting_date_display),
        '</span>',
      '</th>'
    )
  }

  cat('</tr></thead>')
  cat('<tbody>')

  for (p in seq_len(nrow(qc_people))) {

    person_key <- qc_people$name_key[p]
    person_name <- qc_people$name[p]
    person_audience <- qc_people$audience[p]

    cat('<tr>')

    cat(
      '<td>',
        '<span class="ch-qc-person">',
          esc(person_name),
        '</span>',
        '<span class="ch-qc-audience">',
          esc(person_audience),
        '</span>',
      '</td>'
    )

    for (m in seq_len(nrow(qc_meetings))) {

      meeting_name <- qc_meetings$meeting_folder[m]

      cell <- qc_attendance |>
        filter(
          name_key == person_key,
          meeting_folder == meeting_name
        ) |>
        slice(1)

      if (!nrow(cell)) {

        cat(
          '<td>',
            '<span class="ch-qc-absent">—</span>',
          '</td>'
        )

      } else {

        cat(
          '<td class="ch-qc-present">',
            '<span class="ch-qc-present-label">Present</span>',
          '</td>'
        )
      }
    }

    cat('</tr>')
  }

  cat('</tbody>')
  cat('</table>')
  cat('</div>')
}
```

</details>
</section>

</div>



