---
title: "Local Recurrence After Excision of Merkel Cell Carcinoma"
pagetitle: "Local Recurrence After Excision of MCC | SoCO Journal Club"
description: "Meeting recap from the June 12, 2026 Society of Cutaneous Oncology Journal Club discussing local recurrence after complete excision of Merkel cell carcinoma and the role of postoperative radiation."
date: 2026-06-12
author: "Society of Cutaneous Oncology"
categories:
  - 2026
  - Journal Club
  - Merkel Cell Carcinoma
  - Radiation Therapy
  - Local Recurrence
tags:
  - MCC
  - Local Recurrence
  - Postoperative Radiation
  - Surgery
  - Causal Inference
image: card.svg
page-layout: full
title-block-style: none
toc: false
execute:
  echo: false
  warning: false
  message: false
---

<style>
  :root {
    --navy: #082D4D;
    --teal: #28A9A2;
    --coral: #E25A4E;
    --ink: #31424E;
    --muted: #6B747B;
    --pale: #F3F8F8;
    --line: #D9E8E8;
  }

  #title-block-header,
  .quarto-title-block,
  .quarto-title,
  .quarto-title-meta {
    display: none !important;
  }

  body { color: var(--ink); background: #fff; }
  main.content { max-width: 1120px; margin: auto; padding-top: 0 !important; }
  h1,h2,h3 { color: var(--navy); font-weight: 800; }

  .hero {
    margin: 2rem 0 2.4rem;
    padding: 2.8rem 3rem;
    border-radius: 24px;
    background:
      radial-gradient(circle at 88% 12%, rgba(40,169,162,.11), transparent 31%),
      linear-gradient(135deg,#F3F8F8 0%,#FFFFFF 72%);
    border: 1px solid var(--line);
    box-shadow: 0 10px 30px rgba(8,45,77,.07);
  }

  .kicker,.section-kicker {
    color: var(--teal);
    font-weight: 800;
    letter-spacing: .15em;
    text-transform: uppercase;
    font-size: .8rem;
  }

  .hero h1 {
    max-width: 900px;
    font-size: clamp(2.7rem,5vw,4.1rem);
    line-height: 1.02;
    margin: .55rem 0 .8rem;
    letter-spacing: -.04em;
  }

  .hero-copy {
    font-size: 1.2rem;
    max-width: 850px;
    color: #56636D;
    line-height: 1.65;
  }

  .accent {
    width: 94px;
    height: 5px;
    border-radius: 4px;
    background: linear-gradient(90deg,var(--teal) 0 68%,var(--coral) 68%);
    margin-top: 1.4rem;
  }

  .metric-grid {
    display: grid;
    grid-template-columns: repeat(3,1fr);
    gap: 1rem;
    margin: 1.4rem 0 2rem;
  }

  .metric-card {
    border: 1px solid var(--line);
    border-radius: 18px;
    padding: 1.35rem 1.4rem;
    background: #fff;
    box-shadow: 0 6px 18px rgba(8,45,77,.05);
  }

  .metric-label {
    display: block;
    color: var(--muted);
    font-size: .8rem;
    font-weight: 800;
    text-transform: uppercase;
    letter-spacing: .09em;
  }

  .metric-value {
    display: block;
    color: var(--navy);
    font-size: 2.35rem;
    font-weight: 850;
    line-height: 1.05;
    margin: .35rem 0;
  }

  .metric-note { color: var(--muted); font-size: .92rem; line-height: 1.45; }

  .section-kicker { margin-top: 2.8rem; }

  .section-intro {
    font-size: 1.05rem;
    color: #56636D;
    max-width: 860px;
    margin-bottom: 1.2rem;
    line-height: 1.7;
  }

  .paper-card {
    max-width: 980px;
    margin: 1.2rem auto 2rem;
    padding: 1.75rem 2rem 1.7rem;
    border-left: 7px solid var(--teal);
    border-radius: 0 20px 20px 0;
    background: linear-gradient(135deg,rgba(40,169,162,.085),rgba(8,45,77,.035));
    box-shadow: 0 12px 30px rgba(8,45,77,.08);
  }

  .paper-eyebrow {
    color: var(--teal);
    font-size: .78rem;
    font-weight: 850;
    letter-spacing: .14em;
    text-transform: uppercase;
    margin-bottom: .65rem;
  }

  .paper-title {
    color: var(--navy);
    font-size: 1.62rem;
    line-height: 1.22;
    font-weight: 850;
    letter-spacing: -.015em;
    margin: 0 0 .85rem;
  }

  .paper-citation { color: #52616D; font-size: .98rem; line-height: 1.45; }

  .link-row {
    display:flex;
    flex-wrap:wrap;
    gap:.7rem;
    margin-top:1.2rem;
  }

  .soco-link {
    display:inline-flex;
    padding:.58rem .9rem;
    border-radius:999px;
    background:var(--navy);
    color:#fff !important;
    text-decoration:none;
    font-size:.88rem;
    font-weight:750;
  }

  .soco-link.secondary {
    background:#fff;
    border:1px solid rgba(40,169,162,.42);
    color:var(--navy) !important;
  }

  .question-card {
    margin: 1.6rem 0 2rem;
    padding: 1.55rem 1.7rem;
    border-left: 5px solid var(--coral);
    border-radius: 0 14px 14px 0;
    background: linear-gradient(135deg,rgba(226,90,78,.055),rgba(40,169,162,.045));
  }

  .question-card strong {
    display:block;
    color:var(--navy);
    font-size:1.2rem;
    line-height:1.55;
  }

  .highlight-grid {
    display:grid;
    grid-template-columns:repeat(2,minmax(0,1fr));
    gap:1rem;
    margin:1.2rem 0 1.5rem;
  }

  .highlight-card {
    border:1px solid #DCE8EB;
    border-radius:16px;
    padding:1.2rem 1.25rem;
    background:#fff;
    box-shadow:0 5px 18px rgba(8,45,77,.045);
  }

  .highlight-num {
    color:var(--coral);
    font-weight:900;
    font-size:.8rem;
    letter-spacing:.06em;
    text-transform:uppercase;
  }

  .highlight-card h3 {
    color:var(--navy);
    font-size:1.08rem;
    margin:.25rem 0 .55rem;
  }

  .highlight-card p {
    color:#405463;
    font-size:.94rem;
    line-height:1.5;
    margin:0;
  }

  .discussion-quote {
    margin:1.4rem 0;
    padding:1.1rem 1.25rem;
    border-left:5px solid var(--teal);
    background:#EFF8F7;
    border-radius:0 12px 12px 0;
    color:var(--navy);
    font-size:1.05rem;
    font-weight:700;
    line-height:1.45;
  }

  .caution-note {
    background:#FFF8F0;
    border-left:5px solid #E6A34A;
    padding:1rem 1.15rem;
    border-radius:0 12px 12px 0;
    color:#59462E;
    margin:1rem 0 1.5rem;
    font-size:.92rem;
    line-height:1.5;
  }

  .perspective-card {
    margin:2rem 0;
    padding:1.5rem 1.6rem;
    border:1px solid var(--line);
    border-radius:18px;
    background:
      radial-gradient(circle at 88% 12%,rgba(40,169,162,.10),transparent 28%),
      linear-gradient(135deg,#F7FBFB,#fff);
    box-shadow:0 8px 24px rgba(8,45,77,.05);
  }

  .perspective-card h3 { margin:.25rem 0 .65rem; }
  .perspective-card p { color:#52616D; line-height:1.65; margin-bottom:0; }


  .survey-grid {
    display:grid;
    grid-template-columns:repeat(3,minmax(0,1fr));
    gap:1rem;
    margin:1.2rem 0 1.5rem;
  }

  .survey-card {
    padding:1.25rem 1.3rem;
    border:1px solid var(--line);
    border-radius:16px;
    background:#fff;
    box-shadow:0 5px 18px rgba(8,45,77,.045);
  }

  .survey-value {
    display:block;
    color:var(--navy);
    font-size:2rem;
    font-weight:850;
    line-height:1.05;
    margin-bottom:.4rem;
  }

  .survey-label {
    display:block;
    color:var(--teal);
    font-size:.76rem;
    font-weight:850;
    letter-spacing:.08em;
    text-transform:uppercase;
    margin-bottom:.45rem;
  }

  .survey-copy {
    color:#52616D;
    font-size:.92rem;
    line-height:1.5;
  }

  .survey-note {
    margin:1.2rem 0 2rem;
    padding:1.15rem 1.25rem;
    border-left:5px solid var(--teal);
    border-radius:0 12px 12px 0;
    background:#EFF8F7;
    color:var(--navy);
    line-height:1.6;
  }

  /* =========================================================
     FULL SURVEY DISCLOSURE
     ========================================================= */

  .survey-disclosure {
    margin: 1.3rem 0 2.2rem;
  }

  .survey-toggle {
    width: 100%;
    display: grid;
    grid-template-columns: auto 1fr auto;
    gap: .9rem;
    align-items: center;
    padding: 1rem 1.15rem;
    border: 1px solid var(--line);
    border-radius: 16px;
    background:
      linear-gradient(135deg, #F3F8F8 0%, #FFFFFF 100%);
    color: var(--navy);
    text-align: left;
    cursor: pointer;
    box-shadow: 0 6px 18px rgba(8,45,77,.04);
  }

  .survey-toggle:hover {
    border-color: rgba(40,169,162,.48);
    box-shadow: 0 8px 24px rgba(8,45,77,.07);
  }

  .survey-toggle-badge {
    display: inline-flex;
    width: 38px;
    height: 38px;
    align-items: center;
    justify-content: center;
    border-radius: 50%;
    background: rgba(40,169,162,.12);
    color: var(--navy);
    font-size: 1.05rem;
  }

  .survey-toggle-copy strong {
    display: block;
    color: var(--navy);
    font-size: 1rem;
    font-weight: 850;
  }

  .survey-toggle-copy span {
    display: block;
    margin-top: .15rem;
    color: var(--muted);
    font-size: .84rem;
    line-height: 1.4;
  }

  .survey-toggle-icon {
    color: var(--teal);
    font-size: 1.3rem;
    font-weight: 900;
    transition: transform .2s ease;
  }

  .survey-toggle[aria-expanded="true"] .survey-toggle-icon {
    transform: rotate(45deg);
  }

  .survey-panel {
    display: none;
    margin-top: .8rem;
    padding: 1.1rem;
    border: 1px solid var(--line);
    border-radius: 16px;
    background: #fff;
  }

  .survey-panel.is-open {
    display: block;
  }

  .survey-panel-intro {
    margin: 0 0 1.15rem;
    padding: .85rem 1rem;
    border-left: 4px solid var(--teal);
    border-radius: 0 10px 10px 0;
    background: #F5FAFA;
    color: var(--muted);
    font-size: .9rem;
    line-height: 1.55;
  }

  .survey-question-label {
    color: var(--teal);
    font-size: .76rem;
    font-weight: 850;
    letter-spacing: .10em;
    text-transform: uppercase;
    margin: 1rem 0 .35rem;
  }

  .survey-figure-separator {
    margin: 1.5rem 0;
    border: 0;
    border-top: 1px solid #EDF2F4;
  }

  .survey-text-list {
    display: grid;
    gap: .55rem;
    margin-top: .5rem;
  }

  .survey-text-item {
    padding: .78rem .9rem;
    border: 1px solid var(--line);
    border-radius: 11px;
    background: #FAFCFC;
    color: #4B5E6C;
    font-size: .88rem;
    line-height: 1.5;
  }

  .footer-card {
    margin:3rem 0 1rem;
    padding:1.8rem 2rem;
    background:var(--navy);
    color:#fff;
    border-radius:20px;
  }

  .footer-card h2 { color:#fff; margin-top:0; }
  .footer-card p { margin-bottom:0; color:#EAF2F5; }

  /* =========================================================
     COMMUNITY / ENGAGEMENT / ATTENDANCE
     ========================================================= */

  .community-banner {
    position: relative;
    overflow: hidden;
    margin: 1.2rem 0 1.3rem;
    padding: 1.45rem 1.6rem;
    border: 1px solid var(--line);
    border-radius: 18px;
    background:
      radial-gradient(circle at 90% 15%, rgba(40,169,162,.12), transparent 30%),
      linear-gradient(135deg, #F7FBFB 0%, #FFFFFF 78%);
    box-shadow: 0 8px 24px rgba(8,45,77,.05);
  }

  .community-banner::after {
    content: "";
    position: absolute;
    width: 170px;
    height: 170px;
    top: -70px;
    right: -25px;
    opacity: .18;
    background-image:
      radial-gradient(circle, rgba(40,169,162,.72) 0 1.2px, transparent 1.8px);
    background-size: 20px 20px;
    mask-image: radial-gradient(circle, #000 0%, transparent 72%);
    -webkit-mask-image: radial-gradient(circle, #000 0%, transparent 72%);
    pointer-events: none;
  }

  .community-banner-kicker {
    position: relative;
    z-index: 1;
    color: var(--teal);
    font-size: .76rem;
    font-weight: 850;
    letter-spacing: .14em;
    text-transform: uppercase;
  }

  .community-banner-title {
    position: relative;
    z-index: 1;
    margin: .28rem 0 .35rem;
    color: var(--navy);
    font-size: clamp(1.7rem, 3vw, 2.35rem);
    font-weight: 850;
    letter-spacing: -.035em;
    line-height: 1.05;
  }

  .community-banner-copy {
    position: relative;
    z-index: 1;
    max-width: 860px;
    margin: 0;
    color: var(--muted);
    font-size: .97rem;
    line-height: 1.6;
  }

  .engagement-spotlight {
    position: relative;
    overflow: hidden;
    margin: 1rem 0 1.4rem;
    padding: 1.35rem 1.45rem 1.25rem;
    border: 1px solid #E9C85F;
    border-left: 7px solid #D7A400;
    border-radius: 18px;
    background:
      radial-gradient(circle at 92% 18%, rgba(255,255,255,.58), transparent 28%),
      linear-gradient(135deg, #FFF8D8 0%, #FDE9A9 100%);
    box-shadow: 0 10px 28px rgba(116,83,0,.10);
  }

  .engagement-spotlight-title {
    display: flex;
    align-items: center;
    gap: .6rem;
    margin: 0 0 .35rem;
    color: #765308;
    font-size: 1.1rem;
    font-weight: 850;
    letter-spacing: -.01em;
  }

  .engagement-spotlight-copy {
    max-width: 900px;
    margin: 0;
    color: #735F2C;
    font-size: .94rem;
    line-height: 1.55;
  }

  .engagement-pill-row {
    display: flex;
    flex-wrap: wrap;
    gap: .55rem;
    margin-top: .95rem;
  }

  .engagement-pill {
    display: inline-flex;
    align-items: center;
    padding: .5rem .72rem;
    border: 1px solid rgba(118,83,8,.18);
    border-radius: 999px;
    background: rgba(255,255,255,.82);
    color: #57420D;
    font-size: .86rem;
    font-weight: 780;
    box-shadow: 0 2px 7px rgba(116,83,0,.08);
  }

  .engagement-method {
    margin: .75rem 0 0;
    color: #7C6B42;
    font-size: .78rem;
    line-height: 1.5;
  }

  .roster-summary {
    display: flex;
    align-items: baseline;
    justify-content: space-between;
    gap: 1rem;
    margin: 0 0 .8rem;
    padding: .95rem 1.05rem;
    border: 1px solid var(--line);
    border-radius: 14px;
    background: #F9FBFB;
  }

  .roster-summary strong {
    color: var(--navy);
    font-size: 1rem;
  }

  .roster-summary span {
    color: var(--muted);
    font-size: .84rem;
  }

  .attendance-scroll {
    width: 100%;
    overflow-x: auto;
    -webkit-overflow-scrolling: touch;
    border-radius: 16px;
  }

  .attendance-table {
    width: 100%;
    min-width: 690px;
    border-collapse: separate;
    border-spacing: 0;
    overflow: hidden;
    border: 1px solid var(--line);
    border-radius: 16px;
    background: #fff;
    box-shadow: 0 8px 24px rgba(8,45,77,.045);
  }

  .attendance-table thead th {
    padding: .72rem .75rem;
    background: var(--navy);
    color: #fff;
    border: 0;
    font-size: .78rem;
    font-weight: 800;
    text-align: center;
  }

  .attendance-table thead th:first-child {
    text-align: left;
  }

  .attendance-table tbody td {
    padding: .66rem .75rem;
    border-top: 1px solid #E9EFF1;
    color: #334857;
    font-size: .88rem;
    text-align: center;
  }

  .attendance-table tbody tr:nth-child(even) td:not(.minutes-cell) {
    background: #FBFDFD;
  }

  .attendance-table tbody tr:hover td:not(.minutes-cell) {
    background: #F3F9F9;
  }

  .attendance-table .name-cell {
    color: var(--navy);
    font-weight: 750;
    text-align: left;
  }

  .attendance-table .minutes-cell {
    color: #17384C;
    font-variant-numeric: tabular-nums;
  }

  .attendance-table .signal-cell {
    color: #7A868E;
  }

  .attendance-table .signal-on {
    color: var(--teal);
    font-weight: 900;
  }

  .attendance-note {
    margin-top: .8rem;
    color: var(--muted);
    font-size: .82rem;
    line-height: 1.55;
  }

  @media(max-width:760px){
    main.content {
      width:100%;
      max-width:100%;
      padding-left:.85rem !important;
      padding-right:.85rem !important;
      overflow-x:hidden;
    }

    .metric-grid,.highlight-grid,.survey-grid{grid-template-columns:1fr;}

    .hero {
      margin-top:1rem;
      padding:1.55rem 1.15rem;
      border-radius:18px;
    }

    .hero h1 {
      font-size:clamp(2rem,10vw,2.55rem);
      line-height:1.02;
    }

    .hero-copy {
      font-size:1rem;
      line-height:1.55;
    }

    .paper-card {
      margin-left:0;
      margin-right:0;
      padding:1.2rem 1rem;
    }

    .paper-title { font-size:1.3rem; }

    .link-row {
      display:grid;
      grid-template-columns:1fr;
      gap:.55rem;
    }

    .soco-link {
      justify-content:center;
      width:100%;
      text-align:center;
    }

    .community-banner {
      padding:1.1rem;
    }

    .engagement-spotlight {
      padding:1.1rem 1rem;
    }

    .engagement-pill-row {
      display:grid;
      grid-template-columns:1fr;
    }

    .engagement-pill {
      width:100%;
      justify-content:flex-start;
    }

    .roster-summary {
      display:block;
    }

    .roster-summary span {
      display:block;
      margin-top:.3rem;
    }

    .attendance-scroll {
      margin-left:-.2rem;
      margin-right:-.2rem;
      padding-bottom:.25rem;
    }

    .attendance-table {
      min-width:690px;
    }

    .survey-toggle {
      padding:.9rem;
    }

    .survey-panel {
      padding:.8rem;
    }

    .survey-toggle-badge {
      width:34px;
      height:34px;
    }

    .footer-card {
      padding:1.3rem 1.15rem;
      border-radius:16px;
    }
  }
</style>

```{r}
#| label: setup-attendance

# -------------------------------------------------------------------------
# Resolve the meeting folder robustly.
#
# During Quarto render:
#   knitr::current_input() points to index.qmd.
#
# During interactive testing in RStudio:
#   use the active document path.
#
# If meeting_dir already exists and points to a real folder, keep it.
# -------------------------------------------------------------------------

resolve_meeting_dir <- function() {

  # 1. Reuse an already-valid meeting_dir, if present.
  if (
    exists("meeting_dir", inherits = TRUE) &&
    is.character(meeting_dir) &&
    length(meeting_dir) == 1 &&
    nzchar(meeting_dir) &&
    dir.exists(meeting_dir)
  ) {
    return(
      normalizePath(
        meeting_dir,
        winslash = "/",
        mustWork = TRUE
      )
    )
  }

  # 2. During a Quarto / knitr render, derive from index.qmd.
  current_input <- tryCatch(
    knitr::current_input(dir = TRUE),
    error = function(e) NULL
  )

  if (
    !is.null(current_input) &&
    length(current_input) == 1 &&
    !is.na(current_input) &&
    nzchar(current_input) &&
    file.exists(current_input)
  ) {
    return(
      dirname(
        normalizePath(
          current_input,
          winslash = "/",
          mustWork = TRUE
        )
      )
    )
  }

  # 3. During interactive RStudio testing, use the active document.
  if (
    interactive() &&
    requireNamespace("rstudioapi", quietly = TRUE)
  ) {

    ctx <- tryCatch(
      rstudioapi::getSourceEditorContext(),
      error = function(e) NULL
    )

    if (
      !is.null(ctx) &&
      !is.null(ctx$path) &&
      nzchar(ctx$path) &&
      file.exists(ctx$path)
    ) {

      active_path <- normalizePath(
        ctx$path,
        winslash = "/",
        mustWork = TRUE
      )

      active_dir <- dirname(active_path)

      # If the active document is index.qmd, this is already the meeting dir.
      if (basename(active_path) == "index.qmd") {
        return(active_dir)
      }

      # If the active file lives in scripts/, move up one level.
      if (basename(active_dir) == "scripts") {
        return(dirname(active_dir))
      }
    }
  }

  stop(
    paste0(
      "Could not determine the Journal Club meeting directory.\n",
      "Render index.qmd with Quarto, or open index.qmd / process_attendance.R ",
      "in RStudio before running this chunk interactively."
    )
  )
}

meeting_dir <- resolve_meeting_dir()

message("Meeting directory: ", meeting_dir)

# Process the raw Teams export.
source(
  file.path(
    meeting_dir,
    "scripts",
    "process_attendance.R"
  ),
  local = TRUE
)

attendance_dir <- file.path(
  meeting_dir,
  "files",
  "meeting recap-attendance"
)

# Read the cleaned outputs generated above.
people <- readr::read_csv(
  file.path(
    attendance_dir,
    "attendance_clean.csv"
  ),
  show_col_types = FALSE
)

headline <- readr::read_csv(
  file.path(
    attendance_dir,
    "attendance_summary.csv"
  ),
  show_col_types = FALSE
)

# -------------------------------------------------------------------------
# Archived pre-meeting survey
#
# This recap reads the SAVED processed RDS only. It does not call REDCap.
# That keeps the public-site build reproducible and credential-free.
# -------------------------------------------------------------------------

survey_processed_path <- file.path(
  meeting_dir,
  "files",
  "JC_survey_processed",
  "mcc_jc_survey_processed.rds"
)

survey_available <- file.exists(survey_processed_path)

if (survey_available) {

  survey_processed <- readRDS(survey_processed_path)

  dt_clean <- survey_processed$dt_clean
  checkbox_data <- survey_processed$checkbox_data
  question_map <- survey_processed$question_map

  # plot_question() needs the original REDCap data dictionary in order
  # to recover the question labels. Resolve the newest archived dictionary
  # inside this meeting folder rather than relying on the working directory.
  survey_dict_candidates <- list.files(
    file.path(
      meeting_dir,
      "files",
      "data dictionary"
    ),
    pattern = "_DataDictionary_.*\\.csv$",
    full.names = TRUE,
    ignore.case = TRUE
  )

  if (length(survey_dict_candidates) > 0) {
    survey_dict_path <- survey_dict_candidates[
      which.max(file.info(survey_dict_candidates)$mtime)
    ]
  } else {
    survey_dict_path <- NA_character_
    survey_available <- FALSE
  }

  # plot_question() is defined in the archived REDCap helper file.
  helper_path <- file.path(
    meeting_dir,
    "scripts",
    "REDCap Helpers.R"
  )

  if (file.exists(helper_path)) {
    source(helper_path, local = TRUE)
  } else {
    survey_available <- FALSE
  }
}
```

:::: {.hero}

::: {.kicker}
SoCO Journal Club · June 12, 2026
:::

# Local recurrence after excision of Merkel cell carcinoma

::: {.hero-copy}
A discussion about what the baseline risk of true primary-site local recurrence actually is, how postoperative radiation changes that risk, and how much certainty we need before exposing every patient to additional treatment.
:::

::: {.accent}
:::

::::

::: {.section-kicker}
Meeting pulse
:::

## A large MCC group — and a long discussion

::: {.metric-grid}

::: {.metric-card}
[People who joined]{.metric-label}

[`r headline$people`]{.metric-value}

[Unique cleaned people in the Teams attendance record]{.metric-note}
:::

::: {.metric-card}
[Median time together]{.metric-label}

[`r round(headline$median_minutes)` min]{.metric-value}

[Half the group stayed at least this long]{.metric-note}
:::

::: {.metric-card}
[Stayed at least an hour]{.metric-label}

[`r scales::percent(headline$pct_60min_plus, accuracy = 1)`]{.metric-value}

[Joined for at least 60 minutes]{.metric-note}
:::

:::

::: {.section-kicker}
Participation
:::

## A few ways people participated

::: {.section-intro}
Teams captures only a few coarse signals, but they give a useful sense of how actively the group engaged with a nearly two-hour discussion.
:::

::: {.metric-grid}

::: {.metric-card}
[Camera on]{.metric-label}

[`r scales::percent(headline$pct_camera, accuracy = 1)`]{.metric-value}

[Had the camera on at least once]{.metric-note}
:::

::: {.metric-card}
[Unmuted]{.metric-label}

[`r scales::percent(headline$pct_unmute, accuracy = 1)`]{.metric-value}

[Unmuted at least once during the meeting]{.metric-note}
:::

::: {.metric-card}
[Raised a hand]{.metric-label}

[`r scales::percent(headline$pct_hand_raise, accuracy = 1)`]{.metric-value}

[Used the Teams hand-raise signal]{.metric-note}
:::

:::

::: {.section-kicker}
The paper we discussed
:::

## Kavanagh et al. — local recurrence after complete excision

:::: {.paper-card}

::: {.paper-eyebrow}
Primary article · Annals of Surgical Oncology
:::

::: {.paper-title}
Local Recurrence Following Complete Surgical Excision of Primary Merkel Cell Carcinoma
:::

::: {.paper-citation}
**Kavanagh FG, et al.** *Ann Surg Oncol.* 2026;33(7):6681–6690.  
doi: 10.1245/s10434-025-18670-2
:::

::: {.link-row}
[PubMed](https://pubmed.ncbi.nlm.nih.gov/41191307/){.soco-link}
[DOI](https://doi.org/10.1245/s10434-025-18670-2){.soco-link .secondary}
:::

::::

::: {.question-card}
**The question beneath the paper:** After a negative-margin excision, how much risk of true primary-site local recurrence remains — and when is postoperative radiation worth using to prevent it?
:::

The study examined 447 patients with clinically localized MCC treated at Memorial Sloan Kettering Cancer Center. Among 393 patients treated with negative-margin surgery alone, seven local recurrences occurred within the first year, corresponding to an estimated **1-year local recurrence rate of 1.8%**. The rarity of the event also meant that conventional risk-factor modeling was inherently difficult.

::: {.caution-note}
**An important interpretive issue:** this was a natural-history study, not a randomized comparison of surgery versus postoperative radiation. Patients selected for radiation differed from those treated with surgery alone, so the study is highly informative about observed local recurrence after surgery but cannot by itself estimate the causal effect of radiation.
:::


::: {.section-kicker}
Before the discussion
:::

## The survey showed why this question is still unsettled

::: {.section-intro}
The Journal Club survey, later incorporated into the SoCO *Perspectives on the Science* article, made the practice variation visible before the group debated the paper. Clinicians were not starting from a shared estimate of baseline risk or a shared threshold for postoperative radiation.
:::

::: {.survey-grid}

::: {.survey-card}
[6–10%]{.survey-value}
[Most common baseline estimate]{.survey-label}

::: {.survey-copy}
Before the session, the largest group of respondents estimated local recurrence after margin-negative excision alone at 6–10%, even though estimates ranged from below 2% to above 10%.
:::
:::

::: {.survey-card}
[44%]{.survey-value}
[Individualized RT]{.survey-label}

::: {.survey-copy}
The largest group reported individualizing postoperative RT according to patient- and tumor-specific risk factors; 20% routinely recommended RT for nearly all patients and 20% rarely recommended it.
:::
:::

::: {.survey-card}
[Prospective data]{.survey-value}
[Most likely to change practice]{.survey-label}

::: {.survey-copy}
A prospective registry or clinical trial was the evidence type respondents most often selected as most likely to change current practice.
:::
:::

:::

::: {.survey-note}
The survey also showed that disagreement extends beyond whether to radiate. Respondents varied in preferred dose and fractionation, and the clinical scenarios revealed broad agreement at the lowest- and highest-risk extremes but substantially more variation in intermediate and preference-sensitive situations.
:::


<div class="survey-disclosure">

<button
  type="button"
  class="survey-toggle"
  id="survey-toggle"
  aria-expanded="false"
  aria-controls="full-survey-panel">

  <span class="survey-toggle-badge">▤</span>

  <span class="survey-toggle-copy">
    <strong>Explore the full pre-meeting survey</strong>
    <span>Open all archived survey figures, including practice patterns, risk estimates, radiation approaches, and clinical scenarios.</span>
  </span>

  <span class="survey-toggle-icon">+</span>

</button>

</div>


<div id="full-survey-panel" class="survey-panel">

<p class="survey-panel-intro">
These are the archived <strong>pre-discussion</strong> responses from the June 12 Journal Club. The headline findings remain above; this panel preserves the complete survey record for readers who want to inspect the underlying distributions and clinical scenarios.
</p>

```{r}
#| label: full-survey-results
#| echo: false
#| message: false
#| warning: false
#| results: asis
#| fig-width: 10
#| fig-height: 5.6
#| dpi: 120

if (!survey_available) {

  cat(
    '<p style="color:#6B747B;">',
    'Archived survey files were not found in the expected meeting folder.',
    '</p>'
  )

} else {

  # -----------------------------------------------------------------------
  # IMPORTANT:
  # Rebuild the same variable-keyed map used in the original June
  # presentation. The presentation itself used question_map_by_var$<field>
  # rather than iterating through raw question_map entries.
  # -----------------------------------------------------------------------

  question_map_by_var <- purrr::set_names(
    question_map,
    purrr::map_chr(question_map, "var")
  )

  # Exact plotting specifications carried over from the original
  # June 12 Journal Club presentation.
  survey_specs <- list(

    list(
      var = "primary_role",
      order = rev(c(
        "Medical Oncology",
        "Medical Dermatology",
        "Mohs Surgery",
        "Surgical Oncology",
        "ENT",
        "Radiation Oncology",
        "Pathology / Dermatopathology",
        "Research",
        "Trainee",
        "App",
        "Other"
      )),
      title_width = 45,
      x_label_width = 35,
      y_breaks = 1
    ),

    list(
      var = "mcc_patients_per_month",
      order = c(
        "Not Applicable To My Role",
        "0",
        "1-5",
        "6-10",
        ">10"
      ),
      title_width = 55,
      x_label_width = 40,
      y_breaks = 2
    ),

    list(
      var = "primary_rt_frequency",
      order = c(
        "Not Sure / Not Applicable",
        "Rarely Or Never",
        "Sometimes",
        "Often, Depending On Risk Factors",
        "Almost Always"
      ),
      title_width = 60,
      x_label_width = 45,
      y_breaks = 2
    ),

    list(
      var = "primary_rt_dose_fractionation",
      order = c(
        "Not Sure / Not Applicable",
        "Other",
        "My Approach Varies Substantially By Clinical Scenario",
        "Single-Fraction 8 Gy",
        "Moderate Hypofractionation, Such As 20-36 Gy Over Multiple Fractions",
        "Conventional Fractionation, Approximately 50-56 Gy",
        "I Generally Do Not Recommend Adjuvant Rt In This Setting"
      ),
      title_width = 55,
      x_label_width = 35,
      y_breaks = 1
    ),

    list(
      var = "rt_fractionation_varies_by_risk",
      order = c(
        "Not Sure / Not Applicable",
        "I Generally Do Not Recommend Adjuvant Rt In This Setting",
        "Minimally - I Generally Use The Same Dose/Fractionation When I Radiate",
        "Somewhat - I Individualize, But Usually Within A Limited Range",
        "Substantially - I Use Different Approaches For Lower- Versus Higher-Risk Cases"
      ),
      title_width = 58,
      x_label_width = 38,
      y_breaks = 1
    ),

    list(
      var = "rt_decision_factors",
      order = c(
        "Other",
        "Confidence In Surveillance / Salvage If Local Recurrence Occurs",
        "Patient Age, Frailty, Or Treatment Burden",
        "Positive Sentinel Lymph Node Biopsy",
        "Immunosuppression",
        "Close Or Positive Margin",
        "Lymphovascular Invasion",
        "Head And Neck Location",
        "Tumor Size >1 Cm"
      ),
      title_width = 58,
      x_label_width = 52,
      y_breaks = 2
    ),

    list(
      var = "estimated_lr_risk",
      order = c(
        "Not Sure",
        "<2%",
        "2-5%",
        "6-10%",
        ">10%"
      ),
      title_width = 60,
      x_label_width = 35,
      y_breaks = 1
    ),

    list(
      var = "paper_familiarity",
      order = c(
        "Not Familiar At All",
        "Minimally Familiar",
        "Somewhat Familiar",
        "Very Or Moderately Familiar"
      ),
      title_width = 58,
      x_label_width = 42,
      y_breaks = 1
    ),

    list(
      var = "evidence_to_change_rt",
      order = c(
        "Not Sure / Not Applicable",
        "My Practice Is Unlikely To Change Based On Additional Evidence",
        "Updated NCCN Or Other Guideline Recommendations",
        "Prospective Registry Or Clinical Trial Data",
        "Additional Multi-Institutional Retrospective Data",
        "The Kavanagh Et Al. Data Are Already Practice-Informing"
      ),
      title_width = 55,
      x_label_width = 37,
      y_breaks = 1
    ),

    list(
      var = "guideline_vs_individualized",
      order = c(
        "Not Sure / Not Applicable",
        "Often Discuss Omission Of RT In Selected Patients",
        "Individualize Based On Overall Recurrence Risk And Treatment Burden",
        "Generally Follow Guideline-Based Recommendation For RT"
      ),
      title_width = 55,
      x_label_width = 40,
      y_breaks = 1
    ),

    list(
      var = "scenario1_rt",
      order = c(
        "I Do Not Make Treatment Recommendations For MCC / Not Applicable To My Role",
        "Not Enough Information / Depends On Details",
        "Discuss RT But Generally Do Not Recommend It",
        "Observation / No Adjuvant RT",
        "Recommend Adjuvant RT"
      ),
      title_width = 50,
      x_label_width = 40,
      y_breaks = 1
    ),

    list(
      var = "scenario1_rt_regimen",
      order = c(
        "Other",
        "Single-Fraction 8 Gy",
        "Moderate Hypofractionation, Such As 20-36 Gy Over Multiple Fractions",
        "Conventional Fractionation, Approximately 50-56 Gy"
      ),
      title_width = 60,
      x_label_width = 40,
      y_breaks = 1
    ),

    list(
      var = "scenario2_rt",
      order = c(
        "I Do Not Make Treatment Recommendations For MCC / Not Applicable To My Role",
        "Discuss RT But Generally Do Not Recommend It",
        "Observation / No Adjuvant RT",
        "Recommend Adjuvant RT"
      ),
      title_width = 50,
      x_label_width = 40,
      y_breaks = 2
    ),

    list(
      var = "scenario2_rt_regimen",
      order = c(
        "Other",
        "Single-Fraction 8 Gy",
        "Moderate Hypofractionation, Such As 20-36 Gy Over Multiple Fractions",
        "Conventional Fractionation, Approximately 50-56 Gy"
      ),
      title_width = 60,
      x_label_width = 40,
      y_breaks = 1
    ),

    list(
      var = "scenario3_rt",
      order = c(
        "I Do Not Make Treatment Recommendations For MCC / Not Applicable To My Role",
        "Discuss RT But Generally Do Not Recommend It",
        "Observation / No Adjuvant RT",
        "Recommend Adjuvant RT"
      ),
      title_width = 70,
      x_label_width = 40,
      y_breaks = 1
    ),

    list(
      var = "scenario3_rt_regimen",
      order = c(
        "Other",
        "Single-Fraction 8 Gy",
        "Moderate Hypofractionation, Such As 20-36 Gy Over Multiple Fractions",
        "Conventional Fractionation, Approximately 50-56 Gy"
      ),
      title_width = 60,
      x_label_width = 40,
      y_breaks = 1
    ),

    list(
      var = "scenario4_rt_fractionation",
      order = c(
        "I Do Not Make Treatment Recommendations For MCC / Not Applicable To My Role",
        "Single-Fraction 8 Gy",
        "Moderate Hypofractionation Over Multiple Fractions",
        "Conventional Fractionation, Approximately 50-56 Gy",
        "Observation / No Adjuvant RT"
      ),
      title_width = 70,
      x_label_width = 40,
      y_breaks = 1
    ),

    list(
      var = "scenario5_sln_positive_rt",
      order = c(
        "I Do Not Make Treatment Recommendations For MCC / Not Applicable To My Role",
        "Not Enough Information / Depends On Details",
        "If RT Is Used: Other Abbreviated / Hypofractionated Approach",
        "If RT Is Used: Single-Fraction 8 Gy",
        "If RT Is Used: Conventional Fractionation",
        "Nodal-Basin RT",
        "Primary-Site RT",
        "No Adjuvant RT"
      ),
      title_width = 62,
      x_label_width = 42,
      y_breaks = 1
    ),

    list(
      var = "prospective_study_priority",
      order = c(
        "Not Sure / Not Applicable",
        "Low Priority",
        "Uncertain",
        "Moderately Important",
        "Very Important"
      ),
      title_width = 50,
      x_label_width = 50,
      y_breaks = 1
    )
  )

  rendered_n <- 0

  for (spec in survey_specs) {

    if (!spec$var %in% names(question_map_by_var)) {
      next
    }

    qinfo <- question_map_by_var[[spec$var]]

    p <- tryCatch(
      plot_question(
        qinfo,
        dt_clean,
        checkbox_data,
        custom_order = spec$order,
        dict_path = survey_dict_path,
        title_width = spec$title_width,
        x_label_width = spec$x_label_width,
        y_breaks = spec$y_breaks
      ),
      error = function(e) {
        message(
          "Survey plot skipped for ",
          spec$var,
          ": ",
          conditionMessage(e)
        )
        NULL
      }
    )

    if (!is.null(p)) {

      rendered_n <- rendered_n + 1

      cat(
        paste0(
          '<div class="survey-question-label">',
          'Survey item ', rendered_n,
          '</div>'
        )
      )

      print(p)

      cat('<hr class="survey-figure-separator">')
    }
  }

  # -----------------------------------------------------------------------
  # Final free-text question exactly as used in the original presentation.
  # -----------------------------------------------------------------------

  if ("key_uncertainty" %in% names(dt_clean)) {

    free_text <- dt_clean |>
      dplyr::filter(
        !is.na(key_uncertainty),
        stringr::str_squish(key_uncertainty) != ""
      ) |>
      dplyr::distinct(key_uncertainty) |>
      dplyr::pull(key_uncertainty)

    if (length(free_text) > 0) {

      cat(
        '<div class="survey-question-label">',
        'Open-text responses',
        '</div>',
        '<div class="survey-text-list">'
      )

      html_escape <- function(x) {
        x <- gsub("&", "&amp;", x, fixed = TRUE)
        x <- gsub("<", "&lt;", x, fixed = TRUE)
        x <- gsub(">", "&gt;", x, fixed = TRUE)
        x
      }

      for (response in free_text) {
        cat(
          '<div class="survey-text-item">',
          html_escape(response),
          '</div>'
        )
      }

      cat('</div>')
    }
  }

  if (rendered_n == 0) {
    cat(
      '<p style="color:#B45309;font-weight:700;">',
      'The archived survey loaded, but no quantitative survey figures rendered. ',
      'Check the render log for the survey plot messages.',
      '</p>'
    )
  }
}
```

</div>


<script>
document.addEventListener("DOMContentLoaded", function () {
  const button = document.getElementById("survey-toggle");
  const panel = document.getElementById("full-survey-panel");

  if (!button || !panel) return;

  button.addEventListener("click", function () {
    const isOpen = button.getAttribute("aria-expanded") === "true";

    button.setAttribute(
      "aria-expanded",
      isOpen ? "false" : "true"
    );

    panel.classList.toggle(
      "is-open",
      !isOpen
    );
  });
});
</script>

::: {.section-kicker}
Discussion highlights
:::

## What stuck with us from the conversation

::: {.section-intro}
The debate quickly moved beyond the point estimate. The group spent most of its time on what constitutes a true local recurrence, whether existing “high-risk” features actually predict that event, how salvage changes the clinical meaning of recurrence, and what kind of study could finally move the field.
:::

::: {.highlight-grid}

::: {.highlight-card}
[01 · Define the event]{.highlight-num}

### “High risk” is not necessarily high risk for local recurrence

Dan Coit emphasized that many features used to guide postoperative radiation were originally linked to nodal disease, recurrence broadly, disease-specific survival, or overall survival — not specifically to primary-site local recurrence. The endpoint has to match the treatment question.
:::

::: {.highlight-card}
[02 · The baseline risk]{.highlight-num}

### The number everyone needs — and still disagrees about

The MSK cohort places observed 1-year local recurrence after surgery alone at 1.8%. But the group debated whether treatment selection means the untreated risk in a broader population could be meaningfully higher. The argument was not simply about statistics; the baseline risk drives the absolute benefit radiation can plausibly provide.
:::

::: {.highlight-card}
[03 · Salvage matters]{.highlight-num}

### Preventing an event depends on what happens if the event occurs

Dan pushed the group to consider local recurrence together with salvage. If true local recurrence is uncommon and usually controllable with surgery and/or radiation after it occurs, the value of routinely treating everyone up front changes substantially.
:::

::: {.highlight-card}
[04 · Treatment burden]{.highlight-num}

### Neither surgery nor radiation is one thing

Paul Nghiem emphasized that wider surgery can carry meaningful morbidity, particularly in the head and neck, while contemporary radiation can sometimes be delivered with substantially less burden than historical courses. The real comparison is not “treatment versus no treatment,” but the absolute benefits and harms of specific strategies.
:::

::: {.highlight-card}
[05 · Equipoise]{.highlight-num}

### We may be radiating too many patients — but we still do not know whom to omit

Vern Sondak captured the tension well: he worried that current practice may overtreat many patients, yet remained uncertain about which patients can safely avoid radiation. That uncertainty is exactly what makes prospective evidence generation necessary.
:::

::: {.highlight-card}
[06 · The next study]{.highlight-num}

### Better data need a better inferential framework

The discussion moved toward multicenter data, explicit causal assumptions, absolute risk estimation, and Bayesian approaches that can represent uncertainty directly. In a rare disease with a rare endpoint, a future study has to ask a decision-relevant question rather than simply search for statistically significant predictors.
:::

:::

::: {.discussion-quote}
The practical question is not simply whether radiation reduces local recurrence. It is: **for this patient, how much absolute local-recurrence risk is being prevented, what happens if recurrence occurs, and what burden are we accepting to prevent it?**
:::

### Where the discussion landed

The meeting did not end with consensus — and that was useful.

The Kavanagh study provides unusually direct evidence that true primary-site local recurrence can be uncommon after complete negative-margin excision. At the same time, selection into postoperative radiation, variation in surgical and radiation strategies, and disagreement about the baseline untreated risk prevent the study from resolving the causal treatment question on its own.

The group converged more clearly on what the next evidence should look like: **better-defined endpoints, curated multicenter data, explicit attention to salvage and treatment burden, and analyses that estimate absolute treatment benefit under uncertainty.**

::: {.section-kicker}
From Journal Club to Perspectives
:::

## The discussion became a paper

::: {.perspective-card}

::: {.paper-eyebrow}
Perspectives on the Science · Journal of Cutaneous Oncology
:::

### Local Recurrence After Excision of Merkel Cell Carcinoma: What Do We Actually Know, and What Should We Do Next?

The Journal Club discussion — together with the structured survey of participating clinicians — ultimately became a multidisciplinary *Perspectives on the Science* article. The published piece uses those survey results to document variation in baseline risk estimates, radiation practice, dose and fractionation, and responses to specific clinical scenarios, then expands the debate to how the field should generate better evidence.

::: {.link-row}
[Read the JoCO Perspective](https://journalofcutaneousoncology.io/perspectives/vol_4_issue_2/local_recurrence_after_excision_mcc/){.soco-link}
:::

:::

::: {.section-kicker}
Our community
:::

## Who joined us?

<div class="community-banner">

<div class="community-banner-kicker">Our community</div>

<div class="community-banner-title">Who’s in the room today?</div>

<p class="community-banner-copy">
The Teams record captures time present and a few coarse participation signals. For this meeting, we also have the transcript, which gives us a better sense of who materially advanced the discussion. The recognition below combines both sources, with a modest moderator adjustment for substantive contributions that Teams telemetry cannot measure.
</p>

</div>


```{r}
#| label: engagement-standouts
#| results: asis

meeting_max <- max(people$duration_min, na.rm = TRUE)

# -------------------------------------------------------------------------
# Discussion bonus
#
# The four 25-point adjustments below are moderator-confirmed.
# Additional smaller adjustments are transcript-informed.
#
# Transcript review identified Kevin Emerick as a particularly substantive
# additional discussant (19 speaking turns / ~1,100 words), with Howard
# Kaufman, Ajay Sharma, and Adewunmi Adelaja also making meaningful
# contributions. Their smaller bonuses are intentionally not large enough
# to overwhelm the Teams-derived component.
# -------------------------------------------------------------------------

discussion_bonus_rules <- tibble::tribble(
  ~pattern,                                      ~discussion_bonus,
  "Coit",                                        25,
  "Nghiem",                                      25,
  "Sondak",                                      25,
  "David.*Miller|Miller.*David",                 25,
  "Emerick",                                     15,
  "Howard.*Kaufman|Kaufman.*Howard",              8,
  "Ajay.*Sharma|Sharma.*Ajay",                    8,
  "Adewunmi.*Adelaja|Adelaja.*Adewunmi",          8
)

get_discussion_bonus <- function(person_name) {

  matched <- discussion_bonus_rules |>
    dplyr::filter(
      stringr::str_detect(
        person_name,
        stringr::regex(
          pattern,
          ignore_case = TRUE
        )
      )
    )

  if (nrow(matched) == 0) return(0)

  max(matched$discussion_bonus)
}

engagement <- people |>
  mutate(
    attendance_fraction = pmin(duration_min / meeting_max, 1),

    # Objective Teams-derived component: maximum 100 points.
    recorded_engagement =
      55 * attendance_fraction +
      15 * as.numeric(any_camera) +
      20 * as.numeric(any_unmute) +
      10 * as.numeric(any_hand_raise),

    # Moderator / transcript-informed component.
    discussion_bonus = purrr::map_dbl(
      Name,
      get_discussion_bonus
    ),

    engagement_score =
      recorded_engagement +
      discussion_bonus
  ) |>
  arrange(
    desc(engagement_score),
    desc(discussion_bonus),
    desc(duration_min),
    Name
  )

# The four moderator-confirmed discussion leaders should always be
# represented in the recognition panel. Fill any remaining slot from the
# overall engagement ranking so Teams-derived participation still matters.
moderator_priority_patterns <- c(
  "Coit",
  "Nghiem",
  "Sondak",
  "David.*Miller|Miller.*David"
)

moderator_priority <- engagement |>
  filter(
    purrr::map_lgl(
      Name,
      ~ any(
        stringr::str_detect(
          .x,
          stringr::regex(
            moderator_priority_patterns,
            ignore_case = TRUE
          )
        )
      )
    )
  ) |>
  arrange(desc(engagement_score))

remaining_ranked <- engagement |>
  filter(!Name %in% moderator_priority$Name) |>
  arrange(desc(engagement_score))

top_engagement <- dplyr::bind_rows(
  moderator_priority,
  remaining_ranked
) |>
  distinct(Name, .keep_all = TRUE) |>
  slice_head(n = 5)

pill_html <- paste0(
  '<div class="engagement-pill">',
  top_engagement$Name,
  '</div>',
  collapse = ""
)

cat(
  paste0(
    '<div class="engagement-spotlight">',
      '<div class="engagement-spotlight-title">🏅 Engagement standouts</div>',
      '<p class="engagement-spotlight-copy">',
        'A small thank-you to five colleagues who stood out in this unusually substantive MCC discussion.',
      '</p>',
      '<div class="engagement-pill-row">',
        pill_html,
      '</div>',
      '<p class="engagement-method">',
        'The ranking combines time present and recorded Teams signals with a moderator/transcript-informed discussion bonus. ',
        'The four largest adjustments were moderator-confirmed; smaller transcript-informed adjustments recognize additional substantive discussion. ',
        'This is meant as recognition, not as a formal measure of contribution quality.',
      '</p>',
    '</div>'
  )
)
```


::: {.section-intro}
The cleaned Teams attendance record is retained with the meeting materials. Duplicate display names are reconciled and automated note-taking accounts are removed before the metrics below are calculated.
:::


```{r}
#| label: attendance-table
#| results: asis

library(dplyr)

roster <- people |>
  transmute(
    Name,
    Minutes = round(duration_min),
    Camera = if_else(any_camera, "●", "—"),
    Unmuted = if_else(any_unmute, "●", "—"),
    `Raised hand` = if_else(any_hand_raise, "●", "—")
  ) |>
  arrange(desc(Minutes), Name)

cat(
  paste0(
    '<div class="roster-summary">',
      '<strong>', nrow(roster), ' people represented</strong>',
      '<span>Sorted by time in meeting · ● indicates the Teams signal was recorded at least once</span>',
    '</div>'
  )
)

min_minutes <- min(roster$Minutes, na.rm = TRUE)
max_minutes <- max(roster$Minutes, na.rm = TRUE)

minute_fill <- function(x) {
  if (max_minutes == min_minutes) return("rgba(40,169,162,.18)")
  alpha <- 0.06 + 0.28 * ((x - min_minutes) / (max_minutes - min_minutes))
  sprintf("rgba(40,169,162,%.3f)", alpha)
}

html_escape <- function(x) {
  x <- gsub("&", "&amp;", x, fixed = TRUE)
  x <- gsub("<", "&lt;", x, fixed = TRUE)
  x <- gsub(">", "&gt;", x, fixed = TRUE)
  x
}

cat('<div class="attendance-scroll">')
cat('<table class="attendance-table">')
cat(
  '<thead><tr>',
  '<th>Name</th>',
  '<th>Minutes</th>',
  '<th>Camera</th>',
  '<th>Unmuted</th>',
  '<th>Raised hand</th>',
  '</tr></thead><tbody>'
)

for (i in seq_len(nrow(roster))) {

  row <- roster[i, ]

  signal_cell <- function(value) {
    cls <- if (identical(value, "●")) " signal-on" else ""
    paste0('<td class="signal-cell', cls, '">', value, '</td>')
  }

  cat(
    '<tr>',
      '<td class="name-cell">', html_escape(row$Name), '</td>',
      '<td class="minutes-cell" style="background:', minute_fill(row$Minutes), ';">',
        row$Minutes,
      '</td>',
      signal_cell(row$Camera),
      signal_cell(row$Unmuted),
      signal_cell(row$`Raised hand`),
    '</tr>'
  )
}

cat('</tbody></table></div>')
```

<div class="attendance-note">
Participation signals are descriptive only. Camera use, unmuting, and hand raises do not measure the quality or depth of participation; the transcript-informed adjustment is included precisely because those platform signals miss substantive discussion.
</div>


::: {.footer-card}

## Thanks for joining us.

This was exactly the kind of Journal Club the community is meant to create: a focused paper review that opened into a substantive disagreement about evidence, clinical judgment, treatment burden, and what study the field should do next.

:::

::: {.link-row}
[Back to Journal Club](../../jc.qmd){.soco-link}
[Read the JoCO Perspective](https://journalofcutaneousoncology.io/perspectives/vol_4_issue_2/local_recurrence_after_excision_mcc/){.soco-link .secondary}
[PubMed](https://pubmed.ncbi.nlm.nih.gov/41191307/){.soco-link .secondary}
:::
