---
title: "Community Highlights"
pagetitle: "Community Highlights | Society of Cutaneous Oncology"
description: "Recognition of the clinicians, researchers, trainees, and industry collaborators who have participated in tracked Society of Cutaneous Oncology Journal Clubs and Research Forums."
page-layout: full
title-block-style: none
toc: false
---

<style>
:root {
  --soco-navy:#041b33;
  --soco-blue:#06436e;
  --soco-teal:#0f7f86;
  --soco-coral:#ff3b3f;
  --soco-ink:#18293d;
  --soco-muted:#5c6f82;
  --soco-surface:#f6fafb;
  --soco-line:#dbe8ee;
  --soco-pale:#eef8f7;
}

#title-block-header,
.quarto-title-block,
.quarto-title,
.quarto-title-meta {
  display:none !important;
}

html, body {
  max-width:100%;
  overflow-x:hidden;
}

body {
  background:#fff;
}

main.content {
  max-width:100%;
  padding-top:0 !important;
}

.ch-wrap {
  max-width:1160px;
  margin:0 auto;
  padding:0 1.5rem;
}

.ch-hero {
  max-width:1320px;
  margin:3rem auto 0;
  padding:0 1.5rem;
}

.ch-hero-inner {
  position:relative;
  overflow:hidden;
  padding:clamp(2.8rem,5vw,4.7rem);
  border:1px solid var(--soco-line);
  border-radius:1.2rem;
  background:
    radial-gradient(circle at 88% 15%,rgba(15,127,134,.14),transparent 29%),
    radial-gradient(circle at 12% 88%,rgba(255,59,63,.05),transparent 30%),
    linear-gradient(135deg,#fff 0%,#f5faf9 100%);
  box-shadow:0 22px 60px rgba(4,27,51,.07);
}

.ch-hero-inner::after {
  content:"";
  position:absolute;
  width:380px;
  height:380px;
  top:-100px;
  right:-75px;
  opacity:.22;
  background-image:radial-gradient(circle,rgba(15,127,134,.75) 0 1.3px,transparent 2px);
  background-size:30px 30px;
  mask-image:radial-gradient(circle,#000 0%,transparent 72%);
  -webkit-mask-image:radial-gradient(circle,#000 0%,transparent 72%);
  pointer-events:none;
}

.ch-eyebrow {
  position:relative;
  z-index:1;
  color:var(--soco-teal);
  font-size:.78rem;
  font-weight:850;
  letter-spacing:.13em;
  text-transform:uppercase;
}

.ch-hero h1 {
  position:relative;
  z-index:1;
  max-width:900px;
  margin:.55rem 0 .9rem;
  color:var(--soco-navy);
  font-size:clamp(3rem,5vw,4.8rem);
  line-height:.98;
  letter-spacing:-.055em;
}

.ch-hero p {
  position:relative;
  z-index:1;
  max-width:860px;
  margin:0;
  color:#4d6170;
  font-size:1.12rem;
  line-height:1.72;
}

.ch-accent {
  position:relative;
  z-index:1;
  width:94px;
  height:5px;
  margin-top:1.5rem;
  border-radius:99px;
  background:linear-gradient(90deg,var(--soco-teal) 0 68%,var(--soco-coral) 68%);
}

.ch-note {
  margin:2rem 0 0;
  padding:1rem 1.15rem;
  border-left:4px solid var(--soco-teal);
  border-radius:.8rem;
  background:var(--soco-pale);
  color:#40586a;
  line-height:1.62;
}

.ch-section {
  margin-top:5rem;
}

.ch-section-head {
  max-width:850px;
  margin-bottom:1.7rem;
}

.ch-section h2 {
  margin:.25rem 0 .75rem;
  color:var(--soco-navy);
  font-size:clamp(2rem,3.4vw,3rem);
  letter-spacing:-.04em;
}

.ch-section-head p {
  margin:0;
  color:var(--soco-muted);
  font-size:1.04rem;
  line-height:1.72;
}

.ch-metrics {
  display:grid;
  grid-template-columns:repeat(4,minmax(0,1fr));
  gap:1rem;
  margin-top:1.5rem;
}

.ch-metric {
  padding:1.35rem 1.35rem;
  border:1px solid var(--soco-line);
  border-radius:1rem;
  background:#fff;
  box-shadow:0 8px 22px rgba(4,27,51,.05);
}

.ch-metric-label {
  color:var(--soco-muted);
  font-size:.72rem;
  font-weight:800;
  letter-spacing:.09em;
  text-transform:uppercase;
}

.ch-metric-value {
  margin:.25rem 0;
  color:var(--soco-navy);
  font-size:2.2rem;
  font-weight:850;
  line-height:1;
}

.ch-metric-note {
  color:#6a7985;
  font-size:.83rem;
  line-height:1.45;
}

.ch-rollcall {
  display:flex;
  flex-wrap:wrap;
  gap:.55rem;
  margin-top:1.25rem;
}

.ch-name-chip {
  padding:.52rem .72rem;
  border:1px solid var(--soco-line);
  border-radius:999px;
  background:#fff;
  color:#3f5566;
  font-size:.83rem;
  font-weight:650;
}

.ch-leaderboard {
  display:grid;
  gap:.8rem;
  margin-top:1.4rem;
}

.ch-person {
  display:grid;
  grid-template-columns:48px minmax(180px,1.2fr) minmax(210px,1fr) minmax(210px,1fr);
  gap:1rem;
  align-items:center;
  padding:1rem 1.1rem;
  border:1px solid var(--soco-line);
  border-radius:.95rem;
  background:#fff;
}

.ch-rank {
  color:var(--soco-teal);
  font-size:1.1rem;
  font-weight:850;
  text-align:center;
}

.ch-person-name {
  color:var(--soco-navy);
  font-weight:800;
}

.ch-bar-block {
  min-width:0;
}

.ch-bar-label {
  display:flex;
  justify-content:space-between;
  gap:.7rem;
  margin-bottom:.36rem;
  color:#667683;
  font-size:.74rem;
  font-weight:700;
}

.ch-bar-value {
  color:var(--soco-navy);
  font-weight:850;
}

.ch-track {
  width:100%;
  height:8px;
  overflow:hidden;
  border-radius:999px;
  background:#e8f0f2;
}

.ch-fill {
  height:100%;
  border-radius:999px;
  background:linear-gradient(90deg,#279a9b,#17628f);
}

.ch-fill.coral {
  background:linear-gradient(90deg,#ee776b,#ff3b3f);
}

.ch-industry-grid {
  display:grid;
  grid-template-columns:repeat(2,minmax(0,1fr));
  gap:1rem;
  margin-top:1.4rem;
}

.ch-industry-card {
  padding:1.35rem 1.4rem;
  border:1px solid rgba(15,127,134,.26);
  border-radius:1rem;
  background:linear-gradient(135deg,#eef8f7,#fff);
}

.ch-industry-card h3 {
  margin:0 0 .45rem;
  color:var(--soco-navy);
}

.ch-industry-meta {
  margin-bottom:.9rem;
  color:var(--soco-muted);
  font-size:.84rem;
}

.ch-industry-names {
  display:flex;
  flex-wrap:wrap;
  gap:.45rem;
}

.ch-industry-name {
  padding:.45rem .62rem;
  border:1px solid rgba(15,127,134,.22);
  border-radius:999px;
  background:rgba(255,255,255,.88);
  color:#415b6a;
  font-size:.79rem;
  font-weight:650;
}

.ch-meeting-grid {
  display:grid;
  grid-template-columns:repeat(2,minmax(0,1fr));
  gap:1rem;
  margin-top:1.35rem;
}

.ch-meeting {
  padding:1rem 1.1rem;
  border:1px solid var(--soco-line);
  border-radius:.9rem;
  background:var(--soco-surface);
}

.ch-meeting-type {
  color:var(--soco-teal);
  font-size:.7rem;
  font-weight:850;
  letter-spacing:.08em;
  text-transform:uppercase;
}

.ch-meeting-title {
  margin:.22rem 0 .45rem;
  color:var(--soco-navy);
  font-weight:780;
}

.ch-meeting-meta {
  color:var(--soco-muted);
  font-size:.82rem;
}

@media (max-width:900px) {
  .ch-metrics {
    grid-template-columns:repeat(2,minmax(0,1fr));
  }

  .ch-person {
    grid-template-columns:42px 1fr;
  }

  .ch-bar-block {
    grid-column:2;
  }
}

@media (max-width:700px) {
  html,
  body,
  main.content {
    width:100%;
    max-width:100%;
    overflow-x:hidden;
  }

  .ch-hero {
    width:100%;
    margin-top:.75rem;
    padding:0 .7rem;
  }

  .ch-hero-inner {
    width:100%;
    min-width:0;
    padding:1.35rem 1rem;
    border-radius:1rem;
  }

  .ch-hero h1 {
    max-width:100%;
    font-size:clamp(2.15rem,10.5vw,3rem);
    line-height:1.01;
    overflow-wrap:anywhere;
  }

  .ch-hero p {
    font-size:1rem;
    line-height:1.58;
  }

  .ch-wrap {
    width:100%;
    max-width:100%;
    padding:0 .7rem;
  }

  .ch-metrics,
  .ch-industry-grid,
  .ch-meeting-grid {
    grid-template-columns:minmax(0,1fr);
  }

  .ch-metric,
  .ch-industry-card,
  .ch-meeting {
    min-width:0;
  }

  .ch-section {
    margin-top:3.25rem;
  }

  .ch-section h2 {
    font-size:clamp(1.8rem,8.3vw,2.35rem);
    line-height:1.05;
  }

  .ch-rollcall {
    gap:.42rem;
  }

  .ch-name-chip,
  .ch-industry-name {
    max-width:100%;
    padding:.46rem .62rem;
    font-size:.78rem;
    overflow-wrap:anywhere;
  }

  .ch-person {
    grid-template-columns:34px minmax(0,1fr);
    gap:.7rem;
    min-width:0;
    padding:.85rem .8rem;
  }

  .ch-rank {
    font-size:1rem;
  }

  .ch-person-name {
    min-width:0;
    overflow-wrap:anywhere;
  }

  .ch-bar-block {
    grid-column:1 / -1;
    min-width:0;
  }

  .ch-bar-label {
    gap:.45rem;
    font-size:.7rem;
  }

  .ch-bar-label span:first-child {
    min-width:0;
  }

  .ch-bar-value {
    flex:0 0 auto;
    white-space:nowrap;
  }

  .ch-industry-card h3,
  .ch-meeting-title {
    overflow-wrap:anywhere;
  }

  .ch-note {
    padding:.9rem 1rem;
    font-size:.9rem;
  }
}

@media (max-width:430px) {
  .ch-hero {
    padding:0 .5rem;
  }

  .ch-wrap {
    padding:0 .5rem;
  }

  .ch-hero-inner {
    padding:1.15rem .9rem;
  }

  .ch-hero h1 {
    font-size:2.05rem;
  }

  .ch-metric-value {
    font-size:1.9rem;
  }

  .ch-person {
    padding:.78rem .7rem;
  }

  .ch-bar-label {
    align-items:flex-start;
  }

  .ch-bar-value {
    font-size:.68rem;
  }
}
</style>

```{r setup}
#| include: false
#| warning: false
#| message: false

suppressPackageStartupMessages({
  library(tidyverse)
  library(here)
  library(htmltools)
})

project_root <- here::here()
attendance_root <- file.path(project_root, "Attendance Over Time")
community_dir <- file.path(project_root, "community_highlights")
output_dir <- file.path(community_dir, "files")

dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)

if (!dir.exists(attendance_root)) {
  stop(
    "Could not find the attendance archive:\n",
    attendance_root
  )
}

# ============================================================
# MEETING CLASSIFICATION
# ============================================================

meeting_metadata <- tribble(
  ~folder_pattern, ~meeting_type,
  "Open Inference Project", "Research Forum",
  "Bayesian Causal Analysis of Dose Intensity", "Research Forum",
  "Research Forum", "Research Forum"
)

classify_meeting <- function(folder_name) {

  hit <- meeting_metadata |>
    filter(
      str_detect(
        folder_name,
        regex(folder_pattern, ignore_case = TRUE)
      )
    )

  if (nrow(hit)) {
    return(hit$meeting_type[[1]])
  }

  "Journal Club"
}

extract_meeting_date <- function(folder_name) {

  # Parse the date directly from folder names such as:
  # "July 11 2025 - c-Post"
  # "March 9 2026 - Bayesian Causal Analysis..."
  #
  # Use capture groups rather than regex look-behind so this works
  # reliably with stringi/ICU on macOS and inside Quarto.

  m <- str_match(
    folder_name,
    "^([A-Za-z]+)\\s+(\\d{1,2})\\s+(\\d{4})"
  )

  if (nrow(m) == 0 || any(is.na(m[1, 2:4]))) {
    return(as.Date(NA))
  }

  month_text <- m[1, 2]
  day_text   <- m[1, 3]
  year_text  <- m[1, 4]

  month_num <- match(
    str_to_lower(month_text),
    str_to_lower(month.name)
  )

  if (is.na(month_num)) {
    return(as.Date(NA))
  }

  as.Date(
    sprintf(
      "%04d-%02d-%02d",
      as.integer(year_text),
      month_num,
      as.integer(day_text)
    )
  )
}

format_meeting_date <- function(x) {

  if (length(x) != 1 || is.na(x)) {
    return("")
  }

  paste0(
    format(x, "%B"),
    " ",
    as.integer(format(x, "%d")),
    ", ",
    format(x, "%Y")
  )
}

# ============================================================
# IDENTITY CLEANING
# ============================================================

clean_name_key <- function(x) {

  x <- as.character(x)
  x <- str_replace_all(x, "\\u00A0", " ")
  x <- str_squish(x)

  map_chr(x, function(nm) {

    if (is.na(nm) || nm == "") return("")

    nm2 <- nm |>
      str_replace(
        regex(
          ",?\\s*(MD|PhD|DO|MBBS|CNP|NP|PA|MS|MPH|MBA|PGY\\d+)(,?\\s*(MD|PhD|DO|MBBS|CNP|NP|PA|MS|MPH|MBA|PGY\\d+))*\\s*$",
          ignore_case = TRUE
        ),
        ""
      ) |>
      str_squish()

    if (str_detect(nm2, ",")) {

      parts <- str_split_fixed(nm2, ",", 2)

      last_name <- parts[1] |>
        str_squish() |>
        str_to_lower()

      given_part <- parts[2] |>
        str_squish()

      first_name <- given_part |>
        str_split("\\s+") |>
        pluck(1, 1) |>
        str_to_lower()

      key <- paste(first_name, last_name)

    } else {

      words <- nm2 |>
        str_replace_all("[^A-Za-z0-9' -]", " ") |>
        str_squish() |>
        str_split("\\s+") |>
        pluck(1)

      if (length(words) == 1) {
        key <- str_to_lower(words[1])
      } else {
        key <- paste(
          str_to_lower(words[1]),
          str_to_lower(words[length(words)])
        )
      }
    }

    key |>
      str_replace_all("[^a-z0-9]", "") |>
      str_trim()
  })
}

# ============================================================
# EMBEDDED NAME RECONCILIATION
# ============================================================
#
# Keep all identity reconciliation here.
# Add rows as new aliases / malformed Teams display names appear.

name_reconciliation <- tribble(
  ~observed_key,          ~canonical_name,             ~exclude,

  # Clear duplicate identities
  "adeadamson",           "Adewole S. Adamson",        FALSE,
  "adewoleadamson",       "Adewole S. Adamson",        FALSE,

  "andrewknight",         "Andrew D. Knight",          FALSE,
  "andyknight",           "Andrew D. Knight",          FALSE,

  "sameer",               "Sameer Gupta",              FALSE,
  "sameergupta",          "Sameer Gupta",              FALSE,
  "samirgupta",           "Sameer Gupta",              FALSE,
  "sg",                   "Sameer Gupta",              FALSE,

  "vernonsondak",         "Vern Sondak",               FALSE,
  "vernsondak",           "Vern Sondak",               FALSE,

  # Non-person / artifact
  "d237",                 NA_character_,               TRUE,

  # Preferred display names / malformed Teams strings
  "adewunmiadelaja",      "Adewunmi O. Adelaja",       FALSE,
  "ajaysharma",           "Ajay N. Sharma",            FALSE,
  "christinecimoch",      "Christine C. Cimoch",       FALSE,
  "davidmiller",          "David M. Miller",            FALSE,
  "elizabethbuchbinder",  "Elizabeth I. Buchbinder",   FALSE,
  "elizabethlilley",      "Elizabeth J. Lilley",       FALSE,
  "francescollichio",     "Frances Collichio",         FALSE,
  "howardkaufman",        "Howard L. Kaufman",         FALSE,
  "isaacbrownell",        "Isaac Brownell",            FALSE,
  "jenniferdesimone",     "Jennifer DeSimone",         FALSE,
  "jessicafewkes",        "Jessica L. Fewkes",         FALSE,
  "julianeczapla",        "Juliane Andrade Czapla",    FALSE,
  "khalidgarman",         "Khalid Garman",             FALSE,
  "kamanehmontazeri",     "Kamaneh Montazeri",         FALSE,
  "karamkhaddour",        "Karam Khaddour",            FALSE,
  "kevinemerick",         "Kevin S. Emerick",          FALSE,
  "kristarubin",          "Krista M. Rubin",           FALSE,
  "larisageskin",         "Larisa Geskin",             FALSE,
  "lauraferris",          "Laura Ferris",              FALSE,
  "laurenoloughlin",      "Lauren O'Loughlin",         FALSE,
  "meghanmooradian",      "Meghan J. Mooradian",       FALSE,
  "mehranyusuf",          "Mehran Behruj Yusuf",       FALSE,
  "minabakhtiar",         "Mina Bakhtiar",             FALSE,
  "mollyyancovitz",       "Molly Yancovitz",           FALSE,
  "mariam",               "Mariam El-Ashmawy",         FALSE,
  "nikhilkhushalani",     "Nikhil Khushalani",         FALSE,
  "reeddrews",            "Reed E. Drews",             FALSE,
  "rhodaalani",           "Rhoda Alani",               FALSE,
  "rossmerkin",           "Ross D. Merkin",            FALSE,
  "madelienestump",       "Madeliene Stump",           FALSE,
  "tatyanasharova",       "Tatyana Sharova",           FALSE,
  "vatchetchekmedyian",   "Vatche Tchekmedyian",      FALSE
) |>
  mutate(
    canonical_key = if_else(
      is.na(canonical_name),
      NA_character_,
      clean_name_key(canonical_name)
    )
  )

apply_name_reconciliation <- function(df) {

  df |>
    left_join(
      name_reconciliation,
      by = c("name_key" = "observed_key")
    ) |>
    mutate(
      exclude = replace_na(exclude, FALSE),

      name = if_else(
        !is.na(canonical_name),
        canonical_name,
        name
      ),

      name_key = if_else(
        !is.na(canonical_key),
        canonical_key,
        name_key
      )
    ) |>
    filter(!exclude) |>
    select(
      -canonical_name,
      -canonical_key,
      -exclude
    )
}

# ============================================================
# EMBEDDED INDUSTRY LOOKUP
# ============================================================
#
# Domain-based classification works whenever email was retained in
# attendance_clean.csv. For older meetings without email, add a person
# directly to industry_people_overrides below.

industry_domains <- tribble(
  ~domain, ~company,
  "regeneron.com", "Regeneron",
  "bms.com",       "Bristol Myers Squibb",
  "replimune.com", "Replimune"
)

industry_people_overrides <- tribble(
  ~name,               ~company,

  # Bristol Myers Squibb
  "Gregory Norigian",  "Bristol Myers Squibb",
  "Omid Najmi",        "Bristol Myers Squibb",
  "Cara Trulli",       "Bristol Myers Squibb",
  "Leon Sakkal",       "Bristol Myers Squibb",
  "Abraham Selvan",    "Bristol Myers Squibb",
  "Divya Patel",       "Bristol Myers Squibb",
  "Christopher Lao",   "Bristol Myers Squibb",
  "Corey Rantz",       "Bristol Myers Squibb",

  # Replimune
  "Jeannie Hou",       "Replimune",
  "Adam Yakovich",     "Replimune",
  "Adam Whalley",      "Replimune"
) |>
  mutate(
    name = as.character(name),
    company = as.character(company),
    name_key = clean_name_key(name)
  )

# Some industry colleagues participated from a shared room or otherwise
# were not preserved as separate rows in the Teams attendance export.
# Keep those known participants here so they are still acknowledged
# in the industry-recognition section without assigning invented minutes.
supplemental_industry_attendees <- tribble(
  ~name,               ~company,                 ~meeting_folder,

  # Replimune colleagues confirmed to have participated in the IGNYTE meeting.
  "Jeannie Hou",       "Replimune",              "April 12 2026 - IGNYTE",
  "Adam Yakovich",     "Replimune",              "April 12 2026 - IGNYTE",
  "Adam Whalley",      "Replimune",              "April 12 2026 - IGNYTE",

  # Bristol Myers Squibb colleagues confirmed from the April 2025
  # Journal Club invitation / correspondence. Individual Teams
  # attendance records are no longer available for that meeting,
  # so they are acknowledged here without invented attendance minutes.
  "Omid Najmi",        "Bristol Myers Squibb",    "April 2025 - CheckMate 358 Journal Club",
  "Christopher Lao",   "Bristol Myers Squibb",    "April 2025 - CheckMate 358 Journal Club",
  "Leon Sakkal",       "Bristol Myers Squibb",    "April 2025 - CheckMate 358 Journal Club",
  "Divya Patel",       "Bristol Myers Squibb",    "April 2025 - CheckMate 358 Journal Club",
  "Gregory Norigian",  "Bristol Myers Squibb",    "April 2025 - CheckMate 358 Journal Club",
  "Corey Rantz",       "Bristol Myers Squibb",    "April 2025 - CheckMate 358 Journal Club",
  "Abraham Selvan",    "Bristol Myers Squibb",    "April 2025 - CheckMate 358 Journal Club"
) |>
  mutate(
    name_key = clean_name_key(name)
  )


# ============================================================
# ATTENDANCE FILE STANDARDIZATION
# ============================================================

normalize_email <- function(x) {
  x |>
    replace_na("") |>
    as.character() |>
    str_replace_all("\\\\", "") |>
    str_to_lower() |>
    str_trim()
}

extract_domain <- function(email) {
  ifelse(
    str_detect(email, "@"),
    str_replace(email, "^.*@", ""),
    ""
  )
}

standardize_attendance <- function(path, folder_name) {

  x <- readr::read_csv(
    path,
    show_col_types = FALSE
  )

  nms <- names(x)

  name_col <- case_when(
    "name" %in% nms ~ "name",
    "Name" %in% nms ~ "Name",
    "participant" %in% nms ~ "participant",
    "Participant" %in% nms ~ "Participant",
    TRUE ~ NA_character_
  )

  minutes_col <- case_when(
    "minutes" %in% nms ~ "minutes",
    "Minutes" %in% nms ~ "Minutes",
    "duration_min" %in% nms ~ "duration_min",
    "attendance_minutes" %in% nms ~ "attendance_minutes",
    "duration_minutes" %in% nms ~ "duration_minutes",
    TRUE ~ NA_character_
  )

  email_col <- case_when(
    "email" %in% nms ~ "email",
    "Email" %in% nms ~ "Email",
    TRUE ~ NA_character_
  )

  if (is.na(name_col) || is.na(minutes_col)) {
    warning(
      "Skipping ", folder_name,
      ": attendance_clean.csv does not contain recognizable name/minutes columns. ",
      "Columns found: ",
      paste(nms, collapse = " | ")
    )
    return(NULL)
  }

  tibble(
    meeting_folder = folder_name,
    meeting_date = extract_meeting_date(folder_name),
    meeting_type = classify_meeting(folder_name),
    name = as.character(x[[name_col]]),
    minutes = suppressWarnings(as.numeric(x[[minutes_col]])),
    email = if (!is.na(email_col)) as.character(x[[email_col]]) else ""
  ) |>
    mutate(
      name = str_squish(name),
      name_key = clean_name_key(name),
      email = normalize_email(email),
      domain = extract_domain(email)
    ) |>
    filter(
      name != "",
      !is.na(minutes)
    )
}

# ============================================================
# SCAN ALL TRACKED MEETINGS
# ============================================================

meeting_folders <- list.dirs(
  attendance_root,
  recursive = FALSE,
  full.names = TRUE
)

clean_files <- file.path(
  meeting_folders,
  "attendance_clean.csv"
)

has_clean <- file.exists(clean_files)

meeting_folders <- meeting_folders[has_clean]
clean_files <- clean_files[has_clean]

if (!length(clean_files)) {
  stop(
    "No attendance_clean.csv files were found under:\n",
    attendance_root
  )
}

attendance_list <- map2(
  clean_files,
  basename(meeting_folders),
  standardize_attendance
)

attendance_long <- bind_rows(attendance_list)

if (!nrow(attendance_long)) {
  stop("Attendance files were found, but no usable attendance rows were produced.")
}

attendance_long <- apply_name_reconciliation(attendance_long)

# Collapse duplicates within each meeting AFTER reconciliation.
attendance_long <- attendance_long |>
  group_by(
    meeting_folder,
    meeting_date,
    meeting_type,
    name_key
  ) |>
  summarise(
    name = first(name),
    minutes = sum(minutes, na.rm = TRUE),
    email = {
      z <- email[email != "" & !is.na(email)]
      if (length(z)) z[[1]] else ""
    },
    domain = {
      z <- domain[domain != "" & !is.na(domain)]
      if (length(z)) z[[1]] else ""
    },
    .groups = "drop"
  )

# ============================================================
# INDUSTRY CLASSIFICATION
# ============================================================

attendance_long <- attendance_long |>
  left_join(
    industry_domains,
    by = "domain"
  ) |>
  left_join(
    industry_people_overrides |>
      select(
        name_key,
        company_override = company
      ),
    by = "name_key"
  ) |>
  mutate(
    company = coalesce(
      na_if(as.character(company_override), ""),
      na_if(as.character(company), "")
    ),
    audience = if_else(
      !is.na(company),
      "Industry",
      "Academic / clinical"
    )
  ) |>
  select(-company_override)

# ============================================================
# DENOMINATORS
# ============================================================

meeting_index <- attendance_long |>
  distinct(
    meeting_folder,
    meeting_date,
    meeting_type
  ) |>
  arrange(
    meeting_date,
    meeting_folder
  )

n_tracked_meetings <- nrow(meeting_index)

n_tracked_jc <- meeting_index |>
  filter(meeting_type == "Journal Club") |>
  nrow()

n_tracked_rf <- meeting_index |>
  filter(meeting_type == "Research Forum") |>
  nrow()

# ============================================================
# ACADEMIC / CLINICAL MEMBER SUMMARY
# ============================================================

academic <- attendance_long |>
  filter(audience == "Academic / clinical")

member_summary <- academic |>
  group_by(name_key) |>
  summarise(
    name = first(name),
    meetings_attended = n_distinct(meeting_folder),
    journal_clubs_attended = n_distinct(
      meeting_folder[meeting_type == "Journal Club"]
    ),
    research_forums_attended = n_distinct(
      meeting_folder[meeting_type == "Research Forum"]
    ),
    total_minutes = sum(minutes, na.rm = TRUE),
    .groups = "drop"
  ) |>
  mutate(
    tracked_meeting_attendance_pct =
      if (n_tracked_meetings > 0) {
        100 * meetings_attended / n_tracked_meetings
      } else {
        rep(NA_real_, n())
      },

    journal_club_attendance_pct =
      if (n_tracked_jc > 0) {
        100 * journal_clubs_attended / n_tracked_jc
      } else {
        rep(NA_real_, n())
      },

    research_forum_attendance_pct =
      if (n_tracked_rf > 0) {
        100 * research_forums_attended / n_tracked_rf
      } else {
        rep(NA_real_, n())
      }
  )

max_minutes <- max(
  member_summary$total_minutes,
  na.rm = TRUE
)

member_summary <- member_summary |>
  mutate(
    normalized_minutes_pct =
      if (max_minutes > 0) {
        100 * total_minutes / max_minutes
      } else {
        rep(0, n())
      }
  ) |>
  arrange(
    desc(tracked_meeting_attendance_pct),
    desc(normalized_minutes_pct),
    name
  ) |>
  mutate(
    rank = row_number()
  )

# ============================================================
# INDUSTRY RECOGNITION
# ============================================================

industry_summary <- attendance_long |>
  filter(audience == "Industry") |>
  group_by(
    name_key,
    company
  ) |>
  summarise(
    name = first(name),
    meetings_attended = n_distinct(meeting_folder),
    total_minutes = sum(minutes, na.rm = TRUE),
    .groups = "drop"
  )

# Guarantee recognition of known industry participants whose individual
# minutes were not captured because they joined from a shared room or
# were otherwise absent from the person-level Teams export.
supplemental_industry_summary <- supplemental_industry_attendees |>
  group_by(
    name_key,
    company
  ) |>
  summarise(
    name = first(name),
    meetings_attended = n_distinct(meeting_folder),
    total_minutes = 0,
    .groups = "drop"
  )

industry_summary <- bind_rows(
  industry_summary,
  supplemental_industry_summary
) |>
  group_by(
    name_key,
    company
  ) |>
  summarise(
    name = first(name),
    meetings_attended = max(meetings_attended, na.rm = TRUE),
    total_minutes = max(total_minutes, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(
    company,
    desc(meetings_attended),
    desc(total_minutes),
    name
  )

company_summary <- industry_summary |>
  group_by(company) |>
  summarise(
    unique_colleagues = n_distinct(name_key),
    total_person_minutes = sum(total_minutes, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(unique_colleagues), company)

# ============================================================
# MEETING-LEVEL SUMMARY
# ============================================================

meeting_summary <- attendance_long |>
  group_by(
    meeting_folder,
    meeting_date,
    meeting_type
  ) |>
  summarise(
    unique_people = n_distinct(name_key),
    academic_people = n_distinct(
      name_key[audience == "Academic / clinical"]
    ),
    industry_people = n_distinct(
      name_key[audience == "Industry"]
    ),
    total_person_minutes = sum(minutes, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(
    meeting_date,
    meeting_folder
  )

# ============================================================
# OPTIONAL CSV OUTPUTS FOR AUDIT / REUSE
# ============================================================

readr::write_csv(
  attendance_long,
  file.path(output_dir, "community_attendance_long.csv")
)

readr::write_csv(
  member_summary,
  file.path(output_dir, "community_member_summary.csv")
)

readr::write_csv(
  industry_summary,
  file.path(output_dir, "community_industry_summary.csv")
)

readr::write_csv(
  company_summary,
  file.path(output_dir, "community_company_summary.csv")
)

readr::write_csv(
  meeting_summary,
  file.path(output_dir, "community_meeting_summary.csv")
)

# ============================================================
# PAGE OBJECTS
# ============================================================

esc <- function(x) htmltools::htmlEscape(as.character(x))

n_meetings <- nrow(meeting_summary)
n_jc <- sum(meeting_summary$meeting_type == "Journal Club")
n_rf <- sum(meeting_summary$meeting_type == "Research Forum")
n_academic <- nrow(member_summary)
n_industry <- nrow(industry_summary)

total_person_hours <- if (nrow(attendance_long)) {
  sum(attendance_long$minutes, na.rm = TRUE) / 60
} else {
  0
}

top20 <- member_summary |>
  slice_head(n = 20)

```

<div class="ch-hero">
<div class="ch-hero-inner">
<div class="ch-eyebrow">Society of Cutaneous Oncology</div>

# Community Highlights

<p>
A record of the people who keep showing up: clinicians, researchers, trainees, and collaborators who have contributed their time to SoCO Journal Clubs and Research Forums.
</p>

<div class="ch-accent"></div>

<div class="ch-note">
<strong>A note on the archive.</strong> Attendance records are available for a recent subset of SoCO meetings rather than the full history of the community. Everything on this page therefore refers to <strong>tracked meetings</strong> only.
</div>
</div>
</div>

<div class="ch-wrap">

<section class="ch-section">
<div class="ch-section-head">
<div class="ch-eyebrow">The tracked community</div>

## Showing up matters.

<p>
The numbers below are not meant to turn participation into a competition. They are a simple way to recognize the people who have repeatedly made time for thoughtful, multidisciplinary discussion.
</p>
</div>

<div class="ch-metrics">
<div class="ch-metric">
<div class="ch-metric-label">Tracked meetings</div>
<div class="ch-metric-value">`r n_meetings`</div>
<div class="ch-metric-note">`r n_jc` Journal Clubs · `r n_rf` Research Forums</div>
</div>

<div class="ch-metric">
<div class="ch-metric-label">Academic / clinical participants</div>
<div class="ch-metric-value">`r n_academic`</div>
<div class="ch-metric-note">unique people represented in the tracked attendance archive</div>
</div>

<div class="ch-metric">
<div class="ch-metric-label">Industry collaborators</div>
<div class="ch-metric-value">`r n_industry`</div>
<div class="ch-metric-note">recognized separately from the academic community leaderboard</div>
</div>

<div class="ch-metric">
<div class="ch-metric-label">Person-hours</div>
<div class="ch-metric-value">`r round(total_person_hours)`</div>
<div class="ch-metric-note">combined participation time across tracked meetings</div>
</div>
</div>
</section>

<section class="ch-section">
<div class="ch-section-head">
<div class="ch-eyebrow">Thank you</div>

## Everyone who has joined us

<p>
Every name below represents at least one appearance at a tracked SoCO Journal Club or Research Forum. No ranking here—just recognition.
</p>
</div>

```{r roll-call}
#| echo: false
#| results: asis

if (nrow(member_summary)) {
  cat('<div class="ch-rollcall">')

  for (nm in sort(member_summary$name)) {
    cat(
      '<span class="ch-name-chip">',
      esc(nm),
      '</span>'
    )
  }

  cat('</div>')
}
```
</section>

<section class="ch-section">
<div class="ch-section-head">
<div class="ch-eyebrow">Sustained participation</div>

## Top 20 community contributors

<p>
Two separate measures are shown. <strong>Meeting attendance</strong> is the percentage of all tracked SoCO meetings attended—Journal Clubs and Research Forums combined. <strong>Participation time</strong> is normalized to the academic / clinical participant with the greatest total tracked attendance time, who is set to 100%.
</p>
</div>

```{r leaderboard}
#| echo: false
#| results: asis

if (nrow(top20)) {

  cat('<div class="ch-leaderboard">')

  for (i in seq_len(nrow(top20))) {

    meeting_pct <- round(top20$tracked_meeting_attendance_pct[i])
    min_pct <- round(top20$normalized_minutes_pct[i])

    cat(
      '<div class="ch-person">',
        '<div class="ch-rank">', i, '</div>',
        '<div class="ch-person-name">', esc(top20$name[i]), '</div>',

        '<div class="ch-bar-block">',
          '<div class="ch-bar-label">',
            '<span>Meeting attendance</span>',
            '<span class="ch-bar-value">',
              meeting_pct, '% · ',
              top20$meetings_attended[i], ' of ', n_meetings,
            '</span>',
          '</div>',
          '<div class="ch-track">',
            '<div class="ch-fill" style="width:', meeting_pct, '%;"></div>',
          '</div>',
        '</div>',

        '<div class="ch-bar-block">',
          '<div class="ch-bar-label">',
            '<span>Participation time</span>',
            '<span class="ch-bar-value">',
              min_pct, '% · ',
              round(top20$total_minutes[i]), ' min',
            '</span>',
          '</div>',
          '<div class="ch-track">',
            '<div class="ch-fill coral" style="width:', min_pct, '%;"></div>',
          '</div>',
        '</div>',
      '</div>'
    )
  }

  cat('</div>')
}
```
</section>

<section class="ch-section">
<div class="ch-section-head">
<div class="ch-eyebrow">Academic–industry participation</div>

## Industry collaborators

<p>
Industry colleagues are recognized separately rather than included in the academic / clinical participation ranking. Company assignment is based primarily on email domain, with a small person-level override table embedded directly in this page for older attendance exports whose email was not captured. Known colleagues who participated from shared rooms—or whose participation is confirmed from historical meeting correspondence when the Teams attendance export is no longer available—are also acknowledged without assigning invented attendance minutes.
</p>
</div>

```{r industry-recognition}
#| echo: false
#| results: asis

if (nrow(company_summary)) {

  cat('<div class="ch-industry-grid">')

  for (company_name in company_summary$company) {

    company_people <- industry_summary |>
      filter(company == company_name) |>
      arrange(desc(meetings_attended), desc(total_minutes), name)

    company_row <- company_summary |>
      filter(company == company_name) |>
      slice(1)

    cat(
      '<div class="ch-industry-card">',
        '<h3>', esc(company_name), '</h3>',
        '<div class="ch-industry-meta">',
          company_row$unique_colleagues,
          ' colleagues represented · ',
          round(company_row$total_person_minutes / 60),
          ' individually tracked person-hours',
        '</div>',
        '<div class="ch-industry-names">'
    )

    for (j in seq_len(nrow(company_people))) {
      cat(
        '<span class="ch-industry-name">',
        esc(company_people$name[j]),
        '</span>'
      )
    }

    cat(
        '</div>',
      '</div>'
    )
  }

  cat('</div>')
}
```
</section>

<section class="ch-section">
<div class="ch-section-head">
<div class="ch-eyebrow">What is represented</div>

## Meetings in the current attendance archive

<p>
This page processes the <code>Attendance Over Time</code> archive directly. As new <code>attendance_clean.csv</code> files are added, the page updates automatically on render.
</p>
</div>

```{r meeting-archive}
#| echo: false
#| results: asis

if (nrow(meeting_summary)) {

  meeting_show <- meeting_summary |>
    arrange(desc(meeting_date), meeting_folder)

  cat('<div class="ch-meeting-grid">')

  for (i in seq_len(nrow(meeting_show))) {

    title <- str_remove(
      meeting_show$meeting_folder[i],
      "^[A-Za-z]+\\s+\\d{1,2}\\s+\\d{4}\\s*-\\s*"
    )

    date_display <- format_meeting_date(
      as.Date(meeting_show$meeting_date[i])
    )

    cat(
      '<div class="ch-meeting">',
        '<div class="ch-meeting-type">',
          esc(meeting_show$meeting_type[i]),
        '</div>',
        '<div class="ch-meeting-title">',
          esc(title),
        '</div>',
        '<div class="ch-meeting-meta">',
          esc(date_display),
          ' · ',
          meeting_show$academic_people[i],
          ' academic / clinical',
          if (meeting_show$industry_people[i] > 0)
            paste0(
              ' · ',
              meeting_show$industry_people[i],
              ' industry'
            )
          else '',
        '</div>',
      '</div>'
    )
  }

  cat('</div>')
}
```
</section>

</div>
