---
title: "DAROMUN / PIVOTAL"
pagetitle: "DAROMUN / PIVOTAL | SoCO Journal Club Recap"
description: "Meeting recap from the September 25, 2026 Society of Cutaneous Oncology Journal Club discussing the PIVOTAL phase III update of neoadjuvant intralesional DAROMUN in resectable locally advanced melanoma."
date: 2026-09-25
author: "Society of Cutaneous Oncology"
categories:
  - 2026
  - Journal Club
  - Melanoma
  - Neoadjuvant Therapy
  - Intralesional Therapy
tags:
  - DAROMUN
  - PIVOTAL
  - L19IL2
  - L19TNF
  - Melanoma
  - Neoadjuvant Therapy
page-layout: full
title-block-style: none
toc: false
execute:
  echo: false
  warning: false
  message: false
---

<style>
  :root {
    --navy: #082D4D;
    --teal: #28A9A2;
    --coral: #E25A4E;
    --ink: #31424E;
    --muted: #6B747B;
    --pale: #F3F8F8;
    --line: #D9E8E8;
  }

  #title-block-header,
  .quarto-title-block,
  .quarto-title,
  .quarto-title-meta {
    display: none !important;
  }

  body { color: var(--ink); background: #fff; }
  main.content {
    width: 100%;
    max-width: 1120px;
    min-width: 0;
    margin: auto;
    padding-top: 0 !important;
  }

  main.content,
  main.content * {
    box-sizing: border-box;
  }
  h1,h2,h3 { color: var(--navy); font-weight: 800; }

  .hero {
    margin: 2rem 0 2.4rem;
    padding: 2.8rem 3rem;
    border-radius: 24px;
    background:
      radial-gradient(circle at 88% 12%, rgba(40,169,162,.11), transparent 31%),
      linear-gradient(135deg,#F3F8F8 0%,#FFFFFF 72%);
    border: 1px solid var(--line);
    box-shadow: 0 10px 30px rgba(8,45,77,.07);
  }

  .kicker,.section-kicker {
    color: var(--teal);
    font-weight: 800;
    letter-spacing: .15em;
    text-transform: uppercase;
    font-size: .8rem;
  }

  .hero h1 {
    max-width: 900px;
    font-size: clamp(2.7rem,5vw,4.1rem);
    line-height: 1.02;
    margin: .55rem 0 .8rem;
    letter-spacing: -.04em;
  }

  .hero-copy {
    font-size: 1.2rem;
    max-width: 850px;
    color: #56636D;
    line-height: 1.65;
  }

  .accent {
    width: 94px;
    height: 5px;
    border-radius: 4px;
    background: linear-gradient(90deg,var(--teal) 0 68%,var(--coral) 68%);
    margin-top: 1.4rem;
  }

  .metric-grid {
    display: grid;
    grid-template-columns: repeat(3,1fr);
    gap: 1rem;
    margin: 1.4rem 0 2rem;
  }

  .metric-card {
    border: 1px solid var(--line);
    border-radius: 18px;
    padding: 1.35rem 1.4rem;
    background: #fff;
    box-shadow: 0 6px 18px rgba(8,45,77,.05);
  }

  .metric-label {
    display: block;
    color: var(--muted);
    font-size: .8rem;
    font-weight: 800;
    text-transform: uppercase;
    letter-spacing: .09em;
  }

  .metric-value {
    display: block;
    color: var(--navy);
    font-size: 2.35rem;
    font-weight: 850;
    line-height: 1.05;
    margin: .35rem 0;
  }

  .metric-note { color: var(--muted); font-size: .92rem; line-height: 1.45; }

  .section-kicker { margin-top: 2.8rem; }

  .section-intro {
    font-size: 1.05rem;
    color: #56636D;
    max-width: 860px;
    margin-bottom: 1.2rem;
    line-height: 1.7;
  }

  .paper-card {
    max-width: 980px;
    margin: 1.2rem auto 2rem;
    padding: 1.75rem 2rem 1.7rem;
    border-left: 7px solid var(--teal);
    border-radius: 0 20px 20px 0;
    background: linear-gradient(135deg,rgba(40,169,162,.085),rgba(8,45,77,.035));
    box-shadow: 0 12px 30px rgba(8,45,77,.08);
  }

  .paper-eyebrow {
    color: var(--teal);
    font-size: .78rem;
    font-weight: 850;
    letter-spacing: .14em;
    text-transform: uppercase;
    margin-bottom: .65rem;
  }

  .paper-title {
    color: var(--navy);
    font-size: 1.62rem;
    line-height: 1.22;
    font-weight: 850;
    letter-spacing: -.015em;
    margin: 0 0 .85rem;
  }

  .paper-citation { color: #52616D; font-size: .98rem; line-height: 1.45; }

  .link-row {
    display:flex;
    flex-wrap:wrap;
    gap:.7rem;
    margin-top:1.2rem;
  }

  .soco-link {
    display:inline-flex;
    padding:.58rem .9rem;
    border-radius:999px;
    background:var(--navy);
    color:#fff !important;
    text-decoration:none;
    font-size:.88rem;
    font-weight:750;
  }

  .soco-link.secondary {
    background:#fff;
    border:1px solid rgba(40,169,162,.42);
    color:var(--navy) !important;
  }

  .question-card {
    margin: 1.6rem 0 2rem;
    padding: 1.55rem 1.7rem;
    border-left: 5px solid var(--coral);
    border-radius: 0 14px 14px 0;
    background: linear-gradient(135deg,rgba(226,90,78,.055),rgba(40,169,162,.045));
  }

  .question-card strong {
    display:block;
    color:var(--navy);
    font-size:1.2rem;
    line-height:1.55;
  }

  .highlight-grid {
    display:grid;
    grid-template-columns:repeat(2,minmax(0,1fr));
    gap:1rem;
    margin:1.2rem 0 1.5rem;
  }

  .highlight-card {
    border:1px solid #DCE8EB;
    border-radius:16px;
    padding:1.2rem 1.25rem;
    background:#fff;
    box-shadow:0 5px 18px rgba(8,45,77,.045);
  }

  .highlight-num {
    color:var(--coral);
    font-weight:900;
    font-size:.8rem;
    letter-spacing:.06em;
    text-transform:uppercase;
  }

  .highlight-card h3 {
    color:var(--navy);
    font-size:1.08rem;
    margin:.25rem 0 .55rem;
  }

  .highlight-card p {
    color:#405463;
    font-size:.94rem;
    line-height:1.5;
    margin:0;
  }

  .discussion-quote {
    margin:1.4rem 0;
    padding:1.1rem 1.25rem;
    border-left:5px solid var(--teal);
    background:#EFF8F7;
    border-radius:0 12px 12px 0;
    color:var(--navy);
    font-size:1.05rem;
    font-weight:700;
    line-height:1.45;
  }

  .caution-note {
    background:#FFF8F0;
    border-left:5px solid #E6A34A;
    padding:1rem 1.15rem;
    border-radius:0 12px 12px 0;
    color:#59462E;
    margin:1rem 0 1.5rem;
    font-size:.92rem;
    line-height:1.5;
  }

  .perspective-card {
    margin:2rem 0;
    padding:1.5rem 1.6rem;
    border:1px solid var(--line);
    border-radius:18px;
    background:
      radial-gradient(circle at 88% 12%,rgba(40,169,162,.10),transparent 28%),
      linear-gradient(135deg,#F7FBFB,#fff);
    box-shadow:0 8px 24px rgba(8,45,77,.05);
  }

  .perspective-card h3 { margin:.25rem 0 .65rem; }
  .perspective-card p { color:#52616D; line-height:1.65; margin-bottom:0; }


  .survey-grid {
    display:grid;
    grid-template-columns:repeat(3,minmax(0,1fr));
    gap:1rem;
    margin:1.2rem 0 1.5rem;
  }

  .survey-card {
    padding:1.25rem 1.3rem;
    border:1px solid var(--line);
    border-radius:16px;
    background:#fff;
    box-shadow:0 5px 18px rgba(8,45,77,.045);
  }

  .survey-value {
    display:block;
    color:var(--navy);
    font-size:2rem;
    font-weight:850;
    line-height:1.05;
    margin-bottom:.4rem;
  }

  .survey-label {
    display:block;
    color:var(--teal);
    font-size:.76rem;
    font-weight:850;
    letter-spacing:.08em;
    text-transform:uppercase;
    margin-bottom:.45rem;
  }

  .survey-copy {
    color:#52616D;
    font-size:.92rem;
    line-height:1.5;
  }

  .survey-note {
    margin:1.2rem 0 2rem;
    padding:1.15rem 1.25rem;
    border-left:5px solid var(--teal);
    border-radius:0 12px 12px 0;
    background:#EFF8F7;
    color:var(--navy);
    line-height:1.6;
  }

  /* =========================================================
     FULL SURVEY DISCLOSURE
     ========================================================= */

  .survey-disclosure {
    margin: 1.3rem 0 2.2rem;
  }

  .survey-toggle {
    width: 100%;
    display: grid;
    grid-template-columns: auto 1fr auto;
    gap: .9rem;
    align-items: center;
    padding: 1rem 1.15rem;
    border: 1px solid var(--line);
    border-radius: 16px;
    background:
      linear-gradient(135deg, #F3F8F8 0%, #FFFFFF 100%);
    color: var(--navy);
    text-align: left;
    cursor: pointer;
    box-shadow: 0 6px 18px rgba(8,45,77,.04);
  }

  .survey-toggle:hover {
    border-color: rgba(40,169,162,.48);
    box-shadow: 0 8px 24px rgba(8,45,77,.07);
  }

  .survey-toggle-badge {
    display: inline-flex;
    width: 38px;
    height: 38px;
    align-items: center;
    justify-content: center;
    border-radius: 50%;
    background: rgba(40,169,162,.12);
    color: var(--navy);
    font-size: 1.05rem;
  }

  .survey-toggle-copy strong {
    display: block;
    color: var(--navy);
    font-size: 1rem;
    font-weight: 850;
  }

  .survey-toggle-copy span {
    display: block;
    margin-top: .15rem;
    color: var(--muted);
    font-size: .84rem;
    line-height: 1.4;
  }

  .survey-toggle-icon {
    color: var(--teal);
    font-size: 1.3rem;
    font-weight: 900;
    transition: transform .2s ease;
  }

  .survey-toggle[aria-expanded="true"] .survey-toggle-icon {
    transform: rotate(45deg);
  }

  .survey-panel {
    display: none;
    margin-top: .8rem;
    padding: 1.1rem;
    border: 1px solid var(--line);
    border-radius: 16px;
    background: #fff;
  }

  .survey-panel.is-open {
    display: block;
  }

  .survey-panel-intro {
    margin: 0 0 1.15rem;
    padding: .85rem 1rem;
    border-left: 4px solid var(--teal);
    border-radius: 0 10px 10px 0;
    background: #F5FAFA;
    color: var(--muted);
    font-size: .9rem;
    line-height: 1.55;
  }

  .survey-question-label {
    color: var(--teal);
    font-size: .76rem;
    font-weight: 850;
    letter-spacing: .10em;
    text-transform: uppercase;
    margin: 1rem 0 .35rem;
  }

  .survey-figure-separator {
    margin: 1.5rem 0;
    border: 0;
    border-top: 1px solid #EDF2F4;
  }

  .survey-text-list {
    display: grid;
    gap: .55rem;
    margin-top: .5rem;
  }

  .survey-text-item {
    padding: .78rem .9rem;
    border: 1px solid var(--line);
    border-radius: 11px;
    background: #FAFCFC;
    color: #4B5E6C;
    font-size: .88rem;
    line-height: 1.5;
  }

  /* =========================================================
     PUBLICATION-STYLE PRE-MEETING SURVEY ARCHIVE
     ========================================================= */

  .survey-archive-details {
    margin: 1.25rem 0 2.25rem;
    overflow: hidden;
    border: 1px solid var(--line);
    border-radius: 18px;
    background: #fff;
    box-shadow: 0 8px 24px rgba(8,45,77,.045);
  }

  .survey-archive-details > summary {
    position: relative;
    display: grid;
    grid-template-columns: auto minmax(0,1fr) auto;
    gap: .9rem;
    align-items: center;
    padding: 1rem 3.4rem 1rem 1.1rem;
    cursor: pointer;
    list-style: none;
    background: linear-gradient(135deg,#F3F8F8 0%,#FFFFFF 100%);
    color: var(--navy);
  }

  .survey-archive-details > summary::-webkit-details-marker { display:none; }

  .survey-archive-details > summary::after {
    content: "+";
    position: absolute;
    right: 1.15rem;
    top: 50%;
    transform: translateY(-50%);
    color: var(--teal);
    font-size: 1.55rem;
    font-weight: 500;
  }

  .survey-archive-details[open] > summary::after { content:"−"; }

  .survey-archive-badge {
    display:inline-flex;
    width:38px;
    height:38px;
    align-items:center;
    justify-content:center;
    border-radius:50%;
    background:rgba(40,169,162,.12);
    color:var(--navy);
    font-size:1rem;
    font-weight:800;
  }

  .survey-archive-title {
    display:block;
    color:var(--navy);
    font-size:1rem;
    font-weight:850;
  }

  .survey-archive-subtitle {
    display:block;
    margin-top:.15rem;
    color:var(--muted);
    font-size:.84rem;
    line-height:1.45;
  }

  .survey-archive-body {
    padding:1rem 1.1rem 1.2rem;
    background:#fff;
  }

  .survey-archive-intro {
    margin:0 0 1.05rem;
    padding:.9rem 1rem;
    border-left:4px solid var(--teal);
    border-radius:0 11px 11px 0;
    background:#F5FAFA;
    color:#586A75;
    font-size:.9rem;
    line-height:1.58;
  }

  .pub-survey-stack {
    display:grid;
    gap:1rem;
  }

  .pub-survey-panel {
    border:1px solid #DCE8EB;
    border-radius:17px;
    padding:1.15rem 1.2rem 1.2rem;
    background:#fff;
    box-shadow:0 5px 18px rgba(8,45,77,.035);
  }

  .pub-survey-kicker {
    color:var(--teal);
    font-size:.72rem;
    font-weight:850;
    letter-spacing:.11em;
    text-transform:uppercase;
    margin-bottom:.3rem;
  }

  .pub-survey-title {
    color:var(--navy);
    font-size:1.12rem;
    font-weight:850;
    line-height:1.28;
    margin:0;
  }

  .pub-survey-meta {
    color:var(--muted);
    font-size:.8rem;
    margin:.25rem 0 .9rem;
  }

  .pub-survey-context {
    max-width:900px;
    margin:.48rem 0 .35rem;
    padding:.72rem .82rem;
    border-left:4px solid var(--teal);
    border-radius:0 10px 10px 0;
    background:#F5FAFA;
    color:#526574;
    font-size:.86rem;
    line-height:1.5;
  }

  .pub-survey-context strong {
    color:var(--navy);
  }

  .pub-bar-list {
    display:grid;
    gap:.58rem;
  }

  .pub-bar-row {
    display:grid;
    grid-template-columns:minmax(190px,1.55fr) minmax(150px,2.1fr) 64px;
    gap:.75rem;
    align-items:center;
  }

  .pub-bar-label {
    color:#405463;
    font-size:.87rem;
    line-height:1.32;
  }

  .pub-bar-track {
    height:12px;
    border-radius:999px;
    background:#EDF3F4;
    overflow:hidden;
  }

  .pub-bar-fill {
    height:100%;
    border-radius:999px;
    background:linear-gradient(90deg,#198F8B,#51BBB5);
  }

  .pub-bar-fill.uncertainty {
    background:linear-gradient(90deg,#D9665C,#E98A7F);
  }

  .pub-bar-value {
    color:var(--navy);
    font-size:.84rem;
    font-weight:850;
    text-align:right;
    font-variant-numeric:tabular-nums;
  }

  .pub-vote-grid {
    display:grid;
    grid-template-columns:repeat(3,minmax(0,1fr));
    gap:.75rem;
  }

  .pub-vote-card {
    padding:1rem;
    border:1px solid var(--line);
    border-radius:14px;
    background:linear-gradient(135deg,#F8FBFB,#fff);
    text-align:center;
  }

  .pub-vote-label {
    color:var(--muted);
    font-size:.72rem;
    font-weight:850;
    letter-spacing:.09em;
    text-transform:uppercase;
  }

  .pub-vote-value {
    display:block;
    margin:.25rem 0 .15rem;
    color:var(--navy);
    font-size:1.8rem;
    line-height:1;
    font-weight:900;
  }

  .pub-vote-count {
    color:#6B747B;
    font-size:.78rem;
  }

  .survey-archive-note {
    margin:.9rem 0 0;
    color:var(--muted);
    font-size:.8rem;
    line-height:1.5;
  }

  .footer-card {
    margin:3rem 0 1rem;
    padding:1.8rem 2rem;
    background:var(--navy);
    color:#fff;
    border-radius:20px;
  }

  .footer-card h2 { color:#fff; margin-top:0; }
  .footer-card p { margin-bottom:0; color:#EAF2F5; }

  /* =========================================================
     COMMUNITY / ENGAGEMENT / ATTENDANCE
     ========================================================= */






  .engagement-spotlight {
    position: relative;
    overflow: hidden;
    margin: 1rem 0 1.4rem;
    padding: 1.35rem 1.45rem 1.25rem;
    border: 1px solid #E9C85F;
    border-left: 7px solid #D7A400;
    border-radius: 18px;
    background:
      radial-gradient(circle at 92% 18%, rgba(255,255,255,.58), transparent 28%),
      linear-gradient(135deg, #FFF8D8 0%, #FDE9A9 100%);
    box-shadow: 0 10px 28px rgba(116,83,0,.10);
  }

  .engagement-spotlight-title {
    display: flex;
    align-items: center;
    gap: .6rem;
    margin: 0 0 .35rem;
    color: #765308;
    font-size: 1.1rem;
    font-weight: 850;
    letter-spacing: -.01em;
  }

  .engagement-spotlight-copy {
    max-width: 900px;
    margin: 0;
    color: #735F2C;
    font-size: .94rem;
    line-height: 1.55;
  }

  .engagement-pill-row {
    display: flex;
    flex-wrap: wrap;
    gap: .55rem;
    margin-top: .95rem;
  }

  .engagement-pill {
    display: inline-flex;
    align-items: center;
    padding: .5rem .72rem;
    border: 1px solid rgba(118,83,8,.18);
    border-radius: 999px;
    background: rgba(255,255,255,.82);
    color: #57420D;
    font-size: .86rem;
    font-weight: 780;
    box-shadow: 0 2px 7px rgba(116,83,0,.08);
  }

  .engagement-method {
    margin: .75rem 0 0;
    color: #7C6B42;
    font-size: .78rem;
    line-height: 1.5;
  }





  .attendance-details {
    margin: 1rem 0 1.6rem;
    overflow: hidden;
    border: 1px solid var(--line);
    border-radius: 16px;
    background: #fff;
    box-shadow: 0 8px 24px rgba(8,45,77,.045);
  }

  .attendance-details > summary {
    position: relative;
    min-height: 64px;
    padding: 1rem 3.4rem 1rem 1.05rem;
    cursor: pointer;
    list-style: none;
    background: linear-gradient(135deg,#F3F8F8 0%,#FFFFFF 100%);
    color: var(--navy);
  }

  .attendance-details > summary::-webkit-details-marker {
    display: none;
  }

  .attendance-details > summary::after {
    content: "+";
    position: absolute;
    right: 1.1rem;
    top: 50%;
    transform: translateY(-50%);
    color: var(--teal);
    font-size: 1.65rem;
    font-weight: 500;
    line-height: 1;
  }

  .attendance-details[open] > summary::after {
    content: "−";
  }

  .attendance-summary-title {
    display: block;
    color: var(--navy);
    font-size: 1rem;
    font-weight: 850;
  }

  .attendance-summary-subtitle {
    display: block;
    margin-top: .18rem;
    color: var(--muted);
    font-size: .82rem;
    line-height: 1.45;
  }

  .roster-summary {
    display: flex;
    align-items: baseline;
    justify-content: space-between;
    gap: 1rem;
    margin: 0 0 .8rem;
    padding: .95rem 1.05rem;
    border: 1px solid var(--line);
    border-radius: 14px;
    background: #F9FBFB;
  }

  .roster-summary strong {
    color: var(--navy);
    font-size: 1rem;
  }

  .roster-summary span {
    color: var(--muted);
    font-size: .84rem;
  }

  .attendance-scroll {
    width: 100%;
    overflow-x: auto;
    -webkit-overflow-scrolling: touch;
    border-radius: 16px;
  }

  .attendance-table {
    width: 100%;
    min-width: 690px;
    border-collapse: separate;
    border-spacing: 0;
    overflow: hidden;
    border: 1px solid var(--line);
    border-radius: 16px;
    background: #fff;
    box-shadow: 0 8px 24px rgba(8,45,77,.045);
  }

  .attendance-table thead th {
    padding: .72rem .75rem;
    background: var(--navy);
    color: #fff;
    border: 0;
    font-size: .78rem;
    font-weight: 800;
    text-align: center;
  }

  .attendance-table thead th:first-child {
    text-align: left;
  }

  .attendance-table tbody td {
    padding: .66rem .75rem;
    border-top: 1px solid #E9EFF1;
    color: #334857;
    font-size: .88rem;
    text-align: center;
  }

  .attendance-table tbody tr:nth-child(even) td:not(.minutes-cell) {
    background: #FBFDFD;
  }

  .attendance-table tbody tr:hover td:not(.minutes-cell) {
    background: #F3F9F9;
  }

  .attendance-table .name-cell {
    color: var(--navy);
    font-weight: 750;
    text-align: left;
  }

  .attendance-table .minutes-cell {
    color: #17384C;
    font-variant-numeric: tabular-nums;
  }

  .attendance-table .signal-cell {
    color: #7A868E;
  }

  .attendance-table .signal-on {
    color: var(--teal);
    font-weight: 900;
  }

  .attendance-note {
    margin-top: .8rem;
    color: var(--muted);
    font-size: .82rem;
    line-height: 1.55;
  }


  /* =========================================================
     FIRST-MEETING RECOGNITION
     ========================================================= */

  .first-meeting-card {
    margin: 1rem 0 1.55rem;
    overflow: hidden;
    border: 1px solid #E7D4D0;
    border-radius: 16px;
    background: #fff;
    box-shadow: 0 6px 18px rgba(8,45,77,.04);
  }

  .first-meeting-heading {
    padding: .9rem 1rem;
    background: #FBE7E4;
    color: #A63F36;
    font-size: .9rem;
    font-weight: 850;
  }

  .first-meeting-scroll {
    width: 100%;
    overflow-x: auto;
    -webkit-overflow-scrolling: touch;
  }

  .first-meeting-table {
    width: 100%;
    min-width: 660px;
    margin: 0;
    border-collapse: collapse;
    background: #fff;
  }

  .first-meeting-table th {
    padding: .72rem .75rem;
    background: var(--navy);
    color: #fff;
    border: 0;
    font-size: .78rem;
    font-weight: 800;
    text-align: left;
  }

  .first-meeting-table td {
    padding: .72rem .75rem;
    border-top: 1px solid #E6ECEF;
    color: #405463;
    font-size: .88rem;
    line-height: 1.4;
    vertical-align: top;
  }

  .first-meeting-table td:first-child {
    color: var(--navy);
    font-weight: 800;
  }

  .first-meeting-table tbody tr:nth-child(even) td {
    background: #FBFDFD;
  }

  .first-meeting-note {
    margin: .72rem 1rem .9rem;
    color: var(--muted);
    font-size: .78rem;
    line-height: 1.5;
  }

  @media (max-width:760px) {
    /*
      MOBILE LAYOUT
      Quarto uses a page-level CSS grid. These rules:
      1) allow the content grid item and all custom children to shrink;
      2) use minmax(0,1fr) for mobile one-column layouts;
      3) keep intentionally wide attendance tables inside their own scroller;
      4) constrain archived survey figures to the viewport.
    */

    html,
    body {
      max-width: 100%;
      overflow-x: hidden;
    }

    #quarto-content,
    #quarto-content.page-columns,
    main.content,
    .page-columns .content {
      min-width: 0 !important;
      max-width: 100% !important;
    }

    main.content {
      width: 100% !important;
      margin: 0 !important;
      padding: 0 1rem !important;
    }

    main.content > *,
    .hero,
    .metric-grid,
    .metric-card,
    .paper-card,
    .question-card,
    .highlight-grid,
    .highlight-card,
    .discussion-quote,
    .caution-note,
    .perspective-card,
    .survey-grid,
    .survey-card,
    .survey-note,
    .survey-disclosure,
    .survey-toggle,
    .survey-toggle-copy,
    .survey-panel,
    .survey-text-list,
    .survey-text-item,
    .community-banner,
    .engagement-spotlight,
    .engagement-pill-row,
    .engagement-pill,
    .attendance-details,
    .roster-summary,
    .attendance-scroll,
    .attendance-note,
    .first-meeting-card,
    .first-meeting-scroll,
    .first-meeting-note,
    .footer-card,
    .link-row {
      min-width: 0;
      max-width: 100%;
    }

    .hero {
      margin: 1rem 0 1.8rem;
      padding: 1.55rem 1.1rem 1.45rem;
      border-radius: 18px;
    }

    .hero h1 {
      max-width: 100%;
      font-size: clamp(2rem, 9.5vw, 2.55rem);
      line-height: 1.04;
      letter-spacing: -.035em;
      overflow-wrap: anywhere;
    }

    .hero-copy {
      max-width: 100%;
      font-size: 1rem;
      line-height: 1.52;
    }

    .kicker,
    .section-kicker {
      font-size: .72rem;
      line-height: 1.45;
      letter-spacing: .11em;
      overflow-wrap: anywhere;
    }

    main.content h2 {
      max-width: 100%;
      font-size: clamp(1.55rem, 7vw, 2rem);
      line-height: 1.12;
      overflow-wrap: anywhere;
    }

    main.content h3,
    .paper-title {
      max-width: 100%;
      overflow-wrap: anywhere;
    }

    .metric-grid,
    .highlight-grid,
    .survey-grid {
      grid-template-columns: minmax(0,1fr);
      gap: .8rem;
    }

    .metric-card,
    .survey-card,
    .highlight-card {
      padding: 1.05rem 1.1rem;
      border-radius: 14px;
    }

    .metric-value,
    .survey-value {
      font-size: 2rem;
    }

    .paper-card {
      width: 100%;
      margin: 1rem 0 1.8rem;
      padding: 1.2rem 1rem;
      border-left-width: 5px;
      border-radius: 0 15px 15px 0;
    }

    .paper-title {
      font-size: 1.28rem;
    }

    .paper-citation {
      overflow-wrap: anywhere;
    }

    .link-row {
      display: grid;
      grid-template-columns: minmax(0,1fr);
      width: 100%;
      gap: .6rem;
    }

    .soco-link {
      width: 100%;
      max-width: 100%;
      justify-content: center;
      text-align: center;
      white-space: normal;
    }

    .question-card,
    .discussion-quote,
    .caution-note,
    .survey-note {
      padding: 1rem;
    }

    .perspective-card {
      width: 100%;
      padding: 1.15rem 1rem;
      border-radius: 16px;
    }

    .survey-toggle {
      grid-template-columns: auto minmax(0,1fr) auto;
      gap: .65rem;
      padding: .9rem;
    }

    .survey-toggle-copy strong,
    .survey-toggle-copy span {
      overflow-wrap: anywhere;
    }

    .survey-panel {
      width: 100%;
      padding: .85rem;
    }
    .survey-archive-body {
      padding:.8rem;
    }

    .pub-bar-row {
      grid-template-columns:minmax(0,1fr) 58px;
      gap:.45rem .65rem;
    }

    .pub-bar-label {
      grid-column:1 / -1;
    }

    .pub-bar-track {
      grid-column:1;
    }

    .pub-bar-value {
      grid-column:2;
    }

    .pub-vote-grid {
      grid-template-columns:minmax(0,1fr);
    }


    .survey-panel .cell,
    .survey-panel .cell-output,
    .survey-panel .cell-output-display,
    .survey-panel figure,
    .survey-panel .quarto-figure {
      min-width: 0;
      max-width: 100%;
    }

    .community-banner {
      padding: 1.15rem 1rem;
      border-radius: 16px;
    }

    .engagement-spotlight {
      padding: 1.1rem 1rem;
    }

    .engagement-pill-row {
      display: grid;
      grid-template-columns: minmax(0,1fr);
    }

    .engagement-pill {
      width: 100%;
      min-width: 0;
      justify-content: flex-start;
      white-space: normal;
    }

    .attendance-details > summary {
      min-height: 60px;
      padding: .85rem 3rem .85rem .9rem;
    }

    .attendance-summary-title {
      font-size: .92rem;
    }

    .attendance-summary-subtitle {
      font-size: .74rem;
    }

    .roster-summary {
      display: block;
      padding: .85rem .9rem;
    }

    .roster-summary span {
      display: block;
      margin-top: .3rem;
    }

    .attendance-scroll {
      width: 100%;
      max-width: 100%;
      margin: 0;
      padding-bottom: .3rem;
      overflow-x: auto;
      -webkit-overflow-scrolling: touch;
    }

    .attendance-table {
      width: 690px;
      min-width: 690px;
      max-width: none;
    }

    .footer-card {
      margin-top: 2.4rem;
      padding: 1.3rem 1.15rem;
      border-radius: 16px;
    }

    img,
    svg,
    video,
    iframe,
    canvas {
      max-width: 100%;
      height: auto;
    }
  }

  @media (max-width:420px) {
    main.content {
      padding-left: .85rem !important;
      padding-right: .85rem !important;
    }

    .hero {
      padding-left: 1rem;
      padding-right: 1rem;
    }

    .hero h1 {
      font-size: clamp(1.9rem, 9vw, 2.25rem);
    }

    .metric-value,
    .survey-value {
      font-size: 1.9rem;
    }

    .perspective-card {
      padding-left: .9rem;
      padding-right: .9rem;
    }

    .survey-toggle-badge {
      width: 34px;
      height: 34px;
    }

    .attendance-table {
      width: 620px;
      min-width: 620px;
    }
  }
</style>

```{r}
#| label: setup-recap

suppressPackageStartupMessages({
  library(tidyverse)
  library(scales)
})

# -------------------------------------------------------------------------
# Resolve this meeting folder.
# -------------------------------------------------------------------------
resolve_meeting_dir <- function() {

  if (
    exists("meeting_dir", inherits = TRUE) &&
    is.character(meeting_dir) &&
    length(meeting_dir) == 1 &&
    nzchar(meeting_dir) &&
    dir.exists(meeting_dir)
  ) {
    return(normalizePath(meeting_dir, winslash = "/", mustWork = TRUE))
  }

  current_input <- tryCatch(
    knitr::current_input(dir = TRUE),
    error = function(e) NULL
  )

  if (
    !is.null(current_input) &&
    length(current_input) == 1 &&
    !is.na(current_input) &&
    nzchar(current_input) &&
    file.exists(current_input)
  ) {
    return(dirname(normalizePath(current_input, winslash = "/", mustWork = TRUE)))
  }

  if (interactive() && requireNamespace("rstudioapi", quietly = TRUE)) {
    ctx <- tryCatch(
      rstudioapi::getSourceEditorContext(),
      error = function(e) NULL
    )

    if (!is.null(ctx) && !is.null(ctx$path) && nzchar(ctx$path)) {
      active_path <- normalizePath(ctx$path, winslash = "/", mustWork = TRUE)
      active_dir <- dirname(active_path)
      if (basename(active_path) == "index.qmd") return(active_dir)
      if (basename(active_dir) == "scripts") return(dirname(active_dir))
    }
  }

  stop(
    paste0(
      "Could not determine the Journal Club meeting directory.\n",
      "Render index.qmd with Quarto or open index.qmd in RStudio."
    )
  )
}

meeting_dir <- resolve_meeting_dir()

# -------------------------------------------------------------------------
# Attendance + roster: persistent SoCO registry is the source of truth.
#
# Raw Teams exports remain the provenance for participation, but identity,
# event metadata, organization-at-event, and current affiliation are resolved
# upstream in the registry. The recap should not maintain a parallel identity
# or affiliation system.
# -------------------------------------------------------------------------

find_soco_root <- function(start = getwd(), max_up = 12L) {
  here <- normalizePath(start, winslash = "/", mustWork = TRUE)

  for (i in 0:max_up) {
    if (
      dir.exists(file.path(here, "data", "registry")) &&
      dir.exists(file.path(here, "workflows", "registry"))
    ) {
      return(here)
    }

    parent <- dirname(here)
    if (identical(parent, here)) break
    here <- parent
  }

  stop(
    paste(
      "Could not locate the SoCO project root.",
      "Expected data/registry/ and workflows/registry/ under the same root."
    ),
    call. = FALSE
  )
}

soco_root <- find_soco_root(meeting_dir)

registry_view_script <- file.path(
  soco_root,
  "workflows",
  "registry",
  "R",
  "tools",
  "40_build_registry_views.R"
)

if (!file.exists(registry_view_script)) {
  stop(
    "Could not find registry view helper:\n",
    registry_view_script,
    call. = FALSE
  )
}

source(registry_view_script, local = TRUE)

daromun_event <- event_participation |>
  filter(event_id == "SOCO-E0009")

if (!nrow(daromun_event)) {
  stop(
    "SOCO-E0009 (DAROMUN PIVOTAL) has no registry-backed participation rows.",
    call. = FALSE
  )
}

if (
  daromun_event |>
    count(person_id) |>
    filter(n > 1) |>
    nrow() > 0
) {
  stop(
    "SOCO-E0009 contains duplicate person_id rows in event_participation.",
    call. = FALSE
  )
}

duration_available <- !all(is.na(daromun_event$duration_min))

headline <- tibble::tibble(
  people = n_distinct(daromun_event$person_id),
  median_minutes = if (duration_available) {
    median(daromun_event$duration_min, na.rm = TRUE)
  } else {
    NA_real_
  },
  pct_60min_plus = if (duration_available) {
    mean(daromun_event$duration_min >= 60, na.rm = TRUE)
  } else {
    NA_real_
  }
)

display_affiliation <- function(x) {
  x <- str_squish(as.character(x))

  case_when(
    is.na(x) | x == "" ~ "—",

    x %in% c(
      "Massachusetts General Hospital",
      "Brigham and Women's Hospital",
      "Mass General Brigham"
    ) ~ "Mass General Brigham",

    x == "Washington University School of Medicine in St. Louis" ~
      "Washington University in St. Louis",

    TRUE ~ x
  )
}

meeting_roster <- daromun_event |>
  transmute(
    name = name,
    affiliation = display_affiliation(
      coalesce(
        organization_at_event,
        current_affiliation
      )
    )
  ) |>
  distinct() |>
  arrange(name)

roster_n <- nrow(meeting_roster)

# -------------------------------------------------------------------------
# First SoCO meeting recognition.
#
# These names were identified during the live welcome / first-timer sequence.
# Tatyana Sharova is intentionally excluded because this was not her first
# SoCO meeting. The canonical registry name is used for Annekathryn Goodman;
# the transcript's nearby "Catherine" reference resolves to her speaker turn.
# -------------------------------------------------------------------------

first_meeting_specs <- tribble(
  ~canonical_name,         ~display_name,             ~role_override,
  "Alexis Rutt",           "Lexi Rutt",                "Regulatory Coordinator – Melanoma",
  "Patrick Kurpaska",      "Patrick Kurpaska",         "Medical Oncologist",
  "Shannon Saed",          "Shannon Saed",             "Medical Student / Research Fellow",
  "Sara Behbahani",        "Sara Behbahani",           "Mohs Fellow",
  "Annekathryn Goodman",   "Annekathryn Goodman",      "Gynecologic Oncologist"
)

first_meeting <- daromun_event |>
  filter(name %in% first_meeting_specs$canonical_name) |>
  select(
    person_id,
    canonical_name = name,
    current_title,
    organization_at_event,
    current_affiliation
  ) |>
  left_join(
    first_meeting_specs,
    by = "canonical_name"
  ) |>
  mutate(
    professional_role = coalesce(
      role_override,
      current_title,
      "—"
    ),
    institution = display_affiliation(
      coalesce(
        organization_at_event,
        current_affiliation
      )
    ),
    display_order = match(
      canonical_name,
      first_meeting_specs$canonical_name
    )
  ) |>
  arrange(display_order) |>
  select(
    name = display_name,
    professional_role,
    institution
  )

# -------------------------------------------------------------------------
# Survey assets.
#
# Preferred local home:
#   files/meeting recap-survey/
#
# If the files are not there, the recap also looks upward through the repo
# for workflows/journal_club/events/2026-09-25_daromun and finds the exact
# archived outputs there. This lets the Journal Club recap consume the
# workflow outputs without hard-coding a machine-specific absolute path.
# -------------------------------------------------------------------------
find_upward <- function(start_dir, relative_path) {
  current <- normalizePath(start_dir, winslash = "/", mustWork = TRUE)

  repeat {
    candidate <- file.path(current, relative_path)
    if (dir.exists(candidate)) return(candidate)

    parent <- dirname(current)
    if (identical(parent, current)) break
    current <- parent
  }

  NA_character_
}

workflow_dir <- find_upward(
  meeting_dir,
  file.path(
    "workflows",
    "journal_club",
    "events",
    "2026-09-25_daromun"
  )
)

find_recap_asset <- function(filename, required_columns = NULL) {
  search_dirs <- c(
    file.path(meeting_dir, "files", "meeting recap-survey"),
    workflow_dir
  )

  search_dirs <- unique(
    search_dirs[
      !is.na(search_dirs) &
        dir.exists(search_dirs)
    ]
  )

  for (d in search_dirs) {
    candidates <- list.files(
      d,
      recursive = TRUE,
      full.names = TRUE
    )

    hits <- candidates[
      basename(candidates) == filename
    ]

    if (!length(hits)) next

    for (hit in hits) {

      if (!is.null(required_columns)) {
        dat <- tryCatch(
          readr::read_csv(
            hit,
            n_max = 5,
            show_col_types = FALSE
          ),
          error = function(e) NULL
        )

        if (
          is.null(dat) ||
            !all(required_columns %in% names(dat))
        ) {
          next
        }
      }

      return(
        normalizePath(
          hit,
          winslash = "/",
          mustWork = TRUE
        )
      )
    }
  }

  NA_character_
}

question_summary_path <- find_recap_asset(
  "question_summary.csv",
  required_columns = c(
    "question",
    "phase",
    "response",
    "pct",
    "total"
  )
)

compelling_fig <- find_recap_asset("compelling_pre_post.png")
practice_fig <- find_recap_asset("practice_influence.png")

# The full pre-meeting archive lives in the pre_event_survey workflow. Use the
# privacy-safe aggregate export for closed questions. Starting familiarity is
# reconstructed only as an aggregate from the saved local analysis file; no
# respondent-level fields are ever printed to the recap.
pre_summary_path <- NA_character_
pre_analysis_path <- NA_character_
pre_audience_fig <- NA_character_

if (!is.na(workflow_dir)) {
  pre_summary_candidate <- file.path(
    workflow_dir,
    "pre_event_survey",
    "outputs",
    "presentation_export",
    "question_summary.csv"
  )
  pre_analysis_candidate <- file.path(
    workflow_dir,
    "pre_event_survey",
    "data",
    "processed_private",
    "responses",
    "daromun_preJC_v3_analysis.csv"
  )
  pre_audience_candidate <- file.path(
    workflow_dir,
    "pre_event_survey",
    "outputs",
    "presentation_export",
    "figures",
    "audience_snapshot.png"
  )

  if (file.exists(pre_summary_candidate)) {
    pre_summary_path <- normalizePath(pre_summary_candidate, winslash = "/", mustWork = TRUE)
  }
  if (file.exists(pre_analysis_candidate)) {
    pre_analysis_path <- normalizePath(pre_analysis_candidate, winslash = "/", mustWork = TRUE)
  }
  if (file.exists(pre_audience_candidate)) {
    pre_audience_fig <- normalizePath(pre_audience_candidate, winslash = "/", mustWork = TRUE)
  }
}

pre_summary <- tibble::tibble()
pre_analysis <- tibble::tibble()

if (!is.na(pre_summary_path)) {
  pre_summary <- readr::read_csv(pre_summary_path, show_col_types = FALSE)
}

if (!is.na(pre_analysis_path)) {
  pre_analysis <- readr::read_csv(pre_analysis_path, show_col_types = FALSE)
}

pre_lookup_prop <- function(question_name, response_name) {
  if (!nrow(pre_summary)) return(NA_real_)
  x <- pre_summary |>
    dplyr::filter(
      question == question_name,
      response == response_name
    ) |>
    dplyr::pull(proportion)
  if (!length(x)) NA_real_ else x[[1]]
}

pre_scenario_daromun_pct <- pre_lookup_prop(
  "clinical_scenario",
  "DAROMUN → surgery"
)

pre_scenario_need_info_pct <- pre_lookup_prop(
  "clinical_scenario",
  "I’d need more information before deciding"
)

pre_priority_modern_pct <- pre_lookup_prop(
  "discussion_priority",
  "How DAROMUN compares with modern neoadjuvant systemic therapy"
)

pre_adcom_yes_pct <- pre_lookup_prop(
  "adcom_evaluable_meaningful",
  "Yes"
)

# Fallback values are the archived September 25 outputs. If the CSV is found,
# the values below are replaced dynamically from the archived data.
pre_n <- 49L
post_n <- 21L
pre_very_pct <- 0.0816326531
pre_unsure_pct <- 0.4489795918
post_very_pct <- 0.6190476190
post_moderate_pct <- 0.3809523810
practice_high_pct <- 0.6666666667  # practice-changing + substantially

if (!is.na(question_summary_path)) {
  qs <- readr::read_csv(question_summary_path, show_col_types = FALSE)

  get_pct <- function(question_name, phase_name, response_name) {
    x <- qs |>
      filter(
        question == question_name,
        phase == phase_name,
        response == response_name
      ) |>
      pull(pct)
    if (length(x) == 0) NA_real_ else x[1]
  }

  get_total <- function(question_name, phase_name) {
    x <- qs |>
      filter(question == question_name, phase == phase_name) |>
      pull(total) |>
      unique()
    if (length(x) == 0) NA_integer_ else as.integer(x[1])
  }

  pre_n <- get_total("evidence_compelling", "Before JC")
  post_n <- get_total("evidence_compelling", "After JC")
  pre_very_pct <- get_pct("evidence_compelling", "Before JC", "Very compelling")
  pre_unsure_pct <- get_pct(
    "evidence_compelling",
    "Before JC",
    "Unsure / need to understand the data better"
  )
  post_very_pct <- get_pct("evidence_compelling", "After JC", "Very compelling")
  post_moderate_pct <- get_pct("evidence_compelling", "After JC", "Moderately compelling")

  practice_high_pct <- sum(
    qs |>
      filter(
        question == "practice_influence",
        phase == "After JC",
        response %in% c("Practice-changing", "Substantially")
      ) |>
      pull(pct),
    na.rm = TRUE
  )
}

# -------------------------------------------------------------------------
# Community roster is already built above from registry-backed
# event_participation for SOCO-E0009.
# -------------------------------------------------------------------------
```

:::: {.hero}

::: {.kicker}
SoCO Journal Club · September 25, 2026
:::

# DAROMUN / PIVOTAL

::: {.hero-copy}
The randomized efficacy signal was compelling. The harder question was where a locally delivered neoadjuvant therapy belongs in a melanoma treatment landscape that changed while PIVOTAL was being conducted.
:::

::: {.accent}
:::

::::

::: {.section-kicker}
Meeting pulse
:::

## A large group stayed for a long discussion

::: {.metric-grid}

::: {.metric-card}
[People who joined]{.metric-label}

[`r ifelse(is.na(headline$people), "—", headline$people)`]{.metric-value}

[Unique people linked to SOCO-E0009 in the persistent registry]{.metric-note}
:::

::: {.metric-card}
[Median time together]{.metric-label}

[`r ifelse(is.na(headline$median_minutes), "—", paste0(round(headline$median_minutes), " min"))`]{.metric-value}

[Half the group stayed at least this long]{.metric-note}
:::

::: {.metric-card}
[Stayed at least an hour]{.metric-label}

[`r ifelse(is.na(headline$pct_60min_plus), "—", scales::percent(headline$pct_60min_plus, accuracy = 1))`]{.metric-value}

[Joined for at least 60 minutes]{.metric-note}
:::

:::

::: {.section-kicker}
The paper we discussed
:::

## PIVOTAL — the longer follow-up

:::: {.paper-card}

::: {.paper-eyebrow}
Phase III update · Journal of Clinical Oncology · 2026
:::

::: {.paper-title}
Neoadjuvant intralesional L19IL2/L19TNF (DAROMUN) in resectable locally advanced melanoma
:::

::: {.paper-citation}
**Hauschild A, et al.** *J Clin Oncol.* 2026.  
doi: 10.1200/JCO-26-00852
:::

::: {.link-row}
[DOI](https://ascopubs.org/doi/10.1200/JCO-26-00852){.soco-link}
:::

::::

::: {.question-card}
**The question beneath the paper:** PIVOTAL showed a durable randomized recurrence benefit. But how should that result be interpreted — and used — in a contemporary neoadjuvant era?
:::

The 2026 update extended median follow-up to **36.8 months** and reported updated relapse-free survival (RFS), distant metastasis-free survival (DMFS), safety, and post hoc event-free survival (EFS) analyses. The intention-to-treat population included **256 patients**, of whom **222 had recurrent disease**.

The updated RFS analysis remained strongly separated: **HR 0.55**, with median RFS of **23.8 months** with DAROMUN followed by surgery versus **6.5 months** with surgery alone.

::: {.caution-note}
**The interpretive challenge:** this was a randomized trial, but not a head-to-head comparison with contemporary neoadjuvant checkpoint strategies. Its population was predominantly recurrent and often previously treated, making direct cross-trial placement difficult.
:::

::: {.section-kicker}
Starting position
:::

## The pre-meeting survey captured more than confidence

::: {.section-intro}
The pre-Journal Club pulse captured where the room was starting: how compelling the PIVOTAL evidence seemed, what clinicians would do with a recurrent, injectable melanoma after prior anti–PD-1, whether the efficacy result felt clinically meaningful, and which uncertainty most needed discussion.
:::

::: {.survey-grid}

::: {.survey-card}
[`r scales::percent(pre_unsure_pct, accuracy = 1)`]{.survey-value}
[Needed more context]{.survey-label}

::: {.survey-copy}
Before the session, this was the largest single response to the evidence question; only `r scales::percent(pre_very_pct, accuracy = 1)` called the evidence very compelling.
:::
:::

::: {.survey-card}
[`r ifelse(is.na(pre_scenario_daromun_pct), "—", scales::percent(pre_scenario_daromun_pct, accuracy = 1))`]{.survey-value}
[Would choose DAROMUN → surgery]{.survey-label}

::: {.survey-copy}
In the recurrent, injectable post–anti–PD-1 scenario, relatively few respondents entered the meeting already choosing DAROMUN followed by surgery.
:::
:::

::: {.survey-card}
[`r ifelse(is.na(pre_priority_modern_pct), "—", scales::percent(pre_priority_modern_pct, accuracy = 1))`]{.survey-value}
[Wanted the modern comparator question]{.survey-label}

::: {.survey-copy}
The most important agenda item was how DAROMUN should be interpreted alongside contemporary neoadjuvant systemic therapy.
:::
:::

:::

<details class="survey-archive-details">
<summary>
  <span class="survey-archive-badge">▤</span>
  <span>
    <span class="survey-archive-title">Explore the full pre-meeting survey</span>
    <span class="survey-archive-subtitle">Open the complete closed-question results: audience, starting familiarity, evidence, clinical choice, regulatory-style vote, and discussion priorities.</span>
  </span>
</summary>

<div class="survey-archive-body">

<p class="survey-archive-intro">
These are the archived <strong>pre-discussion</strong> responses from September 25, preserving the room’s starting point across the closed survey questions.
</p>

```{r}
#| label: full-pre-survey-archive
#| echo: false
#| message: false
#| warning: false
#| results: asis

html_escape_survey <- function(x) {
  x <- replace_na(as.character(x), "")
  x <- stringr::str_replace_all(x, "&", "&amp;")
  x <- stringr::str_replace_all(x, "<", "&lt;")
  x <- stringr::str_replace_all(x, ">", "&gt;")
  x <- stringr::str_replace_all(x, '"', "&quot;")
  x
}

pct_label <- function(x) {
  ifelse(is.na(x), "—", paste0(round(100 * x), "%"))
}

render_bar_panel <- function(df, kicker, title, sort_desc = FALSE, context = NULL) {

  if (!nrow(df)) return(invisible(NULL))

  df <- df |>
    dplyr::filter(!is.na(response), response != "")

  if (sort_desc) {
    df <- df |>
      dplyr::arrange(dplyr::desc(proportion), response)
  }

  denom <- suppressWarnings(max(df$denominator, na.rm = TRUE))
  if (!is.finite(denom)) denom <- NA_real_

  cat('<section class="pub-survey-panel">')
  cat('<div class="pub-survey-kicker">', html_escape_survey(kicker), '</div>', sep = "")
  cat('<h3 class="pub-survey-title">', html_escape_survey(title), '</h3>', sep = "")
  if (!is.null(context) && nzchar(context)) {
    cat(
      '<div class="pub-survey-context"><strong>Clinical scenario:</strong> ',
      html_escape_survey(context),
      '</div>',
      sep = ""
    )
  }
  cat('<div class="pub-survey-meta">Pre-meeting pulse · n = ', ifelse(is.na(denom), "—", denom), '</div>', sep = "")
  cat('<div class="pub-bar-list">')

  for (i in seq_len(nrow(df))) {
    label <- as.character(df$response[[i]])
    prop <- suppressWarnings(as.numeric(df$proportion[[i]]))
    width <- ifelse(is.na(prop), 0, max(0, min(100, 100 * prop)))
    uncertainty <- stringr::str_detect(
      stringr::str_to_lower(label),
      "unsure|need more|need to understand|more information"
    )

    cat('<div class="pub-bar-row">')
    cat('<div class="pub-bar-label">', html_escape_survey(label), '</div>', sep = "")
    cat('<div class="pub-bar-track"><div class="pub-bar-fill', ifelse(uncertainty, ' uncertainty', ''), '" style="width:', sprintf('%.1f', width), '%"></div></div>', sep = "")
    cat('<div class="pub-bar-value">', pct_label(prop), '</div>', sep = "")
    cat('</div>')
  }

  cat('</div></section>')
}

render_vote_panel <- function(df) {

  if (!nrow(df)) return(invisible(NULL))

  denom <- suppressWarnings(max(df$denominator, na.rm = TRUE))
  if (!is.finite(denom)) denom <- NA_real_

  cat('<section class="pub-survey-panel">')
  cat('<div class="pub-survey-kicker">A regulatory-style threshold</div>')
  cat('<h3 class="pub-survey-title">Are the PIVOTAL efficacy results evaluable and clinically meaningful?</h3>')
  cat('<div class="pub-survey-meta">Pre-meeting pulse · n = ', ifelse(is.na(denom), "—", denom), '</div>', sep = "")
  cat('<div class="pub-vote-grid">')

  for (i in seq_len(nrow(df))) {
    cat('<div class="pub-vote-card">')
    cat('<span class="pub-vote-label">', html_escape_survey(df$response[[i]]), '</span>', sep = "")
    cat('<span class="pub-vote-value">', pct_label(df$proportion[[i]]), '</span>', sep = "")
    cat('<span class="pub-vote-count">', df$n[[i]], ' respondent', ifelse(df$n[[i]] == 1, '', 's'), '</span>', sep = "")
    cat('</div>')
  }

  cat('</div></section>')
}

cat('<div class="pub-survey-stack">')

if (nrow(pre_summary)) {

  role_df <- pre_summary |> dplyr::filter(question == "primary_role")
  evidence_df <- pre_summary |> dplyr::filter(question == "evidence_compelling")
  scenario_df <- pre_summary |> dplyr::filter(question == "clinical_scenario")
  priority_df <- pre_summary |> dplyr::filter(question == "discussion_priority")
  adcom_df <- pre_summary |> dplyr::filter(question == "adcom_evaluable_meaningful")

  render_bar_panel(
    role_df,
    "Who answered?",
    "A multidisciplinary respondent group",
    sort_desc = TRUE
  )

  if (nrow(pre_analysis) && "entry_familiarity" %in% names(pre_analysis)) {
    familiarity_df <- pre_analysis |>
      dplyr::transmute(response = stringr::str_squish(as.character(entry_familiarity))) |>
      dplyr::filter(!is.na(response), response != "") |>
      dplyr::count(response, name = "n") |>
      dplyr::mutate(
        denominator = sum(n),
        proportion = n / denominator
      )

    render_bar_panel(
      familiarity_df,
      "Starting familiarity",
      "How familiar was the room with DAROMUN / PIVOTAL?",
      sort_desc = FALSE
    )
  }

  render_bar_panel(
    evidence_df,
    "Starting position",
    "How compelling was the evidence before discussion?",
    sort_desc = FALSE
  )

  render_vote_panel(adcom_df)

  render_bar_panel(
    scenario_df,
    "A patient in front of you",
    "What would respondents recommend before the discussion?",
    sort_desc = FALSE,
    context = paste(
      "Resectable, injectable locoregional recurrence after prior surgery and adjuvant anti–PD-1.",
      "No distant disease. Assume DAROMUN is available."
    )
  )

  render_bar_panel(
    priority_df,
    "Set the agenda",
    "What most needed discussion?",
    sort_desc = TRUE
  )

} else {
  cat(
    '<div class="caution-note"><strong>Pre-meeting aggregate file not found.</strong> ',
    'Expected <code>pre_event_survey/outputs/presentation_export/question_summary.csv</code> ',
    'inside the DAROMUN workflow.</div>'
  )
}

cat('</div>')
```

<p class="survey-archive-note">
The survey is a descriptive snapshot of SoCO respondents, not a representative estimate of melanoma practice nationally or internationally. Percentages use the non-missing denominator for each question.
</p>

</div>
</details>

::: {.section-kicker}
Before → after
:::

## The community's view changed sharply after the discussion

::: {.section-intro}
Before Journal Club, only `r scales::percent(pre_very_pct, accuracy = 1)` of `r pre_n` respondents rated the evidence **very compelling**, while `r scales::percent(pre_unsure_pct, accuracy = 1)` said they needed to understand the data better. After the discussion, `r scales::percent(post_very_pct, accuracy = 1)` of `r post_n` post-JC respondents selected **very compelling** and the remainder selected **moderately compelling**.
:::

```{r}
#| label: compelling-pre-post
#| results: asis
#| fig-align: center
#| out-width: "100%"

if (!is.na(compelling_fig)) {
  knitr::include_graphics(compelling_fig)
} else {
  cat(
    '<div class="caution-note"><strong>Figure not found.</strong> ',
    'Place <code>compelling_pre_post.png</code> in ',
    '<code>files/meeting recap-survey/</code>, or keep the archived workflow ',
    'under <code>workflows/journal_club/events/2026-09-25_daromun/</code>.</div>'
  )
}
```

::: {.caution-note}
**Important:** the pre- and post-meeting surveys represent aggregate respondent groups rather than paired individual responses. The shift should therefore be interpreted as a change in the distribution of responses, not as documented person-level conversion.
:::

::: {.section-kicker}
Practice signal
:::

## Compelling did not automatically mean practice-changing

::: {.section-intro}
The post-JC question deliberately separated belief in the evidence from its immediate influence on care. `r scales::percent(practice_high_pct, accuracy = 1)` of post-JC respondents said the results should influence current clinical practice **substantially** or be **practice-changing** — a strong signal, but not the same as universal adoption.
:::

```{r}
#| label: practice-influence
#| results: asis
#| fig-align: center
#| out-width: "100%"

if (!is.na(practice_fig)) {
  knitr::include_graphics(practice_fig)
} else {
  cat(
    '<div class="caution-note"><strong>Figure not found.</strong> ',
    'Place <code>practice_influence.png</code> in ',
    '<code>files/meeting recap-survey/</code>, or keep the archived workflow ',
    'under <code>workflows/journal_club/events/2026-09-25_daromun/</code>.</div>'
  )
}
```

::: {.section-kicker}
Discussion highlights
:::

## What the room wrestled with

<div class="highlight-grid">

<div class="highlight-card">
<h3>1 · The efficacy signal survived scrutiny</h3>
<p><strong>Beth Buchbinder</strong> walked the group through the RFS curves and their early separation. <strong>Michael Wong</strong> went further, arguing that the DMFS signal was especially important because it suggested a systemic effect from a locally delivered therapy.</p>
</div>

<div class="highlight-card">
<h3>2 · The neoadjuvant window has to count</h3>
<p>A preoperative strategy cannot be judged only among patients who ultimately reach surgery. <strong>Michael Wong</strong> emphasized that RFS and EFS start different clocks, while <strong>Alfredo Covelli</strong> provided study-team context on why EFS has become more prominent in current neoadjuvant development.</p>
</div>

<div class="highlight-card">
<h3>3 · PIVOTAL studied a different population</h3>
<p><strong>Isaac Brownell</strong> challenged whether the population was comparable with modern neoadjuvant trials at all. <strong>Nikhil Khushalani</strong> sharpened the question: what would this same recurrent, often previously treated population have looked like with contemporary systemic neoadjuvant therapy?</p>
</div>

<div class="highlight-card">
<h3>4 · Safety may be an important differentiator</h3>
<p><strong>Sunandana Chandra</strong> focused on the severe and sometimes life-altering immune toxicities seen with systemic neoadjuvant therapy. <strong>Isaac Brownell</strong> and <strong>Michael Wong</strong> framed the potential advantage as a different benefit–risk tradeoff rather than proof of comparative superiority.</p>
</div>

<div class="highlight-card">
<h3>5 · Patient selection is now the harder question</h3>
<p><strong>Vishal Patel</strong> pushed on practical injection-site toxicity and whether inflammatory breakdown should be interpreted differently when the injected lesion is headed to surgery. He also surfaced questions from <strong>Aubri McEvoy</strong> about molecular selection and what to do after an inadequate pathologic response.</p>
</div>

</div>

::: {.section-kicker}
Where the discussion landed
:::

## The question changed from “does it work?” to “where do I use it?”

::: {.perspective-card}
The meeting ended in a more interesting place than it began. The group largely moved beyond whether PIVOTAL demonstrated a meaningful randomized treatment effect. The unresolved questions were comparative and practical: where DAROMUN fits alongside contemporary neoadjuvant immunotherapy, which patients are best suited for a locally delivered strategy, how toxicity should enter that choice, and which endpoint best captures the full preoperative treatment experience.
:::

::: {.caution-note}
**Where this recap intentionally stops:** the purpose here is to preserve the community's encounter with the evidence — the starting uncertainty, the discussion, the change in aggregate opinion, and the questions that remained. A separate JoCO **Perspective on the Science** can take the next step: external synthesis, comparative positioning, methodological critique, and a durable thesis about where this strategy belongs.
:::

::: {.section-kicker}
Our community
:::

## Who joined us?

```{r}
#| label: first-soco-meeting
#| results: asis

escape_first_meeting <- function(x) {
  x <- replace_na(as.character(x), "")
  x <- stringr::str_replace_all(x, "&", "&amp;")
  x <- stringr::str_replace_all(x, "<", "&lt;")
  x <- stringr::str_replace_all(x, ">", "&gt;")
  x <- stringr::str_replace_all(x, '"', "&quot;")
  x
}

if (nrow(first_meeting)) {

  cat('<div class="first-meeting-card">')
  cat('<div class="first-meeting-heading">👋 First SoCO Meeting</div>')
  cat('<div class="first-meeting-scroll">')
  cat('<table class="first-meeting-table">')
  cat(
    '<thead><tr>',
    '<th>Name</th>',
    '<th>Professional role</th>',
    '<th>Institution</th>',
    '</tr></thead>'
  )
  cat('<tbody>')

  for (i in seq_len(nrow(first_meeting))) {
    cat(
      '<tr>',
      '<td>', escape_first_meeting(first_meeting$name[[i]]), '</td>',
      '<td>', escape_first_meeting(first_meeting$professional_role[[i]]), '</td>',
      '<td>', escape_first_meeting(first_meeting$institution[[i]]), '</td>',
      '</tr>',
      sep = ""
    )
  }

  cat('</tbody></table></div>')
  cat(
    '<div class="first-meeting-note">',
    'A special welcome to colleagues joining SoCO for the first time.',
    '</div>'
  )
  cat('</div>')
}
```

:::: {.engagement-spotlight}

::: {.engagement-spotlight-title}
💬 Voices that shaped the discussion
:::

::: {.engagement-spotlight-copy}
Beth Buchbinder, Michael Wong, Isaac Brownell, Nikhil Khushalani, Sunandana Chandra, and Vishal Patel repeatedly sharpened the discussion across efficacy, trial interpretation, safety, and patient selection.
:::

::: {.engagement-pill-row}
[Beth Buchbinder]{.engagement-pill}
[Michael Wong]{.engagement-pill}
[Isaac Brownell]{.engagement-pill}
[Nikhil Khushalani]{.engagement-pill}
[Sunandana Chandra]{.engagement-pill}
[Vishal Patel]{.engagement-pill}
:::

::: {.engagement-method}
Alfredo Covelli added study-team context throughout the discussion, and Aubri McEvoy's questions helped push the conversation toward molecular selection and management after an inadequate pathologic response.
:::

::::

```{r}
#| label: attendance-roster
#| results: asis

escape_html <- function(x) {
  x <- replace_na(as.character(x), "")
  x <- stringr::str_replace_all(x, "&", "&amp;")
  x <- stringr::str_replace_all(x, "<", "&lt;")
  x <- stringr::str_replace_all(x, ">", "&gt;")
  x <- stringr::str_replace_all(x, '"', "&quot;")
  x
}

if (nrow(meeting_roster)) {

  cat('<details class="attendance-details">')
  cat('<summary>')
  cat(
    '<span class="attendance-summary-title">',
    roster_n,
    ' people represented</span>',
    sep = ""
  )
  cat(
    '<span class="attendance-summary-subtitle">',
    'View attendance and affiliations',
    '</span>',
    sep = ""
  )
  cat('</summary>')

  cat('<div class="attendance-scroll">')
  cat('<table class="attendance-table">')
  cat('<thead><tr><th>Name</th><th>Affiliation</th></tr></thead>')
  cat('<tbody>')

  for (i in seq_len(nrow(meeting_roster))) {
    cat(
      '<tr>',
      '<td class="name-cell">', escape_html(meeting_roster$name[[i]]), '</td>',
      '<td style="text-align:left;">', escape_html(meeting_roster$affiliation[[i]]), '</td>',
      '</tr>',
      sep = ""
    )
  }

  cat('</tbody></table></div>')
  cat('</details>')

} else {
  cat(
    '<div class="caution-note">',
    '<strong>Attendance roster unavailable.</strong> ',
    'The registry-backed event participation view did not produce a readable roster.',
    '</div>'
  )
}
```

::: {.footer-card}

## Thanks for joining us.

This Journal Club brought together academic clinicians, investigators, trainees, and industry colleagues to interrogate the same randomized evidence from different vantage points — and to make explicit where confidence increased and uncertainty remained.

:::

::: {.link-row}
[Back to Journal Club](../../jc.qmd){.soco-link}
[Read the JCO paper](https://ascopubs.org/doi/10.1200/JCO-26-00852){.soco-link .secondary}
:::
